---
title: "Data Cleaning for Study 2"
format: html
---

This file should only be used ONCE to clean the original data. Future analyses should use the output data of this document.

## Setup

### load libraries

```{r}
library(haven)
library(labelled)
library(dplyr)
library(janitor)
library(openxlsx2)
library(ggplot2)
```

## Loading original data

Once the data is loaded from the SPSS document, it does not need to be loaded again. Instead load the .rds file.

```{r}
## Survey
# df_original <- read_sav("../data/SESR+2.1+9-4.sav")
# saveRDS(df_original, file = "../data/df_original.rds")
```

Demographics were merged because the study was broken down into three studies on Prolific. Merger of the three files was done in Excel after verifying the column names and order.

```{r}
# # Demographics
# library(readr)
# demographics <- read_csv("data/demographics.csv")
# saveRDS(demographics, file = "../data/demographics.rds")
```

.rds file

```{r}
df_original <- readRDS("../data/df_original.rds")
demographics <- readRDS("../data/demographics.rds")
```

### clean variables names

```{r}
janitor::clean_names(df_original)
```

```{r}
janitor::clean_names(demographics)
```

### codebooks

```{r}
codebook_df <- generate_dictionary(df_original)
codebook_demographics <-generate_dictionary(demographics)
```

## Duplicate IDs

### duplicates

```{r}
# Count IDs in main dataset
df_counts <- df_original %>%
  count(PROLIFIC_PID, name = "n_df")

# Count IDs in demographics
demographics_counts <- demographics %>%
  count(`Participant id`, name = "n_demographics")

# Combine the counts
id_counts <- full_join(
  df_counts,
  demographics_counts,
  by = c("PROLIFIC_PID" = "Participant id")
) %>%
  mutate(
    n_df = coalesce(n_df, 0L),
    n_demographics = coalesce(n_demographics, 0L)
  ) %>%
  arrange(PROLIFIC_PID)

id_counts_duplicates <- id_counts %>%
  filter(
    n_df > 1 |
    n_demographics > 1
  )

id_counts_duplicates
```

### demographics: remove duplicates

```{r}
demographics_dups <- demographics %>%
  add_count(`Participant id`) %>%
  filter(n > 1) %>%
  arrange(`Participant id`)
```

```{r}
# write_xlsx(demographics_dups, "../data/demographics_dups.xlsx")
```

Duplicate ids in the demographics were removed. Priority was giving to submissions that included undergraduate status and clear completion of the study. Then earlier submissions were prioritized.

```{r}
glimpse(demographics$`Participant id`)
```

```{r}
# Check the demographics initially
nrow(demographics)
```

```{r}
remove_demographic_dups <- c(
  "6a8d0c26e8b1adfdcc967f50", 
  "6a8e484d3665d73ea5a4d4fd", 
  "6a8e026d4a2e824cff1ada21", 
  "6a8f01520e587cc1609e4c79", 
  "6a8e16433ec24b182ef6f7d1", 
  "6a556373d20279928b1f2880", 
  "6a8f926dcc3e7b477da6c75b", 
  "6a8d994187f6f382424bf8e5", 
  "6a8deb0b9f3f0e93ed9b2b93", 
  "6a8cb5e0cfcb19cdb9f8630e", 
  "6a8dc4fd72181d240251e132", 
  "6a8d0973fdbdfa56a09c7b13", 
  "6a34a7ae721837e00ca95fc0", 
  "6a358afde0265204086dd31e", 
  "6a345980b775767343fc0d73", 
  "6a26fbff153782058e7376f1", 
  "6a34412a4d8c168ea819ddc1", 
  "6a2c49b10abd9997062f3a8e", 
  "6a29e0eb85df36d6c7ec4fe8", 
  "6a29e3d4e625df90e4ca3dbc", 
  "6a3c22067621c749efc7e52b", 
  "6a398c63d33a334356a61513", 
  "6a39725206aca68adccf9bc9"
)

demographics_clean <- demographics %>%
  filter(!`Submission id` %in% remove_demographic_dups)
```

```{r}
# Check the number of rows
nrow(remove_demographic_dups)
nrow(demographics_clean)
```

```{r}
# Check that all of the duplicate ids could be found in the demogrpahics data to begin with
# pass if character(0)
setdiff(
  remove_demographic_dups,
  demographics$`Submission id`
)
```

```{r}
# Confirm that the cases are not present
# Should return an empty table
demographics_clean %>%
  filter(`Submission id` %in% remove_demographic_dups)
```

```{r}
# Remove unused content
rm(demographics, demographics_counts, demographics_dups, remove_demographic_dups)
```

### df: remove duplicates

```{r}
duplicate_df <- df_original %>%
  group_by(PROLIFIC_PID) %>%
  filter(n() > 1) %>%
  arrange(PROLIFIC_PID)

duplicate_df
```

```{r}
remove_df_dups <- c(
  "R_3I6DTTtPPaH4vUZ",
  "R_3HNANAPCnuQ4wYZ",
  "R_1iAkWwixWDtqVaN",
  "R_6QBEIW0WKnIAaC5",
  "R_5QPG66u3NUdmZfr",
  "R_5VmOpGEi2Vf45i1",
  "R_1svN5OzYc9mVXMQ",
  "R_33qcfGdPjlfmejD",
  "R_138doLIc4BAGrWh",
  "R_1esKLm6tC615w5E",
  "R_5fWbMpq7t9qXKoi",
  "R_18IfZub4cEQ3TG8",
  "R_1pFJplRS3i0Dfnl",
  "R_7wh0Y6UQvQWBdnO",
  "R_6IBpqlGsWtksFXH",
  "R_3j6cBwYeSpxv176",
  "R_1Bhcnn1v4SVQ6JT",
  "R_7WSrrM99AbqtQZz",
  "R_64r5Cg6QHM8fiaY",
  "R_3vMgTl0Fm6zLsK5",
  "R_5NyoyxFDzTlGx5G",
  "R_5DJZsUAgAgls945",
  "R_7AViuwy7lOExQ7D",
  "R_6EWHeYHMdNOp3A0",
  "R_1HVfrK3enCE6psl",
  "R_5IB4wrzrk8Uk3hh",
  "R_7SjDMMRViGvpTAY",
  "R_3nIUkD8RQ2NONNL",
  "R_5fekwmfcO7j9LmE"
)
```

```{r}
df_clean <- df_original %>%
  filter(!`ResponseId` %in% remove_df_dups)
```

```{r}
nrow(df_original)
length(remove_df_dups)
nrow(df_clean)
```

### drop unused 

```{r}
rm(id_counts, id_counts_duplicates, duplicate_df, duplicate_ids, df_original, df_counts)
rm(remove_df_dups)
```

## Join

### match with demographics

```{r}
names(df_clean)
```

```{r}
names(demographics_clean)
```

```{r}
df_full <- full_join(df_clean, demographics_clean, by = c("PROLIFIC_PID" =  "Participant id"))
```

```{r}
names(df_full)
```

```{r}
rm(codebook_demographics, codebook_df)
rm(df_clean)
rm(demographics_clean)
```

```{r}
codebook_df <- generate_dictionary(df_full)
```

```{r}
write_xlsx(codebook_df, "../data/codebook_df.xlsx")
```

## Cleaning

### view df_full

```{r}
head(df_full, 10)
```

```{r}
unique(df_full$UserLanguage)
```

### create df_full

```{r}
# Create new df with misc rows
df_misc <- df_full %>% 
  select(
    PROLIFIC_PID,
      Random_ID,
      ResponseId,
      Q88_First_Click,
      Q88_Last_Click,
      Q88_Page_Submit,
      Q88_Click_Count,
      Q89_First_Click,
      Q89_Last_Click,
      Q89_Page_Submit,
      Q89_Click_Count,
      Q2.11_First_Click,
      Q2.11_Last_Click,
      Q2.11_Page_Submit,
      Q2.11_Click_Count,
      Q2.14_First_Click,
      Q2.14_Last_Click,
      Q2.14_Page_Submit,
      Q2.14_Click_Count,
      Q90_First_Click,
      Q90_Last_Click,
      Q90_Page_Submit,
      Q90_Click_Count,
      Q91_First_Click,
      Q91_Last_Click,
      Q91_Page_Submit,
      Q91_Click_Count,
      Q92_First_Click,
      Q92_Last_Click,
      Q92_Page_Submit,
      Q92_Click_Count,
      Q93_First_Click,
      Q93_Last_Click,
      Q93_Page_Submit,
      Q93_Click_Count,
      Q7.5_First_Click,
      Q7.5_Last_Click,
      Q7.5_Page_Submit,
      Q7.5_Click_Count,
      Q8.2_First_Click,
      Q8.2_Last_Click,
      Q8.2_Page_Submit,
      Q8.2_Click_Count,
      Q9.2_First_Click,
      Q9.2_Last_Click,
      Q9.2_Page_Submit,
      Q9.2_Click_Count,
      Q10.2_First_Click,
      Q10.2_Last_Click,
      Q10.2_Page_Submit,
      Q10.2_Click_Count,
      Q11.2_First_Click,
      Q11.2_Last_Click,
      Q11.2_Page_Submit,
      Q11.2_Click_Count,
      Q12.2_First_Click,
      Q12.2_Last_Click,
      Q12.2_Page_Submit,
      Q12.2_Click_Count,
      Q14.4_First_Click,
      Q14.4_Last_Click,
      Q14.4_Page_Submit,
      Q14.4_Click_Count,
      LocationLatitude,
      LocationLongitude,
      ExternalReference,
      DistributionChannel,
      RecipientLastName,
      RecipientFirstName,
      RecipientEmail,
      IPAddress,
      Status.x,
      UserLanguage
    )

# Remove from df_full
df_full <- df_full %>% 
  select(
    -Q88_First_Click,
    -Q88_Last_Click,
    -Q88_Page_Submit,
    -Q88_Click_Count,
    -Q89_First_Click,
    -Q89_Last_Click,
    -Q89_Page_Submit,
    -Q89_Click_Count,
    -Q2.11_First_Click,
    -Q2.11_Last_Click,
    -Q2.11_Page_Submit,
    -Q2.11_Click_Count,
    -Q2.14_First_Click,
    -Q2.14_Last_Click,
    -Q2.14_Page_Submit,
    -Q2.14_Click_Count,
    -Q90_First_Click,
    -Q90_Last_Click,
    -Q90_Page_Submit,
    -Q90_Click_Count,
    -Q91_First_Click,
    -Q91_Last_Click,
    -Q91_Page_Submit,
    -Q91_Click_Count,
    -Q92_First_Click,
    -Q92_Last_Click,
    -Q92_Page_Submit,
    -Q92_Click_Count,
    -Q93_First_Click,
    -Q93_Last_Click,
    -Q93_Page_Submit,
    -Q93_Click_Count,
    -Q7.5_First_Click,
    -Q7.5_Last_Click,
    -Q7.5_Page_Submit,
    -Q7.5_Click_Count,
    -Q8.2_First_Click,
    -Q8.2_Last_Click,
    -Q8.2_Page_Submit,
    -Q8.2_Click_Count,
    -Q9.2_First_Click,
    -Q9.2_Last_Click,
    -Q9.2_Page_Submit,
    -Q9.2_Click_Count,
    -Q10.2_First_Click,
    -Q10.2_Last_Click,
    -Q10.2_Page_Submit,
    -Q10.2_Click_Count,
    -Q11.2_First_Click,
    -Q11.2_Last_Click,
    -Q11.2_Page_Submit,
    -Q11.2_Click_Count,
    -Q12.2_First_Click,
    -Q12.2_Last_Click,
    -Q12.2_Page_Submit,
    -Q12.2_Click_Count,
    -Q14.4_First_Click,
    -Q14.4_Last_Click,
    -Q14.4_Page_Submit,
    -Q14.4_Click_Count,
    -LocationLatitude,
    -LocationLongitude,
    -ExternalReference,
    -DistributionChannel,
    -RecipientLastName,
    -RecipientFirstName,
    -RecipientEmail,
    -IPAddress,
    -Status.x,
    -UserLanguage
  )
```

```{r}
names(df_full)
```

### export df_misc

```{r}
write_xlsx(df_misc, "../data/df_misc.xlsx")
```

```{r}
rm(df_misc)
```

### attention check

```{r}
df_full <- df_full %>%
  mutate(
    attention_fail_count =
      (Q9.1_14 != 1) +   # Strategies, 1
      (Q11.1_13 != 5) +  # Dozen, strongly agree = 5
      (Q12.1_19 != 3)    # NFC, uncertain = 3
  )

df_full %>%
  count(attention_fail_count)
```

```{r}

```

### timing

```{r}
df_full <- df_full %>%
  mutate(duration_min = Duration__in_seconds_ / 60)
```

```{r}
ggplot(
  data = df_full, 
  aes(duration_min)
) +
  geom_density()

```

```{r}
df_full %>%
  filter(Duration__in_seconds_ < 300) %>%
  select(PROLIFIC_PID, ResponseId, Duration__in_seconds_, RecordedDate, Progress) %>%
  arrange(Duration__in_seconds_)
```

### flags

attention check \> 3

```{r}
df_full <- df_full %>%
  mutate(
    under_5_min = Duration__in_seconds_ < 300,
    low_completion = Progress < .90, 
    attention_check = attention_fail_count > 2
  )
```

```{r}
df_full %>%
  count(under_5_min, low_completion, attention_check)
```

```{r}
df_full <- df_full %>%
  mutate(
    n_quality_flags =
      under_5_min +
      low_completion +
      attention_check
  )

df_full %>%
  count(n_quality_flags)
```

```{r}
df_full %>% 
  filter(
    under_5_min | 
    low_completion | 
    attention_check
  ) %>% 
  select(
    PROLIFIC_PID, 
    n_quality_flags,
    under_5_min, 
    low_completion, 
    attention_check
  )
```
