---
title: "Data Cleaning for Study 2"
format: html
---

This file should only be used ONCE to clean the original data. Future analyses should use the output data of this document.

## Setup

### load libraries

```{r setup, include=FALSE}
library(haven)
library(labelled)
library(dplyr)
library(janitor)
library(openxlsx2)
library(ggplot2)
library(psych)

source("../_common.R")

run_model <- TRUE
```

## Loading original data

Once the data is loaded from the SPSS document, it does not need to be loaded again. Instead load the .rds file.

```{r}
## Survey
# df_original <- read_sav("../data/SESR+2.1+9-4.sav")
# saveRDS(df_original, file = "../data/df_original.rds")
```

Demographics were merged because the study was broken down into three studies on Prolific. Merger of the three files was done in Excel after verifying the column names and order.

```{r}
# # Demographics
# library(readr)
# demographics <- read_csv("data/demographics.csv")
# saveRDS(demographics, file = "../data/demographics.rds")
```

.rds file

```{r}
df_original <- readRDS("../data/df_original.rds")
demographics <- readRDS("../data/demographics.rds")
```

### clean variables names

```{r}
df_original <- janitor::clean_names(df_original)
```

```{r}
demographics <- janitor::clean_names(demographics)
```

### codebooks

```{r}
codebook_df           <- generate_dictionary(df_original)
codebook_demographics <-generate_dictionary(demographics)
```

```{r}
# write_xlsx(codebook_df, "../codebook/codebook_df_original.xlsx")
# write_xlsx(codebook_demographics, "../codebook/codebook_demo_original.xlsx")
```

## Consent

```{r}
table(df_original$ic)
```

## Duplicate IDs

### duplicates

```{r}
# Count IDs in main dataset
df_counts <- df_original %>%
  count(prolific_pid, name = "n_df")

# Count IDs in demographics
demographics_counts <- demographics %>%
  count(participant_id, name = "n_demographics")

# Combine the counts
id_counts <- full_join(
  df_counts,
  demographics_counts,
  by = c("prolific_pid" = "participant_id")
) %>%
  mutate(
    n_df = coalesce(n_df, 0L),
    n_demographics = coalesce(n_demographics, 0L)
  ) %>%
  arrange(prolific_pid)

id_counts_duplicates <- id_counts %>%
  filter(
    n_df > 1 |
    n_demographics > 1
  )

id_counts_duplicates
```

### demographics: remove duplicates

```{r}
demographics_dups <- demographics %>%
  add_count(participant_id) %>%
  filter(n > 1) %>%
  arrange(participant_id)
```

```{r}
# write_xlsx(demographics_dups, "../data/demographics_dups.xlsx")
```

Duplicate ids in the demographics were removed. Priority was giving to submissions that included undergraduate status and clear completion of the study. Then earlier submissions were prioritized.

```{r}
glimpse(demographics$participant_id)
```

```{r}
# Check the demographics initially
nrow(demographics)
```

```{r}
remove_demographic_dups <- c(
  "6a8d0c26e8b1adfdcc967f50", 
  "6a8e484d3665d73ea5a4d4fd", 
  "6a8e026d4a2e824cff1ada21", 
  "6a8f01520e587cc1609e4c79", 
  "6a8e16433ec24b182ef6f7d1", 
  "6a556373d20279928b1f2880", 
  "6a8f926dcc3e7b477da6c75b", 
  "6a8d994187f6f382424bf8e5", 
  "6a8deb0b9f3f0e93ed9b2b93", 
  "6a8cb5e0cfcb19cdb9f8630e", 
  "6a8dc4fd72181d240251e132", 
  "6a8d0973fdbdfa56a09c7b13", 
  "6a34a7ae721837e00ca95fc0", 
  "6a358afde0265204086dd31e", 
  "6a345980b775767343fc0d73", 
  "6a26fbff153782058e7376f1", 
  "6a34412a4d8c168ea819ddc1", 
  "6a2c49b10abd9997062f3a8e", 
  "6a29e0eb85df36d6c7ec4fe8", 
  "6a29e3d4e625df90e4ca3dbc", 
  "6a3c22067621c749efc7e52b", 
  "6a398c63d33a334356a61513", 
  "6a39725206aca68adccf9bc9"
)

demographics_clean <- demographics %>%
  filter(!submission_id %in% remove_demographic_dups)
```

```{r}
# Check the number of rows
nrow(remove_demographic_dups)
nrow(demographics_clean)
```

```{r}
# Check that all of the duplicate ids could be found in the demogrpahics data to begin with
# pass if character(0)
setdiff(
  remove_demographic_dups,
  demographics$submission_id
)
```

```{r}
# Confirm that the cases are not present
# Should return an empty table
demographics_clean %>%
  filter(submission_id %in% remove_demographic_dups)
```

```{r}
# Remove unused content
rm(demographics, demographics_counts, demographics_dups, remove_demographic_dups)
```

### df: remove duplicates

```{r}
duplicate_df <- df_original %>%
  group_by(prolific_pid) %>%
  filter(n() > 1) %>%
  arrange(prolific_pid)

duplicate_df
```

```{r}
remove_df_dups <- c(
  "R_3I6DTTtPPaH4vUZ",
  "R_3HNANAPCnuQ4wYZ",
  "R_1iAkWwixWDtqVaN",
  "R_6QBEIW0WKnIAaC5",
  "R_5QPG66u3NUdmZfr",
  "R_5VmOpGEi2Vf45i1",
  "R_1svN5OzYc9mVXMQ",
  "R_33qcfGdPjlfmejD",
  "R_138doLIc4BAGrWh",
  "R_1esKLm6tC615w5E",
  "R_5fWbMpq7t9qXKoi",
  "R_18IfZub4cEQ3TG8",
  "R_1pFJplRS3i0Dfnl",
  "R_7wh0Y6UQvQWBdnO",
  "R_6IBpqlGsWtksFXH",
  "R_3j6cBwYeSpxv176",
  "R_1Bhcnn1v4SVQ6JT",
  "R_7WSrrM99AbqtQZz",
  "R_64r5Cg6QHM8fiaY",
  "R_3vMgTl0Fm6zLsK5",
  "R_5NyoyxFDzTlGx5G",
  "R_5DJZsUAgAgls945",
  "R_7AViuwy7lOExQ7D",
  "R_6EWHeYHMdNOp3A0",
  "R_1HVfrK3enCE6psl",
  "R_5IB4wrzrk8Uk3hh",
  "R_7SjDMMRViGvpTAY",
  "R_3nIUkD8RQ2NONNL",
  "R_5fekwmfcO7j9LmE"
)
```

```{r}
df_clean <- df_original %>%
  filter(!`response_id` %in% remove_df_dups)
```

```{r}
nrow(df_original)
length(remove_df_dups)
nrow(df_clean)
```

### verify

```{r}
df_clean %>%
  count(prolific_pid) %>%
  filter(n > 1)
```

```{r}
demographics_clean %>%
  count(participant_id) %>%
  filter(n > 1)
```

### drop unused

```{r}
rm(id_counts, id_counts_duplicates, duplicate_df, df_original, df_counts)
rm(remove_df_dups)
```

## Join

### names

```{r}
names(df_clean)
```

```{r}
names(demographics_clean)
```

```{r}
unique(demographics_clean$status)
```

```{r}
table(demographics_clean$status)
```

### full join

```{r}
df_full <- full_join(
  df_clean, 
  demographics_clean, 
  by = c("prolific_pid" =  "participant_id")
  )
```

```{r}
df_full %>%
  count(prolific_pid) %>%
  filter(n > 1)
```

```{r}
names(df_full)
```

```{r}
df_full %>% 
  filter(is.na(progress)) %>% 
  select(
    prolific_pid, 
    age, 
    progress
  )
```

### check match

```{r}
survey_without_demographics <- anti_join(
  df_clean,
  demographics_clean,
  by = c("prolific_pid" = "participant_id")
)

survey_without_demographics
```

```{r}
demographics_without_survey <- anti_join(
  demographics_clean,
  df_clean,
  by = c("participant_id" = "prolific_pid")
)

demographics_without_survey
```

```{r}
# write_xlsx(survey_without_demographics, "../data/survey_without_demographics.xlsx")
# write_xlsx(demographics_without_survey, "../data/demographics_without_survey.xlsx")
```

```{r}
rm(survey_without_demographics, demographics_without_survey)
```

### drop \<80 Progress

remove participants who did not complete at least 80% as they didn't see the task at less than 80.

```{r}
df_low_completion <- df_full %>%
  filter(progress < 80)

# write_xlsx(df_low_completion, "../data/df_low_completion.xlsx")
```

```{r}
df_low_completion %>%
  select(
    prolific_pid,
    response_id,
    progress,
    duration_in_seconds
  ) %>%
  arrange(progress)
```

```{r}
nrow(df_low_completion)
```

```{r}
class(df_full$progress)
```

```{r}
nrow(df_full)
```

```{r}
df_full <- df_full %>%
  filter(progress >= 80)
```

```{r}
nrow(df_full)
```

```{r}
df_full %>%
  filter(progress < 80)
```

```{r}
rm(df_low_completion)
```

### check match again

```{r}
df_full %>%
  mutate(
    match_status = case_when(
      !is.na(response_id) & !is.na(submission_id) ~ "Matched",
      !is.na(response_id) &  is.na(submission_id) ~ "Survey only - demographics missing",
       is.na(response_id) & !is.na(submission_id) ~ "Demographics only - survey missing",
       TRUE ~ "Missing both"
    )
  ) %>%
  count(match_status)
```

### remove unused

```{r}
rm(codebook_demographics, codebook_df, df_clean, demographics_clean)
```

```{r}
codebook_df <- generate_dictionary(df_full)
```

```{r}
# saveRDS(df_full, "../data/df_full.rds")
```

```{r}
# write_xlsx(codebook_df, "../data/codebook_df.xlsx")
```

## Cleaning

### view df_full

```{r}
head(df_full, 10)
```

### create df_full

```{r}
# Create new df with misc rows
df_misc <- df_full %>% 
  select(
    prolific_pid,
      random_id,
      response_id,
      q88_first_click,
      q88_last_click,
      q88_page_submit,
      q88_click_count,
      q89_first_click,
      q89_last_click,
      q89_page_submit,
      q89_click_count,
      q2_11_first_click,
      q2_11_last_click,
      q2_11_page_submit,
      q2_11_click_count,
      q2_14_first_click,
      q2_14_last_click,
      q2_14_page_submit,
      q2_14_click_count,
      q90_first_click,
      q90_last_click,
      q90_page_submit,
      q90_click_count,
      q91_first_click,
      q91_last_click,
      q91_page_submit,
      q91_click_count,
      q92_first_click,
      q92_last_click,
      q92_page_submit,
      q92_click_count,
      q93_first_click,
      q93_last_click,
      q93_page_submit,
      q93_click_count,
      q7_5_first_click,
      q7_5_last_click,
      q7_5_page_submit,
      q7_5_click_count,
      q8_2_first_click,
      q8_2_last_click,
      q8_2_page_submit,
      q8_2_click_count,
      q9_2_first_click,
      q9_2_last_click,
      q9_2_page_submit,
      q9_2_click_count,
      q10_2_first_click,
      q10_2_last_click,
      q10_2_page_submit,
      q10_2_click_count,
      q11_2_first_click,
      q11_2_last_click,
      q11_2_page_submit,
      q11_2_click_count,
      q12_2_first_click,
      q12_2_last_click,
      q12_2_page_submit,
      q12_2_click_count,
      q14_4_first_click,
      q14_4_last_click,
      q14_4_page_submit,
      q14_4_click_count,
      location_latitude,
      location_longitude,
      external_reference,
      distribution_channel,
      recipient_last_name,
      recipient_first_name,
      recipient_email,
      ip_address,
      status.x,
      user_language
    )

# Remove from df_full
df_full <- df_full %>% 
  select(
    -q88_first_click,
    -q88_last_click,
    -q88_page_submit,
    -q88_click_count,
    -q89_first_click,
    -q89_last_click,
    -q89_page_submit,
    -q89_click_count,
    -q2_11_first_click,
    -q2_11_last_click,
    -q2_11_page_submit,
    -q2_11_click_count,
    -q2_14_first_click,
    -q2_14_last_click,
    -q2_14_page_submit,
    -q2_14_click_count,
    -q90_first_click,
    -q90_last_click,
    -q90_page_submit,
    -q90_click_count,
    -q91_first_click,
    -q91_last_click,
    -q91_page_submit,
    -q91_click_count,
    -q92_first_click,
    -q92_last_click,
    -q92_page_submit,
    -q92_click_count,
    -q93_first_click,
    -q93_last_click,
    -q93_page_submit,
    -q93_click_count,
    -q7_5_first_click,
    -q7_5_last_click,
    -q7_5_page_submit,
    -q7_5_click_count,
    -q8_2_first_click,
    -q8_2_last_click,
    -q8_2_page_submit,
    -q8_2_click_count,
    -q9_2_first_click,
    -q9_2_last_click,
    -q9_2_page_submit,
    -q9_2_click_count,
    -q10_2_first_click,
    -q10_2_last_click,
    -q10_2_page_submit,
    -q10_2_click_count,
    -q11_2_first_click,
    -q11_2_last_click,
    -q11_2_page_submit,
    -q11_2_click_count,
    -q12_2_first_click,
    -q12_2_last_click,
    -q12_2_page_submit,
    -q12_2_click_count,
    -q14_4_first_click,
    -q14_4_last_click,
    -q14_4_page_submit,
    -q14_4_click_count,
    -location_latitude,
    -location_longitude,
    -external_reference,
    -distribution_channel,
    -recipient_last_name,
    -recipient_first_name,
    -recipient_email,
    -ip_address,
    -status.x,
    -user_language
  )
```

```{r}
names(df_full)
```

### export df_misc

```{r}
# saveRDS(df_misc, "../data/df_misc.rds")
```

```{r}
rm(df_misc)
```

## Flags

### progress

\<80 have been removed above. 3 cases without demographics.

```{r}
summary(df_full$progress)
```

#### NA

show cases with Progress `NA`

```{r}
df_full %>% 
  filter(is.na(progress))
```

No NA cases remain, so not needed ot remove them

```{r}
# # Remove the NA cases
# df_full <- df_full %>%
#   filter(!is.na(Progress))
```

```{r}
# summary(df_full$Progress)
```

### attention check

```{r}
df_full <- df_full %>%
  mutate(
    attention_fail_count =
      if_else(is.na(q9_1_14) | q9_1_14 != 1, 1L, 0L) +   # Strategies, 1
      if_else(is.na(q11_1_13) | q11_1_13 != 5, 1L, 0L) + # Dozen, strongly agree = 5
      if_else(is.na(q12_1_19) | q12_1_19 != 3, 1L, 0L)   # NFC, uncertain = 3
  )

df_full %>%
  count(attention_fail_count)
```

### timing

```{r}
df_full <- df_full %>%
  mutate(duration_min = duration_in_seconds / 60)
```

```{r}
ggplot(
  data = df_full, 
  aes(duration_min)
) +
  geom_density()
# Adressing the cases above also addressed the very short times for some submissions
# Updated in figure
```

```{r}
# Zero cases remaining with issue with time that is too fast 
df_full %>%
  filter(duration_in_seconds < 300) %>%
  select(prolific_pid, response_id, duration_in_seconds, recorded_date, progress) %>%
  arrange(duration_in_seconds)
```

### comprehension failure

```{r}
comprehension_items <- c(
  "comprehension1",
  "comprehension2",
  "comprehension3",
  "comprehension4",
  "comprehension5"
)
```

```{r}
df_full <- df_full %>%
  mutate(
    comprehension_n_answered = rowSums(
      !is.na(across(all_of(comprehension_items)))
    )
  )
```

```{r}
df_full <- df_full %>%
  mutate(
    comprehension_n_correct = rowSums(
      across(all_of(comprehension_items)),
      na.rm = TRUE
    )
  )

table(df_full$comprehension_n_correct)
```

```{r}
df_full %>%
  filter(comprehension_n_answered < 5) %>%
  summarise(
    comprehension1_missing = sum(is.na(comprehension1)),
    comprehension2_missing = sum(is.na(comprehension2)),
    comprehension3_missing = sum(is.na(comprehension3)),
    comprehension4_missing = sum(is.na(comprehension4)),
    comprehension5_missing = sum(is.na(comprehension5))
  )
```

```{r}
df_full %>%
  filter(comprehension_n_answered < 5) %>%
  count(
    comp1_missing = is.na(comprehension1),
    comp2_missing = is.na(comprehension2),
    comp3_missing = is.na(comprehension3),
    comp4_missing = is.na(comprehension4),
    comp5_missing = is.na(comprehension5)
  )
```

```{r}
df_full %>%
  filter(comprehension_n_answered < 5) %>%
  select(
    prolific_pid,
    progress,
    comprehension1,
    comprehension2,
    comprehension3,
    comprehension4,
    comprehension5,
    comprehension_n_answered,
    comprehension_n_correct
  ) %>%
  arrange(comprehension_n_answered)
```

```{r}
df_full <- df_full %>%
  mutate(
    comprehension_score = if_else(
      comprehension_n_answered == 5,
      5 - comprehension_n_correct,
      NA_real_
    )
  )
```

```{r}
df_full %>%
  count(comprehension_score)
```

Based on above participants passed the majority of the comprehension check items.

### flags

```{r}
summary(df_full$progress)
```

```{r}
df_full <- df_full %>%
  mutate(
    under_5_min = duration_in_seconds < 300,
    low_completion = progress < 90,
    attention_check = attention_fail_count > 2,
    comprehension_flag = comprehension_score > 0
  )
```

```{r}
df_full <- df_full %>%
  mutate(
    n_quality_flags =
      as.integer(under_5_min) +
      as.integer(low_completion) +
      as.integer(attention_check) +
      as.integer(comprehension_flag)
  )
```

```{r}
df_full %>%
  count(under_5_min, low_completion, attention_check, comprehension_flag)
```

```{r}
df_full <- df_full %>%
  mutate(
    exclude =
      under_5_min |
      low_completion |
      attention_check |
      comprehension_flag
  )

df_full %>%
  count(n_quality_flags)
```

```{r}
df_full %>% 
  filter(
    under_5_min | 
    low_completion | 
    attention_check
  ) %>% 
  select(
    prolific_pid, 
    n_quality_flags,
    under_5_min, 
    low_completion, 
    attention_check
  )
```

```{r}
# saveRDS(df_full, "../data/df_analysis.rds")
```

## Create SES

```{r}
levels(df_full$household_income_usd_us_participants_only)

levels(df_full$personal_income_usd_us_participants_only)

levels(df_full$highest_level_of_education_completed_by_parents)
```

```{r}
ses_data <- df_full %>%
  distinct(
    prolific_pid,
    household_income_usd_us_participants_only,
    personal_income_usd_us_participants_only,
    highest_level_of_education_completed_by_parents
  ) %>%
  mutate(

    household_income_num = case_when(
      household_income_usd_us_participants_only == "Less than $10000" ~ 1,
      household_income_usd_us_participants_only == "$10000–$15999" ~ 2,
      household_income_usd_us_participants_only == "$16000–$19999" ~ 3,
      household_income_usd_us_participants_only == "$20000–$24999" ~ 4,
      household_income_usd_us_participants_only == "$25000–$29999" ~ 5,
      household_income_usd_us_participants_only == "$30000–$34999" ~ 6,
      household_income_usd_us_participants_only == "$35000–$39999" ~ 7,
      household_income_usd_us_participants_only == "$40000–$49999" ~ 8,
      household_income_usd_us_participants_only == "$50000–$59999" ~ 9,
      household_income_usd_us_participants_only == "$60000–$74999" ~ 10,
      household_income_usd_us_participants_only == "$75000–$99999" ~ 11,
      household_income_usd_us_participants_only == "$100000–$149999" ~ 12,
      household_income_usd_us_participants_only == "More than $150000" ~ 13,
      TRUE ~ NA_real_
    ),

    personal_income_num = case_when(
      personal_income_usd_us_participants_only == "Less than $10000" ~ 1,
      personal_income_usd_us_participants_only == "$10000–$15999" ~ 2,
      personal_income_usd_us_participants_only == "$16000–$19999" ~ 3,
      personal_income_usd_us_participants_only == "$20000–$24999" ~ 4,
      personal_income_usd_us_participants_only == "$25000–$29999" ~ 5,
      personal_income_usd_us_participants_only == "$30000–$34999" ~ 6,
      personal_income_usd_us_participants_only == "$35000–$39999" ~ 7,
      personal_income_usd_us_participants_only == "$40000–$49999" ~ 8,
      personal_income_usd_us_participants_only == "$50000–$59999" ~ 9,
      personal_income_usd_us_participants_only == "$60000–$74999" ~ 10,
      personal_income_usd_us_participants_only == "$75000–$99999" ~ 11,
      personal_income_usd_us_participants_only == "$100000–$149999" ~ 12,
      personal_income_usd_us_participants_only == "More than $150000" ~ 13,
      personal_income_usd_us_participants_only == "Rather not say" ~ NA_real_,
      TRUE ~ NA_real_
    ),

    parent_education_num = case_when(
      highest_level_of_education_completed_by_parents ==
        "No formal qualifications" ~ 1,

      highest_level_of_education_completed_by_parents ==
        "Secondary education (e.g. GED/GCSE)" ~ 2,

      highest_level_of_education_completed_by_parents ==
        "High school diploma / A-Levels / Community college" ~ 3,

      highest_level_of_education_completed_by_parents ==
        "Undergraduate degree (BA/BSc/Other)" ~ 4,

      highest_level_of_education_completed_by_parents ==
        "Graduate degree (MA,MSc/MPhil/Other)" ~ 5,

      highest_level_of_education_completed_by_parents ==
        "Doctorate degree (PhD/other)" ~ 6,

      highest_level_of_education_completed_by_parents %in%
        c(
          "Don't know",
          "Not applicable / Prefer not to say"
        ) ~ NA_real_,

      TRUE ~ NA_real_
    )
  )
```

```{r}
ses_data %>%
  count(
    household_income_usd_us_participants_only,
    household_income_num
  )
```

```{r}
ses_data %>%
  count(
    personal_income_usd_us_participants_only,
    personal_income_num
  )
# empty! 
```

```{r}
ses_data %>%
  count(
    highest_level_of_education_completed_by_parents,
    parent_education_num
  )
```

```{r}
names(ses_data)
```

```{r}
ses_data <- ses_data %>% 
  select(
    -personal_income_usd_us_participants_only, 
    -personal_income_num
  )
```

```{r}
names(ses_data)
```

```{r}
rescale_to_1_7 <- function(x, min_value, max_value) {
  1 + (x - min_value) * 6 / (max_value - min_value)
}

ses_data <- ses_data %>%
  mutate(
    household_income_scaled =
      rescale_to_1_7(
        household_income_num,
        1,
        13
      ),

    parent_education_scaled =
      rescale_to_1_7(
        parent_education_num,
        1,
        6
      )
  )
```

```{r}
ses_data <- ses_data %>%
  mutate(
    SES_mean = if_else(
      !is.na(household_income_scaled) &
        !is.na(parent_education_scaled),

      rowMeans(
        cbind(
          household_income_scaled,
          parent_education_scaled
        )
      ),

      NA_real_
    )
  )
```

```{r}
ses_data %>%
  summarise(
    n_total = n(),
    n_household_income = sum(!is.na(household_income_scaled)),
    n_parent_education = sum(!is.na(parent_education_scaled)),
    n_complete_SES = sum(!is.na(SES_mean))
  )
```

```{r}
cor(
  ses_data$household_income_scaled,
  ses_data$parent_education_scaled,
  use = "complete.obs"
)
```

Excluded.

## df Organization

### Structure of Variables

```{r}
df_full <- df_full %>%
  mutate(
    across(
      c(
        sex,
        gender,
        ethnicity_simplified,
        ethnicity,
        household_income_usd_us_participants_only,
        personal_income_usd_us_participants_only,
        highest_level_of_education_completed_by_parents,
        undergraduate_year_of_study,
        student_status,
        employment_status,
        country_of_residence,
        country_of_birth,
        nationality,
        language,
        fluent_languages,
        current_u_s_state_of_residence,
        relationship_marital_status
        ),
      as.factor
    )
  )
```

### drop variables

```{r}
df_full <- df_full %>% 
  select(
    -start_date,
    -end_date,
    -comprehensioncount1,
    -comprehensioncount2,
    -comprehension1,
    -comprehension2,
    -comprehension3,
    -comprehension4,
    -comprehension5,
    -comprehensioncheck1,
    -comprehensioncheck2,
    -status.y,
    -custom_study_tncs_accepted_at,
    -started_at,
    -completed_at,
    -reviewed_at,
    -archived_at,
    -comprehension_n_answered,
    -comprehension_n_correct,
    -comprehension_score,
    -under_5_min,
    -low_completion,
    -attention_check,
    -comprehension_flag,
    -n_quality_flags,
    -exclude
  )
```

```{r}
df_full <- df_full %>% 
  select(
    -q_terminate_flag,
    -prolific_approval_status,
    -ic,
    -finished,
    -q3_2,
    -q3_3,
    -q3_4,
    -q3_5,
    -q3_6,
    -q5_2,
    -q5_3,
    -q5_4,
    -q5_5,
    -q5_6,
    -aboutyouinstructions
  )
```

### values for variable

#### household_income_usd_us_participants_only

```{r}
df_full <- df_full %>%
  mutate(
    household_income_usd_us_participants_only = factor(
      household_income_usd_us_participants_only,
      levels = c(
        "Less than $10000",
        "$10000–$15999",
        "$16000–$19999",
        "$20000–$24999",
        "$25000–$29999",
        "$30000–$34999",
        "$35000–$39999",
        "$40000–$49999",
        "$50000–$59999",
        "$60000–$74999",
        "$75000–$99999",
        "$100000–$149999",
        "More than $150000"
      ),
      ordered = TRUE
    )
  )
```

#### personal_income_usd_us_participants_only

```{r}
df_full <- df_full %>%
  mutate(
    personal_income_usd_us_participants_only =
      na_if(personal_income_usd_us_participants_only, "Rather not say")
  )

df_full <- df_full %>%
  mutate(
    personal_income_usd_us_participants_only = factor(
      personal_income_usd_us_participants_only,
      levels = c(
        "Less than $10000",
        "$10000–$15999",
        "$16000–$19999",
        "$20000–$24999",
        "$25000–$29999",
        "$30000–$34999",
        "$35000–$39999",
        "$40000–$49999",
        "$50000–$59999",
        "$60000–$74999",
        "$75000–$99999",
        "$100000–$149999",
        "More than $150000",
        "Rather not say"
      ),
      ordered = TRUE
    )
  )
```

#### highest_level_of_education_completed_by_parents

```{r}
df_full <- df_full %>%
  mutate(
    highest_level_of_education_completed_by_parents = factor(
      highest_level_of_education_completed_by_parents,
      levels = c(
        "No formal qualifications",
        "Secondary education (e.g. GED/GCSE)",
        "High school diploma / A-Levels / Community college",
        "Undergraduate degree (BA/BSc/Other)",
        "Graduate degree (MA,MSc/MPhil/Other)",
        "Doctorate degree (PhD/other)",
        "Don't know",
        "Not applicable / Prefer not to say"
      )
    )
  )
```

#### undergraduate_year_of_study

```{r}
df_full <- df_full %>%
  mutate(
    undergraduate_year_of_study = factor(
      undergraduate_year_of_study,
      levels = c(
        "1st Year",
        "2nd Year",
        "3rd Year",
        "4th Year",
        "Other"
      )
    )
  )
```

#### gender

```{r}
df_full <- df_full %>%
  mutate(
    gender = na_if(
      as.character(gender),
      "Rather not say"
    ),
    gender = factor(gender)
  )
```

#### ethnicity_simplified

```{r}
df_full <- df_full %>%
  mutate(
    ethnicity_simplified = na_if(
      as.character(ethnicity_simplified),
      "Prefer not to say"
    ),
    ethnicity_simplified = factor(ethnicity_simplified)
  )
```

#### language

```{r}
# Number of fluent languages
df_full <- df_full %>%
  mutate(
    n_fluent_languages = if_else(
      is.na(fluent_languages),
      NA_integer_,
      stringr::str_count(as.character(fluent_languages), ",") + 1L
    )
  )
```

```{r}
# multilingual
df_full <- df_full %>%
  mutate(
    multilingual = case_when(
      is.na(n_fluent_languages) ~ NA,
      n_fluent_languages == 1 ~ "One language",
      n_fluent_languages >= 2 ~ "Multiple languages"
    ),
    multilingual = factor(
      multilingual,
      levels = c("One language", "Multiple languages")
    )
  )
```

#### sex_num

#### structure_num

```{r}
df_full <- df_full %>%
  mutate(
    # Sex
    sex_num = case_when(
      sex == "Female" ~ 1,
      sex == "Male" ~ 0,
      TRUE ~ NA_real_
    ),

    # Structure
    structure = factor(
      structure,
      levels = c("individual", "group"),
      labels = c("Interindividual", "Intergroup")
    ),

    structure_num = case_when(
      structure == "Interindividual" ~ 0,
      structure == "Intergroup" ~ 1,
      TRUE ~ NA_real_
    ),

    # Motivation
    motivation = factor(
      motivation,
      levels = c("proself", "hybrid", "prosocial"),
      labels = c("Proself", "Hybrid", "Prosocial")
    )
  )
```

#### motivation

```{r}
df_full <- df_full %>%
  mutate(
    motivation_prosocial = case_when(
      motivation == "Prosocial" ~ 1,
      motivation %in% c("Proself", "Hybrid") ~ 0,
      TRUE ~ NA_real_
    ),

    motivation_hybrid = case_when(
      motivation == "Hybrid" ~ 1,
      motivation %in% c("Proself", "Prosocial") ~ 0,
      TRUE ~ NA_real_
    )
  )
# proself is the reference category
```

### labels for variables

```{r}
labelled::var_label(df_full$age) <- "Age"
labelled::var_label(df_full$sex) <- "Sex"
labelled::var_label(df_full$gender) <- "Gender"
labelled::var_label(df_full$ethnicity) <- "Ethnicity"
labelled::var_label(df_full$ethnicity_simplified) <- "Ethnicity, simplified"
labelled::var_label(df_full$country_of_birth) <- "Country of birth"
labelled::var_label(df_full$country_of_residence) <- "Country of residence"
labelled::var_label(df_full$nationality) <- "Nationality"
labelled::var_label(df_full$language) <- "Primary language"
labelled::var_label(df_full$student_status) <- "Student status"
labelled::var_label(df_full$employment_status) <- "Employment status"

labelled::var_label(df_full$household_income_usd_us_participants_only) <-
  "Household income (USD; U.S. participants only)"

labelled::var_label(df_full$personal_income_usd_us_participants_only) <-
  "Personal income (USD; U.S. participants only)"

labelled::var_label(df_full$highest_level_of_education_completed_by_parents) <-
  "Highest level of education completed by parents"

labelled::var_label(df_full$undergraduate_year_of_study) <-
  "Undergraduate year of study"

labelled::var_label(df_full$fluent_languages) <-
  "Fluent languages"

labelled::var_label(df_full$current_u_s_state_of_residence) <-
  "Current U.S. state of residence"

labelled::var_label(df_full$relationship_marital_status) <-
  "Relationship or marital status"

labelled::var_label(df_full$submission_id) <- "Prolific submission ID"
labelled::var_label(df_full$time_taken) <- "Prolific time taken"
labelled::var_label(df_full$completion_code) <- "Prolific completion code"
labelled::var_label(df_full$total_approvals) <- "Total Prolific approvals"

labelled::var_label(df_full$condition) <- "Experimental condition"
labelled::var_label(df_full$structure) <- "Structural context"
labelled::var_label(df_full$motivation) <- "Social motivation"
```

### order of variables

```{r}
df_full <- df_full %>% 
  select(
    prolific_pid,
    random_id,
    session_id,
    progress,
    duration_in_seconds,
    duration_min,
    recorded_date,
    response_id,
    submission_id,
    time_taken,
    completion_code,
    condition,
    structure,
    structure_num,
    motivation,
    motivation_prosocial,
    motivation_hybrid,
    which_letter,
    q7_3_1,
    q7_3_2,
    q7_3_3,
    q7_3_4,
    q7_3_5,
    q7_3_6,
    q7_3_7,
    q7_3_8,
    q7_3_9,
    q7_3_10,
    q7_4_1,
    q7_4_2,
    q7_4_3,
    q7_4_4,
    q7_4_5,
    q7_4_6,
    q7_4_7,
    q7_4_8,
    q7_4_9,
    q7_4_10,
    q9_1_1,
    q9_1_2,
    q9_1_3,
    q9_1_4,
    q9_1_5,
    q9_1_6,
    q9_1_7,
    q9_1_8,
    q9_1_9,
    q9_1_10,
    q9_1_11,
    q9_1_12,
    q9_1_13,
    q10_1_1,
    q10_1_2,
    q10_1_3,
    q10_1_4,
    q10_1_5,
    q10_1_6,
    q10_1_7,
    q10_1_8,
    q11_1_1,
    q11_1_2,
    q11_1_3,
    q11_1_4,
    q11_1_5,
    q11_1_6,
    q11_1_7,
    q11_1_8,
    q11_1_9,
    q11_1_10,
    q11_1_11,
    q11_1_12,
    q12_1_1,
    q12_1_2,
    q12_1_3,
    q12_1_4,
    q12_1_5,
    q12_1_6,
    q12_1_7,
    q12_1_8,
    q12_1_9,
    q12_1_10,
    q12_1_11,
    q12_1_12,
    q12_1_13,
    q12_1_14,
    q12_1_15,
    q12_1_16,
    q12_1_17,
    q12_1_18,
    q14_2,
    total_approvals,
    undergraduate_year_of_study,
    fluent_languages,
    relationship_marital_status,
    gender,
    current_u_s_state_of_residence,
    household_income_usd_us_participants_only,
    highest_level_of_education_completed_by_parents,
    personal_income_usd_us_participants_only,
    age,
    sex,
    sex_num,
    ethnicity_simplified,
    country_of_birth,
    country_of_residence, # everyone is from the US confirmation
    nationality,
    language,
    n_fluent_languages,
    multilingual,
    student_status,
    employment_status
  )
```

```{r}
saveRDS(df_full, "../data/df_analysis.rds")
codebook_df <- generate_dictionary(df_full)
write_xlsx(codebook_df, "../codebook/codebook_df_analysis.xlsx")
```

## Scoring

Aimed for threshold of completing \~80% of the items to calculate a score for a participant.

### Need for Cognition

#### recode

```{r}
df_full <- df_full %>%
  mutate(
    rq12_1_3r  = 6 - q12_1_3,
    rq12_1_4r  = 6 - q12_1_4,
    rq12_1_5r  = 6 - q12_1_5,
    rq12_1_7r  = 6 - q12_1_7,
    rq12_1_8r  = 6 - q12_1_8,
    rq12_1_9r  = 6 - q12_1_9,
    rq12_1_12r = 6 - q12_1_12,
    rq12_1_16r = 6 - q12_1_16,
    rq12_1_17r = 6 - q12_1_17
  )
```

#### items

```{r}
nfc_items <- c(
  "q12_1_1",
  "q12_1_2",
  "rq12_1_3r",
  "rq12_1_4r",
  "rq12_1_5r",
  "q12_1_6",
  "rq12_1_7r",
  "rq12_1_8r",
  "rq12_1_9r",
  "q12_1_10",
  "q12_1_11",
  "rq12_1_12r",
  "q12_1_13",
  "q12_1_14",
  "q12_1_15",
  "rq12_1_16r",
  "rq12_1_17r",
  "q12_1_18"
)
```

#### check number of responses

```{r}
df_full <- df_full %>%
  mutate(
    need_cog_n_answered = rowSums(
      !is.na(across(all_of(nfc_items)))
    )
  )

table(df_full$need_cog_n_answered)
```

#### sum and mean

```{r}
# df_full <- df_full %>%
#   mutate(
#     NeedCog_Sum = rowSums(
#       across(all_of(nfc_items)),
#       na.rm = TRUE
#     ),
# 
#     need_cog_mean = rowMeans(
#       across(all_of(nfc_items)),
#       na.rm = TRUE
#     )
#   )
```

```{r}
# Minimum response requirement, 15 items of 18
df_full <- df_full %>%
  mutate(
    need_cog_mean = if_else(
      need_cog_n_answered >= 15,
      rowMeans(
        across(all_of(nfc_items)),
        na.rm = TRUE
      ),
      NA_real_
    )
  )
```

#### Cronbach's alpha

```{r}
nfc_alpha <- psych::alpha(
  df_full %>%
    select(all_of(nfc_items))
)

nfc_alpha
```

```{r}
nfc_alpha$total$raw_alpha
```

```{r}
nfc_alpha$total$std.alpha
```

```{r}
nfc_alpha$item.stats
```

```{r}
nfc_alpha$alpha.drop
```

### Dirty Dozen

#### items

```{r}
narcissism_items <- c(
  "q11_1_9",
  "q11_1_10",
  "q11_1_11",
  "q11_1_12"
)

psychopathy_items <- c(
  "q11_1_5",
  "q11_1_6",
  "q11_1_7",
  "q11_1_8"
)

machiavellianism_items <- c(
  "q11_1_1",
  "q11_1_2",
  "q11_1_3",
  "q11_1_4"
)
```

#### completion

```{r}
df_full <- df_full %>%
  mutate(
    dirty_dozen_narcissism_n = rowSums(
      !is.na(across(all_of(narcissism_items)))
    ),

    dirty_dozen_psychopathy_n = rowSums(
      !is.na(across(all_of(psychopathy_items)))
    ),

    dirty_dozen_machiavellianism_n = rowSums(
      !is.na(across(all_of(machiavellianism_items)))
    )
  )
```

```{r}
table(df_full$dirty_dozen_narcissism_n)
table(df_full$dirty_dozen_psychopathy_n)
table(df_full$dirty_dozen_machiavellianism_n)
```

#### means

```{r}
# df_full <- df_full %>%
#   mutate(
#     dirty_dozen_narcissism = rowMeans(
#       across(all_of(narcissism_items)),
#       na.rm = TRUE
#     ),
# 
#     dirty_dozen_psychopathy = rowMeans(
#       across(all_of(psychopathy_items)),
#       na.rm = TRUE
#     ),
# 
#     dirty_dozen_machiavellianism = rowMeans(
#       across(all_of(machiavellianism_items)),
#       na.rm = TRUE
#     )
#   )
```

```{r}
# Minimum completion, 3 items of 4
df_full <- df_full %>%
  mutate(
    dirty_dozen_narcissism = if_else(
      dirty_dozen_narcissism_n >= 3,
      rowMeans(across(all_of(narcissism_items)), na.rm = TRUE),
      NA_real_
    ),

    dirty_dozen_psychopathy = if_else(
      dirty_dozen_psychopathy_n >= 3,
      rowMeans(across(all_of(psychopathy_items)), na.rm = TRUE),
      NA_real_
    ),

    dirty_dozen_machiavellianism = if_else(
      dirty_dozen_machiavellianism_n >= 3,
      rowMeans(across(all_of(machiavellianism_items)), na.rm = TRUE),
      NA_real_
    )
  )
```

#### Cronbach's alpha

```{r}
alpha_narcissism <- psych::alpha(
  df_full %>%
    select(all_of(narcissism_items))
)

alpha_narcissism
```

```{r}
alpha_psychopathy <- psych::alpha(
  df_full %>%
    select(all_of(psychopathy_items))
)

alpha_psychopathy
```

```{r}
alpha_machiavellianism <- psych::alpha(
  df_full %>%
    select(all_of(machiavellianism_items))
)

alpha_machiavellianism
```

```{r}
alpha_narcissism$total$raw_alpha
alpha_psychopathy$total$raw_alpha
alpha_machiavellianism$total$raw_alpha
```

### Cooperation

#### items

```{r}
competition_items <- c(
  "q10_1_1",
  "q10_1_2",
  "q10_1_3",
  "q10_1_4"
)

cooperation_items <- c(
  "q10_1_5",
  "q10_1_6",
  "q10_1_7",
  "q10_1_8"
)
```

#### recode competition

```{r}
df_full <- df_full %>%
  mutate(
    rq10_1_1r = 6 - q10_1_1,
    rq10_1_2r = 6 - q10_1_2,
    rq10_1_3r = 6 - q10_1_3,
    rq10_1_4r = 6 - q10_1_4
  )
```

```{r}
cooperation_scale_items <- c(
  "rq10_1_1r",
  "rq10_1_2r",
  "rq10_1_3r",
  "rq10_1_4r",
  "q10_1_5",
  "q10_1_6",
  "q10_1_7",
  "q10_1_8"
)
```

#### completion

```{r}
df_full <- df_full %>%
  mutate(
    cooperation_n_answered = rowSums(
      !is.na(across(all_of(cooperation_scale_items)))
    )
  )

table(df_full$cooperation_n_answered)
```

#### mean

```{r}
# df_full <- df_full %>%
#   mutate(
#     cooperation_mean = rowMeans(
#       across(all_of(cooperation_scale_items)),
#       na.rm = TRUE
#     )
#   )
```

```{r}
# minimum response, 6 items of 8
df_full <- df_full %>%
  mutate(
    cooperation_mean = if_else(
      cooperation_n_answered >= 6,
      rowMeans(
        across(all_of(cooperation_scale_items)),
        na.rm = TRUE
      ),
      NA_real_
    )
  )
```

#### Cronbach's alpha

```{r}
cooperation_alpha <- psych::alpha(
  df_full %>%
    select(all_of(cooperation_scale_items))
)

cooperation_alpha
```

```{r}
cooperation_alpha$total$raw_alpha
```

```{r}
cooperation_alpha$total$std.alpha
```

```{r}
cooperation_alpha$item.stats
```

```{r}
cooperation_alpha$alpha.drop
```

### Labels

```{r}
var_label(df_full$need_cog_n_answered) <- "Need for Cognition items answered"
var_label(df_full$need_cog_mean) <- "Need for Cognition mean score"

var_label(df_full$dirty_dozen_narcissism_n) <- "Dirty Dozen Narcissism items answered"
var_label(df_full$dirty_dozen_psychopathy_n) <- "Dirty Dozen Psychopathy items answered"
var_label(df_full$dirty_dozen_machiavellianism_n) <- "Dirty Dozen Machiavellianism items answered"

var_label(df_full$dirty_dozen_narcissism) <- "Dirty Dozen Narcissism mean score"
var_label(df_full$dirty_dozen_psychopathy) <- "Dirty Dozen Psychopathy mean score"
var_label(df_full$dirty_dozen_machiavellianism) <- "Dirty Dozen Machiavellianism mean score"

var_label(df_full$cooperation_n_answered) <- "Cooperation items answered"
var_label(df_full$cooperation_mean) <- "Cooperation mean score"
```

### columns

```{r}
df_full <- df_full %>% 
  select(
    # Cooperation items
    -q10_1_1,
    -q10_1_2,
    -q10_1_3,
    -q10_1_4,
    -q10_1_5,
    -q10_1_6,
    -q10_1_7,
    -q10_1_8,

    # Dirty Dozen items
    -q11_1_1,
    -q11_1_2,
    -q11_1_3,
    -q11_1_4,
    -q11_1_5,
    -q11_1_6,
    -q11_1_7,
    -q11_1_8,
    -q11_1_9,
    -q11_1_10,
    -q11_1_11,
    -q11_1_12,

    # Need for Cognition items
    -q12_1_1,
    -q12_1_2,
    -q12_1_3,
    -q12_1_4,
    -q12_1_5,
    -q12_1_6,
    -q12_1_7,
    -q12_1_8,
    -q12_1_9,
    -q12_1_10,
    -q12_1_11,
    -q12_1_12,
    -q12_1_13,
    -q12_1_14,
    -q12_1_15,
    -q12_1_16,
    -q12_1_17,
    -q12_1_18,

    # Temporary reverse-scored NFC items
    -rq12_1_3r,
    -rq12_1_4r,
    -rq12_1_5r,
    -rq12_1_7r,
    -rq12_1_8r,
    -rq12_1_9r,
    -rq12_1_12r,
    -rq12_1_16r,
    -rq12_1_17r,

    # Temporary reverse-scored cooperation items
    -rq10_1_1r,
    -rq10_1_2r,
    -rq10_1_3r,
    -rq10_1_4r
  )
```

### save df_full

```{r}
# Sort columns
df_full <- df_full %>%
  select(

    # --------------------------------------------------
    # IDs
    # --------------------------------------------------
    prolific_pid,
    response_id,
    random_id,
    session_id,
    submission_id,

    # --------------------------------------------------
    # Experimental conditions
    # --------------------------------------------------
    condition,
    structure,
    structure_num,
    motivation,
    motivation_prosocial,
    motivation_hybrid,
    which_letter,

    # --------------------------------------------------
    # Demographics / potential controls
    # --------------------------------------------------
    age,
    sex,
    sex_num,
    gender,
    ethnicity_simplified,
    household_income_usd_us_participants_only,
    personal_income_usd_us_participants_only,
    highest_level_of_education_completed_by_parents,
    undergraduate_year_of_study,
    student_status,
    employment_status,
    country_of_residence,
    country_of_birth,
    nationality,
    language,
    fluent_languages,
    n_fluent_languages,
    multilingual,
    current_u_s_state_of_residence,
    relationship_marital_status,

    # --------------------------------------------------
    # Information sharing
    # Common/public, high importance
    # --------------------------------------------------
    q7_3_1,
    q7_3_2,
    q7_3_3,
    q7_3_4,
    q7_3_5,

    # Common/public, low importance
    q7_3_6,
    q7_3_7,
    q7_3_8,
    q7_3_9,
    q7_3_10,

    # Unique/private, high importance
    q7_4_1,
    q7_4_2,
    q7_4_3,
    q7_4_4,
    q7_4_5,

    # Unique/private, low importance
    q7_4_6,
    q7_4_7,
    q7_4_8,
    q7_4_9,
    q7_4_10,

    # --------------------------------------------------
    # Strategies
    # --------------------------------------------------
    q9_1_1,
    q9_1_2,
    q9_1_3,
    q9_1_4,
    q9_1_5,
    q9_1_6,
    q9_1_7,
    q9_1_8,
    q9_1_9,
    q9_1_10,
    q9_1_11,
    q9_1_12,
    q9_1_13,

    # --------------------------------------------------
    # Scored measures
    # --------------------------------------------------
    need_cog_n_answered,
    need_cog_mean,

    dirty_dozen_narcissism_n,
    dirty_dozen_psychopathy_n,
    dirty_dozen_machiavellianism_n,
    dirty_dozen_narcissism,
    dirty_dozen_psychopathy,
    dirty_dozen_machiavellianism,

    cooperation_n_answered,
    cooperation_mean,

    # --------------------------------------------------
    # Open-ended feedback
    # --------------------------------------------------
    q14_2,

    # --------------------------------------------------
    # Survey administration / timing
    # --------------------------------------------------
    recorded_date,
    progress,
    duration_in_seconds,
    duration_min,
    time_taken,
    completion_code,
    total_approvals
  )
```

```{r}
saveRDS(df_full, "../data/df_full.rds")
```

```{r}
codebook_full <- generate_dictionary(df_full)
write_xlsx(codebook_full, "../codebook/codebook_full.xlsx")
```

## Create df_long

### clue key

```{r}
### clue_key
clue_key <- tibble(
  item_id = c(
    "q7_3_1", "q7_3_2", "q7_3_3", "q7_3_4", "q7_3_5",
    "q7_3_6", "q7_3_7", "q7_3_8", "q7_3_9", "q7_3_10",
    "q7_4_1", "q7_4_2", "q7_4_3", "q7_4_4", "q7_4_5",
    "q7_4_6", "q7_4_7", "q7_4_8", "q7_4_9", "q7_4_10"
  ),

  info_distribution = c(
    rep("Common", 10),
    rep("Unique", 10)
  ),

  info_importance = c(
    rep("High", 5),
    rep("Low", 5),
    rep("High", 5),
    rep("Low", 5)
  ),

  graves_excluded = c(
    rep(25, 5),
    rep(1, 5),
    rep(25, 5),
    rep(1, 5)
  ),

  clue_number = c(
    1:10,
    1:10
  ),

  clue_text = c(
    "The grave is not located in the northwestern part of the cemetery",
    "The person buried there died before 1776",
    "The person buried there did not die in autumn",
    "The tombstone does not have any religious symbols, nature symbols, or images engraved on it",
    "The inscription does not include 'beloved father' on it",
    "The person buried there lived fewer than 100 years",
    "The person buried there died of natural causes",
    "The person buried there was a monk",
    "The tombstone does not involve a statue",
    "The grave is not located within 50 yards of the current grounds keepers shed",

    "The name of the person ends in '-us'",
    "The person buried there was not an orphan",
    "The grave is not on the hill of the cemetery",
    "The person buried there was not born in springtime",
    "The grave is not located in the southeastern part of the cemetery",
    "The person is not buried a mausoleum",
    "The tombstone includes the person's first name, last name, and date of death",
    "The grave is not located next to the old oak tree",
    "The treasure is not in grave 84, 85, 86, or 87",
    "The tombstone is made of white marble"
  )
)

clue_key
```

### long format

```{r}
df_long <- df_full %>%
  pivot_longer(
    cols = starts_with("q7_3_") | starts_with("q7_4_"),
    names_to = "item_id",
    values_to = "item_response"
  ) %>%
  left_join(
    clue_key,
    by = "item_id"
  )

head(df_long, 25)
```

#### information type labels

```{r}
df_long <- df_long %>%
  dplyr::mutate(
    info_importance = factor(
      info_importance,
      levels = c("Low", "High")
    ),
    info_distribution = factor(
      info_distribution,
      levels = c("Common", "Unique")
    )
  )
```

```{r}
df_long <- df_long %>%
  mutate(
    item_response_label = labelled::to_factor(item_response)
  )
```

### responses

```{r}
attr(df_long$item_response, "labels")
```

### overall

```{r}
df_long %>%
  tabyl(item_response_label) %>%
  adorn_pct_formatting(digits = 1)
```

### by condition

```{r}
df_long %>%
  count(
    condition,
    item_response_label
  ) %>%
  group_by(
    condition
  ) %>%
  mutate(
    Percent = n / sum(n) * 100
  ) %>%
  ungroup()
```

### by condition & information type

```{r}
df_long %>%
  count(
    condition,
    info_distribution,
    info_importance,
    item_response_label
  ) %>%
  group_by(
    condition,
    info_distribution,
    info_importance
  ) %>%
  mutate(
    Percent = n / sum(n) * 100
  ) %>%
  ungroup()
```

```{r}
response_by_condition <- df_long %>%
  count(
    condition,
    info_distribution,
    info_importance,
    item_response_label
  ) %>%
  group_by(
    condition,
    info_distribution,
    info_importance
  ) %>%
  mutate(
    Percent = n / sum(n) * 100,
    Cell = paste0(n, " (", round(Percent, 1), "%)")
  ) %>%
  ungroup() %>%
  select(
    condition,
    info_distribution,
    info_importance,
    item_response_label,
    Cell
  ) %>%
  pivot_wider(
    names_from = item_response_label,
    values_from = Cell
  )

response_by_condition
```

### merge withholding and distortion

```{r}
df_long <- df_long %>%
  mutate(
    shared = case_when(
      item_response == 2 ~ 1,
      item_response %in% c(1, 3) ~ 0,
      TRUE ~ NA_real_
    )
  )
```

### compare item_response and shared

```{r}
tabyl(df_long, item_response)
```

```{r}
tabyl(df_long, shared)
```

### save df_long

```{r}
saveRDS(df_long, "../data/df_long.rds")
codebook_long <- generate_dictionary(df_long)
write_xlsx(codebook_long, "../codebook/codebook_long.xlsx")
```

## rm()

```{r}
rm(df_full, codebook_df)
rm(comprehension_items)
```

## End of Script

```{r}
print("end of script")
```
