---
title: "Data Cleaning for Study 2"
format: html
---

This file should only be used ONCE to clean the original data. Future analyses should use the output data of this document.

## Setup

### load libraries

```{r}
library(haven)
library(labelled)
library(dplyr)
library(janitor)
library(openxlsx2)
library(ggplot2)
```

## Loading original data

Once the data is loaded from the SPSS document, it does not need to be loaded again. Instead load the .rds file.

```{r}
## Survey
# df_original <- read_sav("../data/SESR+2.1+9-4.sav")
# saveRDS(df_original, file = "../data/df_original.rds")
```

Demographics were merged because the study was broken down into three studies on Prolific. Merger of the three files was done in Excel after verifying the column names and order.

```{r}
# # Demographics
# library(readr)
# demographics <- read_csv("data/demographics.csv")
# saveRDS(demographics, file = "../data/demographics.rds")
```

.rds file

```{r}
df_original <- readRDS("../data/df_original.rds")
demographics <- readRDS("../data/demographics.rds")
```

### clean variables names

```{r}
df_original <- janitor::clean_names(df_original)
```

```{r}
demographics <- janitor::clean_names(demographics)
```

### codebooks

```{r}
codebook_df           <- generate_dictionary(df_original)
codebook_demographics <-generate_dictionary(demographics)
```

```{r}
# write_xlsx(codebook_df, "../codebook/codebook_df_original.xlsx")
# write_xlsx(codebook_demographics, "../codebook/codebook_demo_original.xlsx")
```

## Consent

```{r}
table(df_original$ic)
```

## Duplicate IDs

### duplicates

```{r}
# Count IDs in main dataset
df_counts <- df_original %>%
  count(prolific_pid, name = "n_df")

# Count IDs in demographics
demographics_counts <- demographics %>%
  count(participant_id, name = "n_demographics")

# Combine the counts
id_counts <- full_join(
  df_counts,
  demographics_counts,
  by = c("prolific_pid" = "participant_id")
) %>%
  mutate(
    n_df = coalesce(n_df, 0L),
    n_demographics = coalesce(n_demographics, 0L)
  ) %>%
  arrange(prolific_pid)

id_counts_duplicates <- id_counts %>%
  filter(
    n_df > 1 |
    n_demographics > 1
  )

id_counts_duplicates
```

### demographics: remove duplicates

```{r}
demographics_dups <- demographics %>%
  add_count(participant_id) %>%
  filter(n > 1) %>%
  arrange(participant_id)
```

```{r}
# write_xlsx(demographics_dups, "../data/demographics_dups.xlsx")
```

Duplicate ids in the demographics were removed. Priority was giving to submissions that included undergraduate status and clear completion of the study. Then earlier submissions were prioritized.

```{r}
glimpse(demographics$participant_id)
```

```{r}
# Check the demographics initially
nrow(demographics)
```

```{r}
remove_demographic_dups <- c(
  "6a8d0c26e8b1adfdcc967f50", 
  "6a8e484d3665d73ea5a4d4fd", 
  "6a8e026d4a2e824cff1ada21", 
  "6a8f01520e587cc1609e4c79", 
  "6a8e16433ec24b182ef6f7d1", 
  "6a556373d20279928b1f2880", 
  "6a8f926dcc3e7b477da6c75b", 
  "6a8d994187f6f382424bf8e5", 
  "6a8deb0b9f3f0e93ed9b2b93", 
  "6a8cb5e0cfcb19cdb9f8630e", 
  "6a8dc4fd72181d240251e132", 
  "6a8d0973fdbdfa56a09c7b13", 
  "6a34a7ae721837e00ca95fc0", 
  "6a358afde0265204086dd31e", 
  "6a345980b775767343fc0d73", 
  "6a26fbff153782058e7376f1", 
  "6a34412a4d8c168ea819ddc1", 
  "6a2c49b10abd9997062f3a8e", 
  "6a29e0eb85df36d6c7ec4fe8", 
  "6a29e3d4e625df90e4ca3dbc", 
  "6a3c22067621c749efc7e52b", 
  "6a398c63d33a334356a61513", 
  "6a39725206aca68adccf9bc9"
)

demographics_clean <- demographics %>%
  filter(!submission_id %in% remove_demographic_dups)
```

```{r}
# Check the number of rows
nrow(remove_demographic_dups)
nrow(demographics_clean)
```

```{r}
# Check that all of the duplicate ids could be found in the demogrpahics data to begin with
# pass if character(0)
setdiff(
  remove_demographic_dups,
  demographics$submission_id
)
```

```{r}
# Confirm that the cases are not present
# Should return an empty table
demographics_clean %>%
  filter(submission_id %in% remove_demographic_dups)
```

```{r}
# Remove unused content
rm(demographics, demographics_counts, demographics_dups, remove_demographic_dups)
```

### df: remove duplicates

```{r}
duplicate_df <- df_original %>%
  group_by(prolific_pid) %>%
  filter(n() > 1) %>%
  arrange(prolific_pid)

duplicate_df
```

```{r}
remove_df_dups <- c(
  "R_3I6DTTtPPaH4vUZ",
  "R_3HNANAPCnuQ4wYZ",
  "R_1iAkWwixWDtqVaN",
  "R_6QBEIW0WKnIAaC5",
  "R_5QPG66u3NUdmZfr",
  "R_5VmOpGEi2Vf45i1",
  "R_1svN5OzYc9mVXMQ",
  "R_33qcfGdPjlfmejD",
  "R_138doLIc4BAGrWh",
  "R_1esKLm6tC615w5E",
  "R_5fWbMpq7t9qXKoi",
  "R_18IfZub4cEQ3TG8",
  "R_1pFJplRS3i0Dfnl",
  "R_7wh0Y6UQvQWBdnO",
  "R_6IBpqlGsWtksFXH",
  "R_3j6cBwYeSpxv176",
  "R_1Bhcnn1v4SVQ6JT",
  "R_7WSrrM99AbqtQZz",
  "R_64r5Cg6QHM8fiaY",
  "R_3vMgTl0Fm6zLsK5",
  "R_5NyoyxFDzTlGx5G",
  "R_5DJZsUAgAgls945",
  "R_7AViuwy7lOExQ7D",
  "R_6EWHeYHMdNOp3A0",
  "R_1HVfrK3enCE6psl",
  "R_5IB4wrzrk8Uk3hh",
  "R_7SjDMMRViGvpTAY",
  "R_3nIUkD8RQ2NONNL",
  "R_5fekwmfcO7j9LmE"
)
```

```{r}
df_clean <- df_original %>%
  filter(!`response_id` %in% remove_df_dups)
```

```{r}
nrow(df_original)
length(remove_df_dups)
nrow(df_clean)
```

### verify

```{r}
df_clean %>%
  count(prolific_pid) %>%
  filter(n > 1)
```

```{r}
demographics_clean %>%
  count(participant_id) %>%
  filter(n > 1)
```

### drop unused

```{r}
rm(id_counts, id_counts_duplicates, duplicate_df, df_original, df_counts)
rm(remove_df_dups)
```

## Join

### names

```{r}
names(df_clean)
```

```{r}
names(demographics_clean)
```

```{r}
unique(demographics_clean$status)
```

```{r}
table(demographics_clean$status)
```

### full join

```{r}
df_full <- full_join(
  df_clean, 
  demographics_clean, 
  by = c("prolific_pid" =  "participant_id")
  )
```

```{r}
df_full %>%
  count(prolific_pid) %>%
  filter(n > 1)
```

```{r}
names(df_full)
```

```{r}
df_full %>% 
  filter(is.na(progress)) %>% 
  select(
    prolific_pid, 
    age, 
    progress
  )
```

### check match

```{r}
survey_without_demographics <- anti_join(
  df_clean,
  demographics_clean,
  by = c("prolific_pid" = "participant_id")
)

survey_without_demographics
```

```{r}
demographics_without_survey <- anti_join(
  demographics_clean,
  df_clean,
  by = c("participant_id" = "prolific_pid")
)

demographics_without_survey
```

```{r}
# write_xlsx(survey_without_demographics, "../data/survey_without_demographics.xlsx")
# write_xlsx(demographics_without_survey, "../data/demographics_without_survey.xlsx")
```

```{r}
rm(survey_without_demographics, demographics_without_survey)
```

### drop \<80 Progress

remove participants who did not complete at least 80% as they didn't see the task at less than 80.

```{r}
df_low_completion <- df_full %>%
  filter(progress < 80)

# write_xlsx(df_low_completion, "../data/df_low_completion.xlsx")
```

```{r}
df_low_completion %>%
  select(
    prolific_pid,
    response_id,
    progress,
    duration_in_seconds
  ) %>%
  arrange(progress)
```

```{r}
nrow(df_low_completion)
```

```{r}
class(df_full$progress)
```

```{r}
nrow(df_full)
```

```{r}
df_full <- df_full %>%
  filter(progress >= 80)
```

```{r}
nrow(df_full)
```

```{r}
df_full %>%
  filter(progress < 80)
```

```{r}
rm(df_low_completion)
```

### check match again

```{r}
df_full %>%
  mutate(
    match_status = case_when(
      !is.na(response_id) & !is.na(submission_id) ~ "Matched",
      !is.na(response_id) &  is.na(submission_id) ~ "Survey only - demographics missing",
       is.na(response_id) & !is.na(submission_id) ~ "Demographics only - survey missing",
       TRUE ~ "Missing both"
    )
  ) %>%
  count(match_status)
```

### remove unused

```{r}
rm(codebook_demographics, codebook_df, df_clean, demographics_clean)
```

```{r}
codebook_df <- generate_dictionary(df_full)
```

```{r}
# saveRDS(df_full, "../data/df_full.xlsx")
```

```{r}
# write_xlsx(codebook_df, "../data/codebook_df.xlsx")
```

## Cleaning

### view df_full

```{r}
head(df_full, 10)
```

### create df_full

```{r}
# Create new df with misc rows
df_misc <- df_full %>% 
  select(
    prolific_pid,
      random_id,
      response_id,
      q88_first_click,
      q88_last_click,
      q88_page_submit,
      q88_click_count,
      q89_first_click,
      q89_last_click,
      q89_page_submit,
      q89_click_count,
      q2_11_first_click,
      q2_11_last_click,
      q2_11_page_submit,
      q2_11_click_count,
      q2_14_first_click,
      q2_14_last_click,
      q2_14_page_submit,
      q2_14_click_count,
      q90_first_click,
      q90_last_click,
      q90_page_submit,
      q90_click_count,
      q91_first_click,
      q91_last_click,
      q91_page_submit,
      q91_click_count,
      q92_first_click,
      q92_last_click,
      q92_page_submit,
      q92_click_count,
      q93_first_click,
      q93_last_click,
      q93_page_submit,
      q93_click_count,
      q7_5_first_click,
      q7_5_last_click,
      q7_5_page_submit,
      q7_5_click_count,
      q8_2_first_click,
      q8_2_last_click,
      q8_2_page_submit,
      q8_2_click_count,
      q9_2_first_click,
      q9_2_last_click,
      q9_2_page_submit,
      q9_2_click_count,
      q10_2_first_click,
      q10_2_last_click,
      q10_2_page_submit,
      q10_2_click_count,
      q11_2_first_click,
      q11_2_last_click,
      q11_2_page_submit,
      q11_2_click_count,
      q12_2_first_click,
      q12_2_last_click,
      q12_2_page_submit,
      q12_2_click_count,
      q14_4_first_click,
      q14_4_last_click,
      q14_4_page_submit,
      q14_4_click_count,
      location_latitude,
      location_longitude,
      external_reference,
      distribution_channel,
      recipient_last_name,
      recipient_first_name,
      recipient_email,
      ip_address,
      status.x,
      user_language
    )

# Remove from df_full
df_full <- df_full %>% 
  select(
    -q88_first_click,
    -q88_last_click,
    -q88_page_submit,
    -q88_click_count,
    -q89_first_click,
    -q89_last_click,
    -q89_page_submit,
    -q89_click_count,
    -q2_11_first_click,
    -q2_11_last_click,
    -q2_11_page_submit,
    -q2_11_click_count,
    -q2_14_first_click,
    -q2_14_last_click,
    -q2_14_page_submit,
    -q2_14_click_count,
    -q90_first_click,
    -q90_last_click,
    -q90_page_submit,
    -q90_click_count,
    -q91_first_click,
    -q91_last_click,
    -q91_page_submit,
    -q91_click_count,
    -q92_first_click,
    -q92_last_click,
    -q92_page_submit,
    -q92_click_count,
    -q93_first_click,
    -q93_last_click,
    -q93_page_submit,
    -q93_click_count,
    -q7_5_first_click,
    -q7_5_last_click,
    -q7_5_page_submit,
    -q7_5_click_count,
    -q8_2_first_click,
    -q8_2_last_click,
    -q8_2_page_submit,
    -q8_2_click_count,
    -q9_2_first_click,
    -q9_2_last_click,
    -q9_2_page_submit,
    -q9_2_click_count,
    -q10_2_first_click,
    -q10_2_last_click,
    -q10_2_page_submit,
    -q10_2_click_count,
    -q11_2_first_click,
    -q11_2_last_click,
    -q11_2_page_submit,
    -q11_2_click_count,
    -q12_2_first_click,
    -q12_2_last_click,
    -q12_2_page_submit,
    -q12_2_click_count,
    -q14_4_first_click,
    -q14_4_last_click,
    -q14_4_page_submit,
    -q14_4_click_count,
    -location_latitude,
    -location_longitude,
    -external_reference,
    -distribution_channel,
    -recipient_last_name,
    -recipient_first_name,
    -recipient_email,
    -ip_address,
    -status.x,
    -user_language
  )
```

```{r}
names(df_full)
```

### export df_misc

```{r}
# saveRDS(df_misc, "../data/df_misc.xlsx")
```

```{r}
rm(df_misc)
```

## Flags

### progress

\<80 have been removed above. 3 cases without demographics.

```{r}
summary(df_full$progress)
```

#### NA

show cases with Progress `NA`

```{r}
df_full %>% 
  filter(is.na(progress))
```

No NA cases remain, so not needed ot remove them

```{r}
# # Remove the NA cases
# df_full <- df_full %>%
#   filter(!is.na(Progress))
```

```{r}
# summary(df_full$Progress)
```

### attention check

```{r}
df_full <- df_full %>%
  mutate(
    attention_fail_count =
      if_else(is.na(q9_1_14) | q9_1_14 != 1, 1L, 0L) +   # Strategies, 1
      if_else(is.na(q11_1_13) | q11_1_13 != 5, 1L, 0L) + # Dozen, strongly agree = 5
      if_else(is.na(q12_1_19) | q12_1_19 != 3, 1L, 0L)   # NFC, uncertain = 3
  )

df_full %>%
  count(attention_fail_count)
```

### timing

```{r}
df_full <- df_full %>%
  mutate(duration_min = duration_in_seconds / 60)
```

```{r}
ggplot(
  data = df_full, 
  aes(duration_min)
) +
  geom_density()
# Adressing the cases above also addressed the very short times for some submissions
# Updated in figure
```

```{r}
# Zero cases remaining with issue with time that is too fast 
df_full %>%
  filter(duration_in_seconds < 300) %>%
  select(prolific_pid, response_id, duration_in_seconds, recorded_date, progress) %>%
  arrange(duration_in_seconds)
```

### comprehension failure

```{r}
comprehension_items <- c(
  "comprehension1",
  "comprehension2",
  "comprehension3",
  "comprehension4",
  "comprehension5"
)
```

```{r}
df_full <- df_full %>%
  mutate(
    comprehension_n_answered = rowSums(
      !is.na(across(all_of(comprehension_items)))
    )
  )
```

```{r}
df_full <- df_full %>%
  mutate(
    comprehension_n_correct = rowSums(
      across(all_of(comprehension_items)),
      na.rm = TRUE
    )
  )

table(df_full$comprehension_n_correct)
```

```{r}
df_full %>%
  filter(comprehension_n_answered < 5) %>%
  summarise(
    comprehension1_missing = sum(is.na(comprehension1)),
    comprehension2_missing = sum(is.na(comprehension2)),
    comprehension3_missing = sum(is.na(comprehension3)),
    comprehension4_missing = sum(is.na(comprehension4)),
    comprehension5_missing = sum(is.na(comprehension5))
  )
```

```{r}
df_full %>%
  filter(comprehension_n_answered < 5) %>%
  count(
    comp1_missing = is.na(comprehension1),
    comp2_missing = is.na(comprehension2),
    comp3_missing = is.na(comprehension3),
    comp4_missing = is.na(comprehension4),
    comp5_missing = is.na(comprehension5)
  )
```

```{r}
df_full %>%
  filter(comprehension_n_answered < 5) %>%
  select(
    prolific_pid,
    progress,
    comprehension1,
    comprehension2,
    comprehension3,
    comprehension4,
    comprehension5,
    comprehension_n_answered,
    comprehension_n_correct
  ) %>%
  arrange(comprehension_n_answered)
```

```{r}
df_full <- df_full %>%
  mutate(
    comprehension_score = if_else(
      comprehension_n_answered == 5,
      5 - comprehension_n_correct,
      NA_real_
    )
  )
```

```{r}
df_full %>%
  count(comprehension_score)
```

Based on above participants passed the majority of the comprehension check items.

### flags

```{r}
summary(df_full$progress)
```

```{r}
df_full <- df_full %>%
  mutate(
    under_5_min = duration_in_seconds < 300,
    low_completion = progress < 90,
    attention_check = attention_fail_count > 2,
    comprehension_flag = comprehension_score > 0
  )
```

```{r}
df_full <- df_full %>%
  mutate(
    n_quality_flags =
      as.integer(under_5_min) +
      as.integer(low_completion) +
      as.integer(attention_check) +
      as.integer(comprehension_flag)
  )
```

```{r}
df_full %>%
  count(under_5_min, low_completion, attention_check, comprehension_flag)
```

```{r}
df_full <- df_full %>%
  mutate(
    exclude =
      under_5_min |
      low_completion |
      attention_check |
      comprehension_flag
  )

df_full %>%
  count(n_quality_flags)
```

```{r}
df_full %>% 
  filter(
    under_5_min | 
    low_completion | 
    attention_check
  ) %>% 
  select(
    prolific_pid, 
    n_quality_flags,
    under_5_min, 
    low_completion, 
    attention_check
  )
```

```{r}
# saveRDS(df_full, "../data/df_analysis.xlsx")
```

## df Organization

### Structure of Variables

```{r}
df_full <- df_full %>%
  mutate(
    across(
      c(
        sex,
        gender,
        ethnicity_simplified,
        ethnicity,
        household_income_usd_us_participants_only,
        personal_income_usd_us_participants_only,
        highest_level_of_education_completed_by_parents,
        undergraduate_year_of_study,
        student_status,
        employment_status,
        country_of_residence,
        country_of_birth,
        nationality,
        language,
        fluent_languages,
        current_u_s_state_of_residence,
        relationship_marital_status
        ),
      as.factor
    )
  )
```

### drop variables

```{r}
df_full <- df_full %>% 
  select(
    -start_date,
    -end_date,
    -comprehensioncount1,
    -comprehensioncount2,
    -comprehension1,
    -comprehension2,
    -comprehension3,
    -comprehension4,
    -comprehension5,
    -comprehensioncheck1,
    -comprehensioncheck2,
    -status.y,
    -custom_study_tncs_accepted_at,
    -started_at,
    -completed_at,
    -reviewed_at,
    -archived_at,
    -comprehension_n_answered,
    -comprehension_n_correct,
    -comprehension_score,
    -under_5_min,
    -low_completion,
    -attention_check,
    -comprehension_flag,
    -n_quality_flags,
    -exclude
  )
```

```{r}
df_full <- df_full %>% 
  select(
    -q_terminate_flag,
    -prolific_approval_status,
    -ic,
    -finished,
    -q3_2,
    -q3_3,
    -q3_4,
    -q3_5,
    -q3_6,
    -q5_2,
    -q5_3,
    -q5_4,
    -q5_5,
    -q5_6,
    -aboutyouinstructions
  )
```

### order of variables

```{r}
df_full <- df_full %>% 
  select(
    prolific_pid,
    random_id,
    session_id,
    progress,
    duration_in_seconds,
    duration_min,
    recorded_date,
    response_id,
    submission_id,
    time_taken,
    completion_code,
    condition,
    structure,
    motivation,
    which_letter,
    q7_3_1,
    q7_3_2,
    q7_3_3,
    q7_3_4,
    q7_3_5,
    q7_3_6,
    q7_3_7,
    q7_3_8,
    q7_3_9,
    q7_3_10,
    q7_4_1,
    q7_4_2,
    q7_4_3,
    q7_4_4,
    q7_4_5,
    q7_4_6,
    q7_4_7,
    q7_4_8,
    q7_4_9,
    q7_4_10,
    q9_1_1,
    q9_1_2,
    q9_1_3,
    q9_1_4,
    q9_1_5,
    q9_1_6,
    q9_1_7,
    q9_1_8,
    q9_1_9,
    q9_1_10,
    q9_1_11,
    q9_1_12,
    q9_1_13,
    q10_1_1,
    q10_1_2,
    q10_1_3,
    q10_1_4,
    q10_1_5,
    q10_1_6,
    q10_1_7,
    q10_1_8,
    q11_1_1,
    q11_1_2,
    q11_1_3,
    q11_1_4,
    q11_1_5,
    q11_1_6,
    q11_1_7,
    q11_1_8,
    q11_1_9,
    q11_1_10,
    q11_1_11,
    q11_1_12,
    q12_1_1,
    q12_1_2,
    q12_1_3,
    q12_1_4,
    q12_1_5,
    q12_1_6,
    q12_1_7,
    q12_1_8,
    q12_1_9,
    q12_1_10,
    q12_1_11,
    q12_1_12,
    q12_1_13,
    q12_1_14,
    q12_1_15,
    q12_1_16,
    q12_1_17,
    q12_1_18,
    q14_2,
    total_approvals,
    undergraduate_year_of_study,
    fluent_languages,
    relationship_marital_status,
    gender,
    ethnicity,
    current_u_s_state_of_residence,
    household_income_usd_us_participants_only,
    highest_level_of_education_completed_by_parents,
    personal_income_usd_us_participants_only,
    age,
    sex,
    ethnicity_simplified,
    country_of_birth,
    country_of_residence,
    nationality,
    language,
    student_status,
    employment_status
  )
```

```{r}
saveRDS(df_full, "../data/df_analysis.xlsx")
codebook_df <- generate_dictionary(df_full)
write_xlsx(codebook_df, "../codebook/codebook_df_analysis.xlsx")
```

### rm()

```{r}
rm(df_full, codebook_df)
```

## End of Script

```{r}
print("end of script")
```
