---
title: "Descriptives for Study 2"
format: html
---

## Setup

```{r}
library(psych)
library(openxlsx2)
library(gtsummary)
library(dplyr)
library(janitor)
library(tibble)
library(tidyr)
library(labelled)
# library(modelsummary)
```

```{r}
# cleaned and scored data
df <- readRDS("../data/df_sorted.rds")
```

### Experimental Manipulations

```{r}
nrow(df)

df %>%
  count(structure, motivation) %>%
  mutate(
    percent = 100 * n / sum(n)
  )
```

```{r}
names(df)
```

## Demographics

```{r}
# Excel formula to copy based columns from codebook
# =IF(ISNUMBER(SEARCH(" ", B11)), ("'"&B11&"',"), (B11&","))
demographics <- df %>% 
  select(
    age,
    sex,
    gender,
    ethnicity_simplified,
    ethnicity,
    household_income_usd_us_participants_only,
    personal_income_usd_us_participants_only,
    highest_level_of_education_completed_by_parents,
    undergraduate_year_of_study,
    student_status,
    employment_status,
    country_of_residence,
    country_of_birth,
    nationality,
    language,
    fluent_languages,
    current_u_s_state_of_residence,
    relationship_marital_status
  )
```

### table_demo_describe

```{r}
table_demo_describe <- psych::describe(demographics)

table_demo_describe
```

### table_demo_summary

```{r}
table_demo_summary <- demographics %>%
  tbl_summary(
    statistic = all_categorical() ~ "{n} ({p}%)",
    digits = all_categorical() ~ c(0, 0),
    missing = "no"
  )

table_demo_summary
```

### table_demo_tabyl

```{r}
# tabyl approach
table_demo_tabyl <- bind_rows(

  tabyl(demographics, sex) %>%
    transmute(
      Variable = sex,
      n = n,
      Percent = round(percent * 100)
    ) %>%
    mutate(Group = "Sex"),

  tabyl(demographics, gender) %>%
    transmute(
      Variable = gender,
      n = n,
      Percent = round(percent * 100)
    ) %>%
    mutate(Group = "Gender"),

  tabyl(demographics, ethnicity_simplified) %>%
    transmute(
      Variable = ethnicity_simplified,
      n = n,
      Percent = round(percent * 100)
    ) %>%
    mutate(Group = "Ethnicity simplified"),

  tabyl(demographics, ethnicity) %>%
    transmute(
      Variable = ethnicity,
      n = n,
      Percent = round(percent * 100)
    ) %>%
    mutate(Group = "Ethnicity"),

  tabyl(demographics, household_income_usd_us_participants_only) %>%
    transmute(
      Variable = household_income_usd_us_participants_only,
      n = n,
      Percent = round(percent * 100)
    ) %>%
    mutate(Group = "Household income"),

  tabyl(demographics, personal_income_usd_us_participants_only) %>%
    transmute(
      Variable = personal_income_usd_us_participants_only,
      n = n,
      Percent = round(percent * 100)
    ) %>%
    mutate(Group = "Personal income"),

  tabyl(demographics, highest_level_of_education_completed_by_parents) %>%
    transmute(
      Variable = highest_level_of_education_completed_by_parents,
      n = n,
      Percent = round(percent * 100)
    ) %>%
    mutate(Group = "Parental education"),

  tabyl(demographics, undergraduate_year_of_study) %>%
    transmute(
      Variable = undergraduate_year_of_study,
      n = n,
      Percent = round(percent * 100)
    ) %>%
    mutate(Group = "Undergraduate year of study"),

  tabyl(demographics, student_status) %>%
    transmute(
      Variable = student_status,
      n = n,
      Percent = round(percent * 100)
    ) %>%
    mutate(Group = "Student status"),

  tabyl(demographics, employment_status) %>%
    transmute(
      Variable = employment_status,
      n = n,
      Percent = round(percent * 100)
    ) %>%
    mutate(Group = "Employment status"),

  tabyl(demographics, country_of_residence) %>%
    transmute(
      Variable = country_of_residence,
      n = n,
      Percent = round(percent * 100)
    ) %>%
    mutate(Group = "Country of residence"),

  tabyl(demographics, country_of_birth) %>%
    transmute(
      Variable = country_of_birth,
      n = n,
      Percent = round(percent * 100)
    ) %>%
    mutate(Group = "Country of birth"),

  tabyl(demographics, nationality) %>%
    transmute(
      Variable = nationality,
      n = n,
      Percent = round(percent * 100)
    ) %>%
    mutate(Group = "Nationality"),

  tabyl(demographics, language) %>%
    transmute(
      Variable = language,
      n = n,
      Percent = round(percent * 100)
    ) %>%
    mutate(Group = "Language"),

  tabyl(demographics, fluent_languages) %>%
    transmute(
      Variable = fluent_languages,
      n = n,
      Percent = round(percent * 100)
    ) %>%
    mutate(Group = "Fluent languages"),

  tabyl(demographics, current_u_s_state_of_residence) %>%
    transmute(
      Variable = current_u_s_state_of_residence,
      n = n,
      Percent = round(percent * 100)
    ) %>%
    mutate(Group = "Current U.S. state of residence"),

  tabyl(demographics, relationship_marital_status) %>%
    transmute(
      Variable = relationship_marital_status,
      n = n,
      Percent = round(percent * 100)
    ) %>%
    mutate(Group = "Relationship/marital status")
) %>%
  select(Group, Variable, n, Percent)

table_demo_tabyl
```

## Information Sharing

### clue_key

```{r}
clue_key <- tibble(
  item_id = c(
    "q7_3_1", "q7_3_2", "q7_3_3", "q7_3_4", "q7_3_5",
    "q7_3_6", "q7_3_7", "q7_3_8", "q7_3_9", "q7_3_10",
    "q7_4_1", "q7_4_2", "q7_4_3", "q7_4_4", "q7_4_5",
    "q7_4_6", "q7_4_7", "q7_4_8", "q7_4_9", "q7_4_10"
  ),

  info_distribution = c(
    rep("Common", 10),
    rep("Unique", 10)
  ),

  info_importance = c(
    rep("High", 5),
    rep("Low", 5),
    rep("High", 5),
    rep("Low", 5)
  ),

  graves_excluded = c(
    rep(25, 5),
    rep(1, 5),
    rep(25, 5),
    rep(1, 5)
  ),

  clue_number = c(
    1:10,
    1:10
  ),

  clue_text = c(
    "The grave is not located in the northwestern part of the cemetery",
    "The person buried there died before 1776",
    "The person buried there did not die in autumn",
    "The tombstone does not have any religious symbols, nature symbols, or images engraved on it",
    "The inscription does not include 'beloved father' on it",
    "The person buried there lived fewer than 100 years",
    "The person buried there died of natural causes",
    "The person buried there was a monk",
    "The tombstone does not involve a statue",
    "The grave is not located within 50 yards of the current grounds keepers shed",

    "The name of the person ends in '-us'",
    "The person buried there was not an orphan",
    "The grave is not on the hill of the cemetery",
    "The person buried there was not born in springtime",
    "The grave is not located in the southeastern part of the cemetery",
    "The person is not buried a mausoleum",
    "The tombstone includes the person's first name, last name, and date of death",
    "The grave is not located next to the old oak tree",
    "The treasure is not in grave 84, 85, 86, or 87",
    "The tombstone is made of white marble"
  )
)

clue_key
```

### long format

```{r}
df_long <- df %>%
  pivot_longer(
    cols = starts_with("q7_3_") | starts_with("q7_4_"),
    names_to = "item_id",
    values_to = "item_response"
  ) %>%
  left_join(
    clue_key,
    by = "item_id"
  )

head(df_long, 25)
```

### responses

```{r}
attr(df_long$item_response, "labels")
```

```{r}
df_long <- df_long %>%
  mutate(
    item_response_label = labelled::to_factor(item_response)
  )
```

### overall

```{r}
df_long %>%
  tabyl(item_response_label) %>%
  adorn_pct_formatting(digits = 1)
```

### by condition

```{r}
df_long %>%
  count(
    condition,
    item_response_label
  ) %>%
  group_by(
    condition
  ) %>%
  mutate(
    Percent = n / sum(n) * 100
  ) %>%
  ungroup()
```

### by condition & information type

```{r}
df_long %>%
  count(
    condition,
    info_distribution,
    info_importance,
    item_response_label
  ) %>%
  group_by(
    condition,
    info_distribution,
    info_importance
  ) %>%
  mutate(
    Percent = n / sum(n) * 100
  ) %>%
  ungroup()
```

```{r}
response_by_condition <- df_long %>%
  count(
    condition,
    info_distribution,
    info_importance,
    item_response_label
  ) %>%
  group_by(
    condition,
    info_distribution,
    info_importance
  ) %>%
  mutate(
    Percent = n / sum(n) * 100,
    Cell = paste0(n, " (", round(Percent, 1), "%)")
  ) %>%
  ungroup() %>%
  select(
    condition,
    info_distribution,
    info_importance,
    item_response_label,
    Cell
  ) %>%
  pivot_wider(
    names_from = item_response_label,
    values_from = Cell
  )

response_by_condition
```

### merge withholding and distortion

```{r}
df_long <- df_long %>%
  mutate(
    shared = case_when(
      item_response == 2 ~ 1,
      item_response %in% c(1, 3) ~ 0,
      TRUE ~ NA_real_
    )
  )
```

### compare item_response and shared

```{r}
tabyl(df_long, item_response)
```

```{r}
tabyl(df_long, shared)
```

### breakdown

#### by clue

```{r}
df_long %>%
  group_by(item_id, info_distribution, info_importance) %>%
  summarise(
    n = n(),
    Share_n = sum(shared == 1, na.rm = TRUE),
    Share_percent = mean(shared, na.rm = TRUE) * 100,
    .groups = "drop"
  ) %>%
  arrange(Share_percent)
```

#### by participant

```{r}
df_long %>%
  group_by(response_id) %>%
  summarise(
    n_items = n(),
    Share_n = sum(shared == 1, na.rm = TRUE),
    Share_percent = mean(shared, na.rm = TRUE) * 100,
    .groups = "drop"
  )
```

```{r}
df_long %>%
  group_by(response_id) %>%
  summarise(
    Share_percent = mean(shared, na.rm = TRUE) * 100,
    .groups = "drop"
  ) %>%
  summarise(
    Mean = mean(Share_percent),
    SD = sd(Share_percent),
    Min = min(Share_percent),
    Max = max(Share_percent)
  )
```

#### by condition

```{r}
shared_by_condition <- df_long %>%
  count(
    condition,
    info_distribution,
    info_importance,
    shared
  ) %>%
  group_by(
    condition,
    info_distribution,
    info_importance
  ) %>%
  mutate(
    Percent = n / sum(n) * 100,
    Cell = paste0(n, " (", round(Percent, 1), "%)")
  ) %>%
  ungroup() %>%
  select(
    condition,
    info_distribution,
    info_importance,
    shared,
    Cell
  ) %>%
  pivot_wider(
    names_from = shared,
    values_from = Cell
  )

shared_by_condition
```

## Measures

```{r}
vars_main <- c(
  "need_cog_mean",
  "dirty_dozen_narcissism",
  "dirty_dozen_psychopathy",
  "dirty_dozen_machiavellianism",
  "cooperation_mean"
)

# Count of missing values (NA)
df %>%
  summarise(
    across(
      all_of(vars_main),
      ~ sum(is.na(.x))
    )
  )
```

```{r}
control_table <- df_long %>%
  distinct(response_id, .keep_all = TRUE) %>%
  summarise(
    across(
      c(
        need_cog_mean,
        age
        # add other continuous controls here
      ),
      list(
        n = ~ sum(!is.na(.)),
        M = ~ mean(., na.rm = TRUE),
        SD = ~ sd(., na.rm = TRUE)
      )
    )
  )
```

## Save to Workbook

```{r}
# Create the workbook
wb <- wb_workbook()
```

### table_demo_describe

```{r}
sheet_name <- "Describe"
table      <- table_demo_describe

wb$add_worksheet(sheet_name)

wb$add_data_table(
  sheet = sheet_name, 
  x = table
)
```

### table_demo_summary

```{r}
sheet_name <- "Summary"

table <- table_demo_summary %>%
  as_tibble()

wb$add_worksheet(sheet_name)

wb$add_data_table(
  sheet = sheet_name,
  x = table
)
```

### table_demo_tabyl

```{r}
sheet_name <- "Tabyl"
table      <- table_demo_tabyl %>% 
  as_tibble()

wb$add_worksheet(sheet_name)

wb$add_data_table(
  sheet = sheet_name, 
  x = table
)
```

### save file

```{r}
wb_save(
  wb, 
  file = "../tables/describe.xlsx"
)
```

### save df

```{r}
saveRDS(df, "../data/df_descriptives.rds")
codebook_df_descriptives <- generate_dictionary(df)
write_xlsx(codebook_df_descriptives, "../codebook/codebook_df_descriptives.xlsx")
```

### save df_long

```{r}
saveRDS(df_long, "../data/df_long.rds")
codebook_df_long <- generate_dictionary(df_long)
write_xlsx(codebook_df_long, "../codebook/codebook_df_long.xlsx")
```

### rm()

```{r}
rm(table_demo_describe, table_demo_summary, table_demo_tabyl)
rm(table)
rm(wb, sheet_name)
rm(clue_key, control_table, demographics, response_by_condition, shared_by_condition)
rm(df, df_long, codebook_df_descriptives, codebook_df_long)
rm(vars_main)
```

## End of Script

```{r}
print("end of script")
```
