---
title: "Descriptives for Study 2"
format: html
---

## Setup

```{r setup, include=FALSE}
library(psych)
library(openxlsx2)
library(gtsummary)
library(dplyr)
library(janitor)
library(tibble)
library(tidyr)
library(labelled)
library(gt)
library(emmeans)
# library(modelsummary)

source("../_common.R")

run_model <- TRUE
```

```{r}
# cleaned and scored data
df <- readRDS("../data/df_full.rds")
df_long <- readRDS("../data/df_long.rds")
```

### Experimental Manipulations

```{r}
nrow(df)

df %>%
  count(structure, motivation) %>%
  mutate(
    percent = 100 * n / sum(n)
  )
```

```{r}
names(df)
```

## Demographics

```{r}
# Excel formula to copy based columns from codebook
# =IF(ISNUMBER(SEARCH(" ", B11)), ("'"&B11&"',"), (B11&","))
demographics <- df %>% 
  select(
    age,
    sex,
    gender,
    ethnicity_simplified,
    household_income_usd_us_participants_only,
    personal_income_usd_us_participants_only,
    highest_level_of_education_completed_by_parents,
    undergraduate_year_of_study,
    student_status,
    employment_status,
    country_of_residence,
    country_of_birth,
    nationality,
    language,
    fluent_languages,
    current_u_s_state_of_residence,
    relationship_marital_status
  )
```

### table_demo_describe

```{r}
table_demo_describe <- psych::describe(demographics)

table_demo_describe
```

### table_demo_summary

```{r}
table_demo_summary <- demographics %>%
  tbl_summary(
    statistic = all_categorical() ~ "{n} ({p}%)",
    digits = all_categorical() ~ c(0, 0),
    missing = "no"
  )

table_demo_summary
```

### table_demo_tabyl

```{r}
# tabyl approach
table_demo_tabyl <- bind_rows(

  tabyl(demographics, sex) %>%
    transmute(
      Variable = as.character(sex),
      n = n,
      Percent = round(percent * 100)
    ) %>%
    mutate(Group = "Sex"),

  tabyl(demographics, gender) %>%
    transmute(
      Variable = as.character(gender),
      n = n,
      Percent = round(percent * 100)
    ) %>%
    mutate(Group = "Gender"),

  tabyl(demographics, ethnicity_simplified) %>%
    transmute(
      Variable = as.character(ethnicity_simplified),
      n = n,
      Percent = round(percent * 100)
    ) %>%
    mutate(Group = "Ethnicity simplified"),

  tabyl(demographics, household_income_usd_us_participants_only) %>%
    transmute(
      Variable = as.character(household_income_usd_us_participants_only),
      n = n,
      Percent = round(percent * 100)
    ) %>%
    mutate(Group = "Household income"),

  tabyl(demographics, personal_income_usd_us_participants_only) %>%
    transmute(
      Variable = as.character(personal_income_usd_us_participants_only),
      n = n,
      Percent = round(percent * 100)
    ) %>%
    mutate(Group = "Personal income"),

  tabyl(demographics, highest_level_of_education_completed_by_parents) %>%
    transmute(
      Variable = as.character(
        highest_level_of_education_completed_by_parents
      ),
      n = n,
      Percent = round(percent * 100)
    ) %>%
    mutate(Group = "Parental education"),

  tabyl(demographics, undergraduate_year_of_study) %>%
    transmute(
      Variable = as.character(undergraduate_year_of_study),
      n = n,
      Percent = round(percent * 100)
    ) %>%
    mutate(Group = "Undergraduate year of study"),

  tabyl(demographics, student_status) %>%
    transmute(
      Variable = as.character(student_status),
      n = n,
      Percent = round(percent * 100)
    ) %>%
    mutate(Group = "Student status"),

  tabyl(demographics, employment_status) %>%
    transmute(
      Variable = as.character(employment_status),
      n = n,
      Percent = round(percent * 100)
    ) %>%
    mutate(Group = "Employment status"),

  tabyl(demographics, country_of_residence) %>%
    transmute(
      Variable = as.character(country_of_residence),
      n = n,
      Percent = round(percent * 100)
    ) %>%
    mutate(Group = "Country of residence"),

  tabyl(demographics, country_of_birth) %>%
    transmute(
      Variable = as.character(country_of_birth),
      n = n,
      Percent = round(percent * 100)
    ) %>%
    mutate(Group = "Country of birth"),

  tabyl(demographics, nationality) %>%
    transmute(
      Variable = as.character(nationality),
      n = n,
      Percent = round(percent * 100)
    ) %>%
    mutate(Group = "Nationality"),

  tabyl(demographics, language) %>%
    transmute(
      Variable = as.character(language),
      n = n,
      Percent = round(percent * 100)
    ) %>%
    mutate(Group = "Language"),

  tabyl(demographics, fluent_languages) %>%
    transmute(
      Variable = as.character(fluent_languages),
      n = n,
      Percent = round(percent * 100)
    ) %>%
    mutate(Group = "Fluent languages"),

  tabyl(demographics, current_u_s_state_of_residence) %>%
    transmute(
      Variable = as.character(current_u_s_state_of_residence),
      n = n,
      Percent = round(percent * 100)
    ) %>%
    mutate(Group = "Current U.S. state of residence"),

  tabyl(demographics, relationship_marital_status) %>%
    transmute(
      Variable = as.character(relationship_marital_status),
      n = n,
      Percent = round(percent * 100)
    ) %>%
    mutate(Group = "Relationship/marital status")

) %>%
  select(
    Group,
    Variable,
    n,
    Percent
  )

table_demo_tabyl
```

### table_demo_purr

```{r}
demographic_vars <- c(
  "sex",
  "ethnicity_simplified",
  "household_income_usd_us_participants_only",
  "highest_level_of_education_completed_by_parents",
  "undergraduate_year_of_study",
  "student_status",
  "employment_status",
  "relationship_marital_status"
)
```

```{r}
demographic_labels <- c(
  sex = "Sex",
  ethnicity_simplified = "Race / Ethnicity",
  household_income_usd_us_participants_only = "Household Income",
  highest_level_of_education_completed_by_parents = "Parental Education",
  undergraduate_year_of_study = "Undergraduate Year of Study",
  student_status = "Student Status",
  employment_status = "Employment Status",
  relationship_marital_status = "Relationship / Marital Status"
)
```

```{r}
participant_characteristics_long <- purrr::map_dfr(
  demographic_vars,
  function(var) {

    df %>%
      count(.data[[var]], name = "n") %>%
      mutate(
        Percent = n / sum(n) * 100,
        Group = demographic_labels[[var]],
        Variable = as.character(.data[[var]])
      ) %>%
      select(
        Group,
        Variable,
        n,
        Percent
      )
  }
)
```

```{r}
participant_characteristics_long <- participant_characteristics_long %>%
  mutate(
    Variable = case_when(
      is.na(Variable) ~ "Missing",
      Variable == "NA" ~ "Missing",
      TRUE ~ Variable
    )
  )
```

```{r}
participant_characteristics_long <- purrr::map_dfr(
  demographic_vars,
  function(var) {

    df %>%
      filter(!is.na(.data[[var]])) %>%
      count(.data[[var]], name = "n") %>%
      mutate(
        Percent = n / sum(n) * 100,
        Group = demographic_labels[[var]],
        Variable = as.character(.data[[var]])
      ) %>%
      select(
        Group,
        Variable,
        n,
        Percent
      )
  }
)
```

```{r}
table_participant_characteristics_data <- participant_characteristics_long %>%
  group_by(Group) %>%
  group_modify(
    ~ bind_rows(
      tibble(
        Variable = unique(.y$Group),
        n = NA_integer_,
        Percent = NA_real_
      ),
      .x %>%
        select(
          Variable,
          n,
          Percent
        )
    )
  ) %>%
  ungroup() %>%
  select(
    Variable,
    n,
    Percent
  )
```

```{r}
table_participant_characteristics_data <- 
  table_participant_characteristics_data %>%
  mutate(
    Percent = ifelse(
      is.na(Percent),
      "",
      sprintf(
        "%.0f",
        round_half_up(Percent, 0)
      )
    ),
    n = ifelse(
      is.na(n),
      "",
      as.character(n)
    )
  )
```

```{r}
table_participant_characteristics <- 
  table_participant_characteristics_data %>%
  gt() %>%
  cols_label(
    Variable = "Variable",
    n = md("*n*"),
    Percent = "%"
  ) %>%
  cols_align(
    align = "left",
    columns = Variable
  ) %>%
  cols_align(
    align = "center",
    columns = c(n, Percent)
  ) %>%
  tab_options(
    table.font.names = "Times New Roman",
    table.font.size = 12,
    column_labels.font.weight = "bold",
    data_row.padding = px(3)
  )

table_demo_purr <- table_participant_characteristics
```

### table_continuous

```{r}
continuous_vars <- c(
  "need_cog_mean",
  "dirty_dozen_narcissism",
  "dirty_dozen_psychopathy",
  "dirty_dozen_machiavellianism", 
  "cooperation_mean"
)
```

```{r}
continuous_labels <- c(
  need_cog_mean = "Need for Cognition",
  dirty_dozen_narcissism = "Narcissism",
  dirty_dozen_psychopathy = "Psychopathy",
  dirty_dozen_machiavellianism = "Machiavellianism",
  cooperation_mean = "Self-Reported Cooperation"
)
```

```{r}
table_continuous_data <- purrr::map_dfr(
  continuous_vars,
  function(var) {
    
    x <- df[[var]]
    
    tibble(
      Variable = continuous_labels[[var]],
      n = sum(!is.na(x)),
      M = mean(x, na.rm = TRUE),
      SD = sd(x, na.rm = TRUE)
    )
  }
)
```

```{r}
table_continuous_data <- table_continuous_data %>%
  mutate(
    M = format_stat(M),
    SD = format_stat(SD)
  )
```

```{r}
table_continuous <- table_continuous_data %>%
  gt() %>%
  cols_label(
    Variable = "Variable",
    n = md("*n*"),
    M = md("*M*"),
    SD = md("*SD*")
  ) %>%
  cols_align(
    align = "left",
    columns = Variable
  ) %>%
  cols_align(
    align = "center",
    columns = c(n, M, SD)
  ) %>%
  tab_options(
    table.font.names = "Times New Roman",
    table.font.size = 12,
    column_labels.font.weight = "bold",
    data_row.padding = px(3)
  )

table_continuous
```

## Information Sharing

### breakdown

#### by clue

```{r}
df_long %>%
  group_by(item_id, info_distribution, info_importance) %>%
  summarise(
    n = n(),
    Share_n = sum(shared == 1, na.rm = TRUE),
    Share_percent = mean(shared, na.rm = TRUE) * 100,
    .groups = "drop"
  ) %>%
  arrange(Share_percent)
```

#### by participant

```{r}
df_long %>%
  group_by(response_id) %>%
  summarise(
    n_items = n(),
    Share_n = sum(shared == 1, na.rm = TRUE),
    Share_percent = mean(shared, na.rm = TRUE) * 100,
    .groups = "drop"
  )
```

```{r}
df_long %>%
  group_by(response_id) %>%
  summarise(
    Share_percent = mean(shared, na.rm = TRUE) * 100,
    .groups = "drop"
  ) %>%
  summarise(
    Mean = mean(Share_percent),
    SD = sd(Share_percent),
    Min = min(Share_percent),
    Max = max(Share_percent)
  )
```

#### by condition

```{r}
shared_by_condition <- df_long %>%
  count(
    condition,
    info_distribution,
    info_importance,
    shared
  ) %>%
  group_by(
    condition,
    info_distribution,
    info_importance
  ) %>%
  mutate(
    Percent = n / sum(n) * 100,
    Cell = paste0(n, " (", round(Percent, 1), "%)")
  ) %>%
  ungroup() %>%
  select(
    condition,
    info_distribution,
    info_importance,
    shared,
    Cell
  ) %>%
  pivot_wider(
    names_from = shared,
    values_from = Cell
  )

shared_by_condition
```

### table_info_sharing

```{r}
# table_info_sharing_data <- df_long %>%
#   count(
#     info_distribution,
#     info_importance,
#     item_response_label,
#     name = "n"
#   ) %>%
#   group_by(
#     info_distribution,
#     info_importance
#   ) %>%
#   mutate(
#     Percent = n / sum(n) * 100,
#     Cell = paste0(
#       n,
#       " (",
#       sprintf("%.1f", Percent),
#       "%)"
#     )
#   ) %>%
#   ungroup() %>%
#   select(
#     info_distribution,
#     info_importance,
#     item_response_label,
#     Cell
#   ) %>%
#   tidyr::pivot_wider(
#     names_from = item_response_label,
#     values_from = Cell
#   )
```

```{r}
# table_info_sharing_data <- df_long %>%
#   count(
#     info_distribution,
#     info_importance,
#     item_response_label,
#     name = "n"
#   ) %>%
#   group_by(
#     info_distribution,
#     info_importance
#   ) %>%
#   mutate(
#     Percent = n / sum(n) * 100,
#     Percent = round_half_up(Percent, 1),
#     Cell = paste0(
#       n,
#       " (",
#       sprintf("%.1f", Percent),
#       "%)"
#     )
#   ) %>%
#   ungroup() %>%
#   select(
#     info_distribution,
#     info_importance,
#     item_response_label,
#     Cell
#   ) %>%
#   pivot_wider(
#     names_from = item_response_label,
#     values_from = Cell
#   ) %>%
#   mutate(
#     `Information Type` = paste(
#       info_distribution,
#       info_importance,
#       sep = ", "
#     )
#   )
```

```{r}
# table_info_sharing <- table_info_sharing_data %>%
#   gt() %>%
#   cols_label(
#     `Information Type` = "Information Type",
#     Shared = md("Shared, *n* (%)"),
#     Withheld = md("Withheld, *n* (%)"),
#     Distorted = md("Distorted, *n* (%)")
#   ) %>%
#   cols_align(
#     align = "left",
#     columns = `Information Type`
#   ) %>%
#   cols_align(
#     align = "center",
#     columns = c(
#       Shared,
#       Withheld,
#       Distorted
#     )
#   ) %>%
#   tab_options(
#     table.font.names = "Times New Roman",
#     table.font.size = 12,
#     column_labels.font.weight = "bold",
#     data_row.padding = px(3)
#   )
# 
# table_info_sharing
```

### table_info_sharing_average

```{r}
participant_response_props <- df_long %>%
  group_by(
    response_id,
    condition,
    info_distribution,
    info_importance
  ) %>%
  summarise(
    Share = mean(item_response_label == "Share", na.rm = TRUE),
    Withhold = mean(item_response_label == "Withhold", na.rm = TRUE),
    Distort = mean(item_response_label == "Distort", na.rm = TRUE),
    .groups = "drop"
  )

participant_response_props
```

```{r}
info_sharing_descriptives <- participant_response_props %>%
  group_by(
    condition,
    info_distribution,
    info_importance
  ) %>%
  summarise(
    n = n(),

    Share_M = mean(Share, na.rm = TRUE),
    Share_SD = sd(Share, na.rm = TRUE),

    Withhold_M = mean(Withhold, na.rm = TRUE),
    Withhold_SD = sd(Withhold, na.rm = TRUE),

    Distort_M = mean(Distort, na.rm = TRUE),
    Distort_SD = sd(Distort, na.rm = TRUE),

    .groups = "drop"
  )

info_sharing_descriptives
```

```{r}
table_info_sharing_data <- info_sharing_descriptives %>%
  mutate(
    Share = paste0(
      format_stat(Share_M),
      " (",
      format_stat(Share_SD),
      ")"
    ),

    Withhold = paste0(
      format_stat(Withhold_M),
      " (",
      format_stat(Withhold_SD),
      ")"
    ),

    Distort = paste0(
      format_stat(Distort_M),
      " (",
      format_stat(Distort_SD),
      ")"
    ),

    `Information Type` = paste(
      info_distribution,
      info_importance,
      sep = ", "
    ),

    condition = dplyr::recode(
      condition,
      "individual-prosocial" = "Interindividual, Prosocial",
      "individual-hybrid" = "Interindividual, Hybrid",
      "individual-proself" = "Interindividual, Proself",
      "group-prosocial" = "Intergroup, Prosocial",
      "group-hybrid" = "Intergroup, Hybrid",
      "group-proself" = "Intergroup, Proself"
    ),

    `Information Type` = factor(
      `Information Type`,
      levels = c(
        "Common, Low",
        "Common, High",
        "Unique, Low",
        "Unique, High"
      )
    ),

    condition = factor(
      condition,
      levels = c(
        "Interindividual, Prosocial",
        "Interindividual, Hybrid",
        "Interindividual, Proself",
        "Intergroup, Prosocial",
        "Intergroup, Hybrid",
        "Intergroup, Proself"
      )
    )
  ) %>%
  arrange(
    condition,
    `Information Type`
  ) %>%
  select(
    condition,
    `Information Type`,
    n,
    Share,
    Withhold,
    Distort
  )
```

```{r}
table_info_sharing <- table_info_sharing_data %>%
  gt(
    groupname_col = "condition"
  ) %>%
  cols_label(
    `Information Type` = "Information Type",
    n = md("*n*"),
    Share = md("Share *M* (*SD*)"),
    Withhold = md("Withhold *M* (*SD*)"),
    Distort = md("Distort *M* (*SD*)")
  ) %>%
  cols_align(
    align = "left",
    columns = `Information Type`
  ) %>%
  cols_align(
    align = "center",
    columns = c(
      n,
      Share,
      Withhold,
      Distort
    )
  ) %>%
  tab_options(
    table.font.names = "Times New Roman",
    table.font.size = 12,
    column_labels.font.weight = "bold",
    row_group.font.weight = "bold",
    data_row.padding = px(3)
  )

table_info_sharing
```

```{r}
table_info_sharing_excel <- table_info_sharing_data %>%
  group_by(condition) %>%
  group_modify(
    ~ bind_rows(
      tibble(
        `Information Type` = as.character(.y$condition),
        n = "",
        Share = "",
        Withhold = "",
        Distort = ""
      ),
      .x %>%
        mutate(
          `Information Type` = as.character(`Information Type`),
          n = as.character(n)
        ) %>%
        select(
          `Information Type`,
          n,
          Share,
          Withhold,
          Distort
        )
    )
  ) %>%
  ungroup()
```

### diagnostic

```{r}
distortion_summary <- df_long %>%
  summarise(
    Total_responses = n(),
    Distorted_n = sum(
      item_response_label == "Distorted",
      na.rm = TRUE
    ),
    Distorted_pct = Distorted_n / Total_responses * 100
  )

distortion_summary
```

```{r}
distortion_by_condition <- df_long %>%
  group_by(condition) %>%
  summarise(
    Total_responses = n(),
    Distorted_n = sum(
      item_response_label == "Distorted",
      na.rm = TRUE
    ),
    Distorted_pct = Distorted_n / Total_responses * 100,
    .groups = "drop"
  )

distortion_by_condition
```

```{r}
info_sharing_by_condition <- df_long %>%
  count(
    condition,
    info_distribution,
    info_importance,
    item_response_label,
    name = "n"
  ) %>%
  group_by(
    condition,
    info_distribution,
    info_importance
  ) %>%
  mutate(
    Percent = n / sum(n) * 100,
    Percent = round_half_up(Percent, 1),
    Cell = paste0(
      n,
      " (",
      sprintf("%.1f", Percent),
      "%)"
    )
  ) %>%
  ungroup() %>%
  select(
    condition,
    info_distribution,
    info_importance,
    item_response_label,
    Cell
  ) %>%
  pivot_wider(
    names_from = item_response_label,
    values_from = Cell
  )

info_sharing_by_condition
```

## Measures

```{r}
vars_main <- c(
  "need_cog_mean",
  "dirty_dozen_narcissism",
  "dirty_dozen_psychopathy",
  "dirty_dozen_machiavellianism",
  "cooperation_mean"
)

# Count of missing values (NA)
df %>%
  summarise(
    across(
      all_of(vars_main),
      ~ sum(is.na(.x))
    )
  )
```

```{r}
control_table <- df_long %>%
  distinct(response_id, .keep_all = TRUE) %>%
  summarise(
    across(
      c(
        need_cog_mean,
        age
        # add other continuous controls here
      ),
      list(
        n = ~ sum(!is.na(.)),
        M = ~ mean(., na.rm = TRUE),
        SD = ~ sd(., na.rm = TRUE)
      )
    )
  )
```

## Correlations

apa_corr_matrix()

#### create sharing by information type

```{r}
participant_sharing_types <- df_long %>%
  group_by(
    response_id,
    info_distribution,
    info_importance
  ) %>%
  summarise(
    sharing_proportion = mean(shared, na.rm = TRUE),
    .groups = "drop"
  ) %>%
  mutate(
    sharing_type = paste(
      info_distribution,
      info_importance,
      sep = "_"
    )
  ) %>%
  select(
    response_id,
    sharing_type,
    sharing_proportion
  ) %>%
  pivot_wider(
    names_from = sharing_type,
    values_from = sharing_proportion,
    names_prefix = "sharing_"
  )
```

```{r}
df_participant <- df_long %>%
  distinct(response_id, .keep_all = TRUE)
```

```{r}
df_participant <- df_participant %>%
  left_join(
    participant_sharing_types,
    by = "response_id"
  )
```

#### corr_vars

```{r}
# proself is the reference category
```

```{r}
corr_vars <- c(
  "structure_num",
  "motivation_prosocial",
  "motivation_hybrid",

  "sharing_Common_Low",
  "sharing_Common_High",
  "sharing_Unique_Low",
  "sharing_Unique_High",

  "cooperation_mean",

  "age",
  "sex_num",
  "need_cog_mean",
  "dirty_dozen_narcissism",
  "dirty_dozen_psychopathy",
  "dirty_dozen_machiavellianism"
)

corr_labels <- c(
  structure_num = "Structure",
  motivation_prosocial = "Motivation: Prosocial",
  motivation_hybrid = "Motivation: Hybrid",

  sharing_Common_Low = "Common, Low",
  sharing_Common_High = "Common, High",
  sharing_Unique_Low = "Unique, Low",
  sharing_Unique_High = "Unique, High",

  cooperation_mean = "Self-Reported Cooperation",

  age = "Age",
  sex_num = "Sex",
  need_cog_mean = "Need for Cognition",
  dirty_dozen_narcissism = "Narcissism",
  dirty_dozen_psychopathy = "Psychopathy",
  dirty_dozen_machiavellianism = "Machiavellianism"
)
```

#### table_correlations

```{r}
table_correlations <- apa_corr_matrix(
  data = df_participant,
  vars = corr_vars,
  labels = corr_labels,
  type = "pearson",
  digits = 2,
  stars = TRUE,
  blank_upper = TRUE,
  blank_diag = TRUE,
  return = "table"
)

table_correlations_data <- table_correlations %>%
  tibble::rownames_to_column("Variable")

table_correlations_data <- table_correlations %>%
  tibble::rownames_to_column("Variable") %>%
  mutate(
    Variable = paste0(
      row_number(),
      ". ",
      Variable
    )
  )
```

```{r}
make_section_row <- function(label, table) {
  
  out <- as.list(
    rep("", ncol(table))
  )
  
  names(out) <- names(table)
  out$Variable <- label
  
  tibble::as_tibble(out)
}
```

```{r}
table_correlations_paper <- bind_rows(
  
  make_section_row(
    "Manipulations",
    table_correlations_data
  ),
  
  table_correlations_data %>%
    slice(1:3),
  
  make_section_row(
    "Information Sharing",
    table_correlations_data
  ),
  
  table_correlations_data %>%
    slice(4:7),
  
  make_section_row(
    "Cooperation",
    table_correlations_data
  ),
  
  table_correlations_data %>%
    slice(8),
  
  make_section_row(
    "Controls",
    table_correlations_data
  ),
  
  table_correlations_data %>%
    slice(9:n())
)
```

```{r}
table_correlations_gt <- table_correlations_paper %>%
  gt() %>%
  cols_label(
    Variable = "Variable"
  ) %>%
  cols_align(
    align = "left",
    columns = Variable
  ) %>%
  cols_align(
    align = "center",
    columns = -Variable
  ) %>%
  tab_options(
    table.font.names = "Times New Roman",
    table.font.size = 12,
    column_labels.font.weight = "bold",
    data_row.padding = px(3)
  )
```

## Control Variables by Conditions

```{r}
control_vars <- c(
  "age",
  "sex_num",
  "need_cog_mean",
  "dirty_dozen_narcissism",
  "dirty_dozen_psychopathy",
  "dirty_dozen_machiavellianism"
)

control_labels <- c(
  age = "Age",
  sex_num = "Sex (female = 1)",
  need_cog_mean = "Need for Cognition",
  dirty_dozen_narcissism = "Narcissism",
  dirty_dozen_psychopathy = "Psychopathy",
  dirty_dozen_machiavellianism = "Machiavellianism"
)
```

```{r}
control_descriptives_long <- df_participant %>%
  select(
    structure,
    motivation,
    all_of(control_vars)
  ) %>%
  pivot_longer(
    cols = all_of(control_vars),
    names_to = "Variable",
    values_to = "Value"
  ) %>%
  group_by(
    Variable,
    structure,
    motivation
  ) %>%
  summarise(
    n = sum(!is.na(Value)),
    M = mean(Value, na.rm = TRUE),
    SD = sd(Value, na.rm = TRUE),
    .groups = "drop"
  ) %>%
  mutate(
    Variable = recode(
      Variable,
      !!!control_labels
    ),

    Cell = paste0(
      format_stat(M),
      " (",
      format_stat(SD),
      ")"
    )
  )
```

```{r}
table_control_descriptives_data <- control_descriptives_long %>%
  mutate(
    Condition = paste(
      structure,
      motivation,
      sep = "_"
    )
  ) %>%
  select(
    Variable,
    Condition,
    Cell
  ) %>%
  pivot_wider(
    names_from = Condition,
    values_from = Cell
  )
```

```{r}
table_control_descriptives_data <- table_control_descriptives_data %>%
  mutate(
    Variable = factor(
      Variable,
      levels = c(
        "Age",
        "Sex (female = 1)",
        "Need for Cognition",
        "Narcissism",
        "Psychopathy",
        "Machiavellianism"
      )
    )
  ) %>%
  arrange(Variable)
```

```{r}
names(table_control_descriptives_data)
```

```{r}
table_control_descriptives <- table_control_descriptives_data %>%
  gt() %>%

  tab_spanner(
    label = "Interindividual",
    columns = c(
      Interindividual_Hybrid,
      Interindividual_Proself,
      Interindividual_Prosocial
    )
  ) %>%

  tab_spanner(
    label = "Intergroup",
    columns = c(
      Intergroup_Hybrid,
      Intergroup_Proself,
      Intergroup_Prosocial
    )
  ) %>%

  cols_label(
    Variable = "Variable",

    Interindividual_Hybrid = "Hybrid",
    Interindividual_Proself = "Proself",
    Interindividual_Prosocial = "Prosocial",

    Intergroup_Hybrid = "Hybrid",
    Intergroup_Proself = "Proself",
    Intergroup_Prosocial = "Prosocial"
  ) %>%

  cols_align(
    align = "left",
    columns = Variable
  ) %>%

  cols_align(
    align = "center",
    columns = -Variable
  ) %>%

  tab_options(
    table.font.names = "Times New Roman",
    table.font.size = 12,
    column_labels.font.weight = "bold",
    data_row.padding = px(3)
  )

table_control_descriptives
```

#### sample size

```{r}
df_participant %>%
  count(
    structure,
    motivation
  )
```

#### ANOVA

```{r}
contrasts(df_participant$structure) <- contr.sum(2)
contrasts(df_participant$motivation) <- contr.sum(3)
```

```{r}
control_anova_results <- purrr::map_dfr(
  control_vars,
  function(var) {

    formula <- as.formula(
      paste0(
        var,
        " ~ structure * motivation"
      )
    )

    model <- lm(
      formula,
      data = df_participant
    )

    residual_df <- df.residual(model)

    aov_table <- car::Anova(
      model,
      type = 3
    )

    aov_df <- as.data.frame(aov_table) %>%
      tibble::rownames_to_column("Effect")

    error_ss <- aov_df %>%
      filter(Effect == "Residuals") %>%
      pull(`Sum Sq`)

    aov_df %>%
      filter(
        Effect %in% c(
          "structure",
          "motivation",
          "structure:motivation"
        )
      ) %>%
      mutate(
        Variable = control_labels[[var]],

        residual_df = residual_df,

        partial_eta2 =
          `Sum Sq` /
          (`Sum Sq` + error_ss),

        Effect = recode(
          Effect,
          structure = "Structure",
          motivation = "Motivation",
          `structure:motivation` = "Structure × Motivation"
        )
      ) %>%
      select(
        Variable,
        Effect,
        Df,
        residual_df,
        `F value`,
        `Pr(>F)`,
        partial_eta2
      )
  }
)

control_anova_results
```

```{r}
table_control_anova_data <- control_anova_results %>%
  mutate(
    df = as.character(Df),

    F = format_stat(
      `F value`
    ),

    p = format_stat(
      `Pr(>F)`,
      p_value = TRUE
    ),

    partial_eta2 = format_stat(
      partial_eta2
    )
  ) %>%
  select(
    Variable,
    Effect,
    df,
    F,
    p,
    partial_eta2
  )
```

```{r}
table_control_anova_paper <- table_control_anova_data %>%
  rename(
    `Control Variable` = Variable,
    `Effect` = Effect,
    `df` = df,
    `F` = F,
    `p` = p,
    `ηp²` = partial_eta2
  )
```

#### post-hoc

##### age

```{r}
# Age model
age_model <- lm(
  age ~ structure * motivation,
  data = df_participant
)

# Estimated marginal means for all six cells
age_emm <- emmeans(
  age_model,
  ~ structure * motivation
)

age_emm
```

```{r}
# Structure simple effects within Motivation
age_structure_pairs <- emmeans(
  age_model,
  ~ structure | motivation
) %>%
  pairs(
    adjust = "holm"
  ) %>%
  summary(
    infer = c(TRUE, TRUE)
  ) %>%
  as.data.frame()
```

```{r}
# Motivation simple effects within Structure
age_motivation_pairs <- emmeans(
  age_model,
  ~ motivation | structure
) %>%
  pairs(
    adjust = "holm"
  ) %>%
  summary(
    infer = c(TRUE, TRUE)
  ) %>%
  as.data.frame()
```

```{r}
names(age_structure_pairs)
names(age_motivation_pairs)
```

```{r}
age_followups <- bind_rows(
  age_structure_pairs %>%
    mutate(
      Variable = "Age",
      Comparison = paste0(
        contrast,
        ", ",
        motivation
      )
    ),

  age_motivation_pairs %>%
    mutate(
      Variable = "Age",
      Comparison = paste0(
        contrast,
        ", ",
        structure
      )
    )
)

age_followups
```

```{r}
table_age_followups_data <- age_followups %>%
  mutate(
    Estimate = format_stat(estimate),
    SE = format_stat(SE),
    t = format_stat(t.ratio),
    CI = paste0(
      "[",
      format_stat(lower.CL),
      ", ",
      format_stat(upper.CL),
      "]"
    ),
    p = format_stat(
      p.value,
      p_value = TRUE
    )
  ) %>%
  select(
    Variable,
    Comparison,
    Estimate,
    SE,
    df,
    t,
    CI,
    p
  )

table_age_followups_data
```

##### structure

```{r}
names(table_control_anova_data)
```

```{r}
control_anova_results %>%
  filter(
    Variable == "Sex (female = 1)",
    Effect == "Structure"
  )
```

```{r}
# Direction of significant sex Structure effect
sex_by_structure <- df_participant %>%
  group_by(structure) %>%
  summarise(
    n = sum(!is.na(sex_num)),
    n_female = sum(sex_num == 1, na.rm = TRUE),
    pct_female = mean(sex_num, na.rm = TRUE) * 100,
    .groups = "drop"
  )

sex_by_structure
```

## Save to Workbook

```{r}
# Create the workbook
wb <- wb_workbook()
```

### table_demo_describe

```{r}
sheet_name <- "Describe"
table      <- table_demo_describe

wb$add_worksheet(sheet_name)

wb$add_data_table(
  sheet = sheet_name, 
  x = table
)
```

### table_demo_summary

```{r}
sheet_name <- "Summary"

table <- table_demo_summary %>%
  as_tibble()

wb$add_worksheet(sheet_name)

wb$add_data_table(
  sheet = sheet_name,
  x = table
)
```

### table_demo_tabyl

```{r}
sheet_name <- "Tabyl"
table      <- table_demo_tabyl %>% 
  as_tibble()

wb$add_worksheet(sheet_name)

wb$add_data_table(
  sheet = sheet_name, 
  x = table
)
```

### table_demo_purr

```{r}
sheet_name <- "Purr"
table      <- table_demo_purr[["_data"]]

wb$add_worksheet(sheet_name)

wb$add_data_table(
  sheet = sheet_name, 
  x = table
)
```

### table_continuous

```{r}
sheet_name <- "Continuous Descriptives"

wb$add_worksheet(sheet_name)

wb$add_data_table(
  sheet = sheet_name,
  x = table_continuous_data
)
```

### table_info_sharing

```{r}
sheet_name <- "Information Sharing"

wb$add_worksheet(sheet_name)

wb$add_data_table(
  sheet = sheet_name,
  x = table_info_sharing_excel
)
```

### table_correlations

```{r}
sheet_name <- "Coreelations"

wb$add_worksheet(sheet_name)

wb$add_data_table(
  sheet = sheet_name,
  x = table_correlations_paper
)
```

### table_control_descriptives_data

```{r}
sheet_name <- "Control Descriptives"

wb$add_worksheet(sheet_name)

wb$add_data_table(
  sheet = sheet_name,
  x = table_control_descriptives_data
)
```

### table_control_anova_paper

```{r}
sheet_name <- "Control ANOVAs"

wb$add_worksheet(sheet_name)

wb$add_data_table(
  sheet = sheet_name,
  x = table_control_anova_paper
)
```

### table_age_followups_data

```{r}
sheet_name <- "Follow up"

wb$add_worksheet(sheet_name)

wb$add_data_table(
  sheet = sheet_name,
  x = table_age_followups_data
)
```

### save file

```{r}
wb_save(
  wb, 
  file = "../tables/describe.xlsx"
)
```

### rm()

```{r}
# rm(table_demo_describe, table_demo_summary, table_demo_tabyl)
# rm(table)
# rm(wb, sheet_name)
# rm(clue_key, control_table, demographics, response_by_condition, shared_by_condition)
# rm(df, df_long, codebook_df_descriptives, codebook_df_long)
# rm(vars_main)
```

## End of Script

```{r}
print("end of script")
```
