---
title: "03-03_Strategies"
format: html
---

## Setup

```{r}
library(psych)
library(emmeans)
library(performance)
library(dplyr)
library(janitor)
library(tidyr)
```

```{r}
df <- readRDS("../data/df_descriptives.rds")
```

## EFA

Tutorial:

[**https://rpubs.com/pjmurphy/758265**](https://rpubs.com/pjmurphy/758265)

[*https://quantdev.ssri.psu.edu/tutorials/intro-basic-exploratory-factor-analysis*](https://quantdev.ssri.psu.edu/tutorials/intro-basic-exploratory-factor-analysis)

### Define variables

```{r}
strategy_items <- c(
  "q9_1_1",
  "q9_1_2",
  "q9_1_3",
  "q9_1_4",
  "q9_1_5",
  "q9_1_6",
  "q9_1_7",
  "q9_1_8",
  "q9_1_9",
  "q9_1_10",
  "q9_1_11",
  "q9_1_12",
  "q9_1_13"
)
```

```{r}
df_strategy <- df %>%
  select(all_of(strategy_items))
```

#### Check structure

```{r}
# str(df_strategy)
# 
# sapply(df_strategy, class)
# 
# sapply(df_strategy, function(x) sort(unique(x)))
```

#### Check number of participants in new df

```{r}
nrow(df_strategy)
```

```{r}
dplyr::n_distinct(df$prolific_pid)
```

#### Missingness

```{r}
# Two participants missing
strategy_missing <- tibble::tibble(
  item = strategy_items,
  n_valid = sapply(df_strategy, function(x) sum(!is.na(x))),
  n_missing = sapply(df_strategy, function(x) sum(is.na(x))),
  percent_missing = sapply(
    df_strategy,
    function(x) mean(is.na(x)) * 100
  )
)

strategy_missing
```

```{r}
# Two participants who missed all items
# Otherwise everyone completed the items
df <- df %>%
  mutate(
    strategy_n_answered = rowSums(!is.na(across(all_of(strategy_items))))
  )

table(df$strategy_n_answered)
```

```{r}
sum(complete.cases(df_strategy))
mean(complete.cases(df_strategy)) * 100
```

#### Remove missing cases

n=228

Two participants are missing so they will be removed from the dataset

```{r}
df_strategy <- df_strategy[
  complete.cases(df_strategy),
]
```

```{r}
dim(df_strategy)
```

### Summary / Descriptives

```{r}
df %>%
  select(all_of(strategy_items)) %>%
  summary()
```

```{r}
strategy_descriptives <- psych::describe(df_strategy)

strategy_descriptives
```

```{r}
strategy_item_audit <- psych::describe(df_strategy) %>%
  as.data.frame() %>%
  tibble::rownames_to_column("item") %>%
  tibble::as_tibble() %>%
  dplyr::select(
    item,
    n,
    mean,
    sd,
    median,
    min,
    max,
    skew,
    kurtosis
  )

strategy_missing <- tibble::tibble(
  item = names(df_strategy),
  missing_n = colSums(is.na(df_strategy)),
  missing_percent = colMeans(is.na(df_strategy)) * 100
)

strategy_item_audit <- strategy_item_audit %>%
  dplyr::left_join(
    strategy_missing,
    by = "item"
  ) %>%
  dplyr::mutate(
    dplyr::across(
      tidyselect::where(is.numeric),
      ~ round(.x, 2)
    )
  )

strategy_item_audit
```

```{r}
strategy_frequencies <- df_strategy %>%
  tidyr::pivot_longer(
    cols = everything(),
    names_to = "item",
    values_to = "response"
  ) %>%
  count(item, response, .drop = FALSE) %>%
  group_by(item) %>%
  mutate(
    percent = n / sum(n) * 100
  ) %>%
  ungroup()

strategy_frequencies
```

#### Visualization

```{r}
strategy_plot_data <- df_strategy %>%
  tidyr::pivot_longer(
    cols = everything(),
    names_to = "item",
    values_to = "response"
  ) %>%
  filter(!is.na(response)) %>%
  count(item, response) %>%
  group_by(item) %>%
  mutate(
    percent = 100 * n / sum(n)
  ) %>%
  ungroup()

ggplot2::ggplot(
  strategy_plot_data,
  ggplot2::aes(
    x = factor(response),
    y = percent
  )
) +
  ggplot2::geom_col() +
  ggplot2::facet_wrap(
    ~ item,
    scales = "free_y"
  ) +
  ggplot2::labs(
    x = "Response",
    y = "Percent",
    title = "Strategy Item Response Distributions"
  ) +
  ggplot2::theme_minimal()
```

### Correlations

Pick a correlation matrix and provide justification for selection.

##### pearson

```{r}
strategy_cor_pearson <- cor(
  df_strategy,
  use = "complete.obs",
  method = "pearson"
)

round(strategy_cor_pearson, 2)
```

```{r}
corrplot::corrplot(
  strategy_cor_pearson,
  method = "color",
  type = "lower",
  order = "hclust",
  addCoef.col = "black",
  tl.col = "black",
  tl.cex = 0.8,
  number.cex = 0.6
)
```

##### polychoric

```{r}
strategy_poly <- psych::polychoric(df_strategy)

strategy_cor_poly <- strategy_poly$rho

round(strategy_cor_poly, 2)
```

```{r}
corrplot::corrplot(
  strategy_cor_poly,
  method = "color",
  type = "lower",
  order = "hclust",
  addCoef.col = "black",
  tl.col = "black",
  tl.cex = 0.8,
  number.cex = 0.6
)
```

##### comparison

```{r}
cor(
  strategy_cor_pearson[lower.tri(strategy_cor_pearson)],
  strategy_cor_poly[lower.tri(strategy_cor_poly)]
)
```

#### assign correlation matrix

Looking for meaningful correlations to suggest a common factor. No relationships -\> no EFA.

```{r}
strategy_cor <- strategy_cor_poly
```

##### KMO

KMO evaluates whether the pattern of correlations is suitable for factor analysis. Very low values can suggest that the items do not share enough common variance.

Interpretation as per pjmurphy.

-   0.00 to 0.49 unacceptable
-   0.50 to 0.59 miserable
-   0.60 to 0.69 mediocre
-   0.70 to 0.79 middling
-   0.80 to 0.89 meritorious
-   0.90 to 1.00 marvelous

```{r}
kmo_strategy <- psych::KMO(strategy_cor)
```

```{r}
kmo_sentence <- sprintf(
  "The Kaiser-Meyer-Olkin measure indicated adequate sampling adequacy for factor analysis, with an overall MSA of %.2f and item-level MSA values ranging from %.2f to %.2f.",
  kmo_strategy$MSA,
  min(kmo_strategy$MSAi),
  max(kmo_strategy$MSAi)
)

kmo_sentence
```

##### Bartlett's test

A significant Bartlett test indicates that the correlation matrix differs from an identity matrix, which supports proceeding with a factor analysis. It should not be used as the only factorability criterion.

```{r}
bartlett_strategy <- psych::cortest.bartlett(
  strategy_cor,
  n = nrow(df_strategy)
)
```

```{r}
bartlett_sentence <- sprintf(
  "Bartlett's test of sphericity was significant, χ²(%d) = %.2f, p < .001, indicating that the correlation matrix differed significantly from an identity matrix.",
  bartlett_strategy$df,
  bartlett_strategy$chisq
)

bartlett_sentence
```

### Determine the Number of Factors

Use scree plot. Also parallel analysis.

#### parallel

Parallel analysis suggested four factors.

```{r}
psych::fa.parallel(
  df_strategy,
  fa = "fa",
  fm = "pa"
)
```

```{r}
# precomputed correlation matrix
psych::fa.parallel(
  strategy_cor,
  n.obs = nrow(df_strategy),
  fa = "fa",
  fm = "pa"
)
```

```{r}
set.seed(12345)

strategy_parallel <- psych::fa.parallel(
  strategy_cor,
  n.obs = nrow(df_strategy),
  fa = "fa",
  cor = "cor",
  plot = TRUE
)
```

#### scree plot

```{r}
psych::scree(
  strategy_cor,
  factors = TRUE,
  pc = FALSE
)
```

#### eigenvalues

```{r}
strategy_eigenvalues <- eigen(
  strategy_cor
)$values

strategy_eigen_table <- tibble::tibble(
  factor = seq_along(strategy_eigenvalues),
  eigenvalue = strategy_eigenvalues
)

strategy_eigen_table
```

When deciding on factor count, consider:

-   parallel analysis,
-   scree plot,
-   eigenvalues,
-   interpretability of the solution,
-   whether each retained factor has enough substantive indicators.

### Extraction Method

ML may be useful when item distributions and multivariate behavior are sufficiently close to the assumptions needed for ML-based estimation.

PAF is often a useful choice when normality is questionable. Promax is an oblique rotation, which allows factors to correlate. This aligns with the expectation that strategy dimensions may overlap rather than being independent.

```{r}
efa_1 <- psych::fa(
  strategy_cor,
  nfactors = 1,
  n.obs = nrow(df_strategy),
  rotate = "promax",
  fm = "pa"
)

efa_2 <- psych::fa(
  strategy_cor,
  nfactors = 2,
  n.obs = nrow(df_strategy),
  rotate = "promax",
  fm = "pa"
)

efa_3 <- psych::fa(
  strategy_cor,
  nfactors = 3,
  n.obs = nrow(df_strategy),
  rotate = "promax",
  fm = "pa"
)


efa_4 <- psych::fa(
  strategy_cor,
  nfactors = 4,
  n.obs = nrow(df_strategy),
  rotate = "promax",
  fm = "pa"
)
```

#### efa_1

```{r}
efa_1
```

#### efa_2

```{r}
efa_2
```

#### efa_3

```{r}
efa_3
```

#### efa_4

```{r}
efa_4
```

#### loadings

##### efa_2

```{r}
print(
  efa_2$loadings,
  cutoff = .20,
  sort = TRUE
)

round(
  efa_2$communality,
  2
)
```

##### efa_3

```{r}
print(
  efa_3$loadings,
  cutoff = .20,
  sort = TRUE
)

round(
  efa_3$communality,
  2
)
```

##### efa_4

```{r}
print(
  efa_4$loadings,
  cutoff = .20,
  sort = TRUE
)

round(
  efa_4$communality,
  2
)
```

##### compare loadings

```{r}
loadings_2 <- as.data.frame(unclass(efa_2$loadings)) %>%
  tibble::rownames_to_column("item")

loadings_3 <- as.data.frame(unclass(efa_3$loadings)) %>%
  tibble::rownames_to_column("item")

loadings_4 <- as.data.frame(unclass(efa_4$loadings)) %>%
  tibble::rownames_to_column("item")
```

```{r}
loadings_2 %>%
  dplyr::mutate(
    dplyr::across(
      where(is.numeric),
      ~ round(.x, 3)
    )
  )

loadings_3 %>%
  dplyr::mutate(
    dplyr::across(
      where(is.numeric),
      ~ round(.x, 3)
    )
  )

loadings_4 %>%
  dplyr::mutate(
    dplyr::across(
      where(is.numeric),
      ~ round(.x, 3)
    )
  )
```

##### compare items-level

```{r}
evaluate_loadings <- function(fit) {
  
  L <- abs(as.data.frame(unclass(fit$loadings)))
  
  tibble::tibble(
    item = rownames(L),
    primary_loading = apply(L, 1, max),
    second_loading = apply(
      L,
      1,
      function(x) sort(x, decreasing = TRUE)[2]
    ),
    loading_difference = primary_loading - second_loading,
    communality = fit$communality
  )
}

eval_2 <- evaluate_loadings(efa_2)
eval_3 <- evaluate_loadings(efa_3)
eval_4 <- evaluate_loadings(efa_4)

eval_2
eval_3
eval_4
```

## Remove q9_1_1

q9_1_1 was removed because it did not load meaningfully to the retained factor stucture.

```{r}
df_strategy_reduced <- df_strategy %>%
  dplyr::select(-q9_1_1)
```

### Correlation

```{r}
strategy_cor_reduced <- psych::polychoric(
  df_strategy_reduced
)$rho
```

### Evidence

```{r}
eigen(strategy_cor_reduced)$values

psych::scree(
  strategy_cor_reduced,
  factors = TRUE,
  pc = FALSE
)

set.seed(12345)

psych::fa.parallel(
  strategy_cor_reduced,
  n.obs = nrow(df_strategy_reduced),
  fa = "fa",
  cor = "cor"
)
```

```{r}
psych::fa.parallel(
  df_strategy_reduced,
  fa = "fa",
  cor = "poly",
  fm = "pa",
  plot = TRUE
)
```

Parallel analysis suggeted four factors,

### efa_2, efa_3, efa_4

```{r}
efa_2_reduced <- psych::fa(
  strategy_cor_reduced,
  nfactors = 2,
  n.obs = nrow(df_strategy_reduced),
  rotate = "promax",
  fm = "pa"
)

efa_3_reduced <- psych::fa(
  strategy_cor_reduced,
  nfactors = 3,
  n.obs = nrow(df_strategy_reduced),
  rotate = "promax",
  fm = "pa"
)

efa_4_reduced <- psych::fa(
  strategy_cor_reduced,
  nfactors = 4,
  n.obs = nrow(df_strategy_reduced),
  rotate = "promax",
  fm = "pa"
)
```

#### Inspect

```{r}
print(
  efa_2_reduced,
  sort = TRUE,
  cutoff = .30
)
```

```{r}
print(
  efa_3_reduced,
  sort = TRUE,
  cutoff = .30
)
```

```{r}
print(
  efa_4_reduced,
  sort = TRUE,
  cutoff = .30
)
```

### loadings

``` r
print(
  efa_paf$loadings,
  cutoff = .30
)
```

```{r}
loadings_2_reduced <- as.data.frame(
  unclass(efa_2_reduced$loadings)
) %>%
  tibble::rownames_to_column("item")

loadings_3_reduced <- as.data.frame(
  unclass(efa_3_reduced$loadings)
) %>%
  tibble::rownames_to_column("item")

loadings_4_reduced <- as.data.frame(
  unclass(efa_4_reduced$loadings)
) %>%
  tibble::rownames_to_column("item")
```

```{r}
loadings_2_reduced %>%
  dplyr::mutate(
    dplyr::across(where(is.numeric), ~ round(.x, 3))
  )

loadings_3_reduced %>%
  dplyr::mutate(
    dplyr::across(where(is.numeric), ~ round(.x, 3))
  )

loadings_4_reduced %>%
  dplyr::mutate(
    dplyr::across(where(is.numeric), ~ round(.x, 3))
  )
```

### factor correlations

Because Promax is oblique, factor correlations are expected and can be substantively meaningful.

```{r}
round(efa_2_reduced$Phi, 2)
round(efa_3_reduced$Phi, 2)
round(efa_4_reduced$Phi, 2)
```

### communalities

Low communalities may indicate that an item is poorly represented by the retained factor solution.

```{r}
round(efa_2_reduced$communality, 2)
round(efa_3_reduced$communality, 2)
round(efa_4_reduced$communality, 2)
```

When reviewing item loadings, examine:

-   the size of the primary loading,
-   whether the loading is theoretically coherent,
-   cross-loadings on other factors,
-   items that fail to load meaningfully anywhere,
-   factors represented by too few items.

Avoid making item-retention decisions from a single numerical cutoff alone.

If the parallel analysis and scree plot are ambiguous, fit nearby solutions and compare their interpretability. The final factor count should be based on statistical evidence and interpretability together.

## Reliability

### Factor 1

-   **Cronbach's α = .873**

-   95% CI approximately **\[.85, .90\]**

-   standardized α = **.872**

-   average inter-item correlation = **.460**

```{r}
factor1_items <- c(
  "q9_1_2",
  "q9_1_3",
  "q9_1_4",
  "q9_1_5",
  "q9_1_6",
  "q9_1_9",
  "q9_1_10",
  "q9_1_12"
)

psych::alpha(
  df_strategy_reduced %>%
    select(all_of(factor1_items)),
  check.keys = TRUE  # reverse q9_1_4
)
```

### Factor 2

-   **Cronbach's α = .712**

-   95% CI approximately **\[.65, .77\]**

-   standardized α = **.711**

-   average inter-item correlation = **.381**

Weakest item: q9_1_8

-   the smallest factor loading

-   by far the lowest communality

-   the weakest corrected item-total correlation

-   and deleting it increases alpha from `.712` to `.761`

Your Factor 2 items are:

-   `q9_1_7`: focused on information that ruled out **fewer graves**

-   `q9_1_11`: information that ruled out **fewer graves and others did not know**

-   `q9_1_13`: information that ruled out **fewer graves and others already knew**

-   [`q9_1_8`: information that **everyone already had access to**]{.underline}

```{r}
factor2_items <- c(
  "q9_1_7",
  "q9_1_8",
  "q9_1_11",
  "q9_1_13"
)

psych::alpha(
  df_strategy_reduced %>%
    select(all_of(factor2_items)),
    check.keys = TRUE 
)
```

## Remove q9_1_8

q9_1_8 was removed because:

-   weak factor loading

-   low communality

-   low corrected item-total correlation

-   improved reliability when removed

-   weaker conceptual fit with the other items in Factor 2

### Drop q9_1_8

```{r}
df_strategy_reduced8 <- df_strategy_reduced %>%
  dplyr::select(-q9_1_8)
```

### Correlation

```{r}
strategy_cor_reduced8 <- psych::polychoric(
  df_strategy_reduced8
)$rho
```

### EFA

```{r}
efa_2_reduced8 <- psych::fa(
  strategy_cor_reduced8,
  nfactors = 2,
  n.obs = nrow(df_strategy_reduced8),
  rotate = "promax",
  fm = "pa"
)

print(
  efa_2_reduced8$loadings,
  cutoff = .20,
  sort = TRUE
)
```

```{r}
round(efa_2_reduced8$Phi, 2)

round(efa_2_reduced8$communality, 2)
```

### Factor 2

```{r}
factor2_items_reduced8 <- c(
  "q9_1_7",
  "q9_1_11",
  "q9_1_13"
)

alpha_factor2_reduced8 <- psych::alpha(
  df_strategy_reduced8 %>%
    dplyr::select(dplyr::all_of(factor2_items_reduced8))
)

alpha_factor2_reduced8
```

Reliability should be interpreted together with item count, content coverage, and the EFA structure.

## Composite scores

### Factor 1

Because one of the items is negative, it will be reversed.

```{r}
df <- df %>%
  mutate(
    q9_1_4r = 6 - q9_1_4
  )
```

```{r}
factor1_items <- c(
  "q9_1_2",
  "q9_1_3",
  "q9_1_4r",
  "q9_1_5",
  "q9_1_6",
  "q9_1_9",
  "q9_1_10",
  "q9_1_12"
)
```

### Factor 2

```{r}
# Restating for continuity
factor2_items <- c(
  "q9_1_7",
  "q9_1_11",
  "q9_1_13"
)
```

### Calculate

```{r}
df <- df %>%
  mutate(
    strategy_factor1 = rowMeans(
      pick(all_of(factor1_items)),
      na.rm = FALSE
    ),
    
    strategy_factor2 = rowMeans(
      pick(all_of(factor2_items)),
      na.rm = FALSE
    )
  )
```

### Summary

```{r}
summary(
  df %>%
    select(
      strategy_factor1,
      strategy_factor2
    )
)

# should have 2 NA
```

### Describe

```{r}
psych::describe(
  df %>%
    select(
      strategy_factor1,
      strategy_factor2
    )
)
```

```{r}
df %>%
  select(
    strategy_factor1,
    strategy_factor2
  ) %>%
  tidyr::pivot_longer(
    everything(),
    names_to = "factor",
    values_to = "score"
  ) %>%
  ggplot2::ggplot(
    ggplot2::aes(x = score)
  ) +
  ggplot2::geom_histogram(
    bins = 15
  ) +
  ggplot2::facet_wrap(
    ~ factor,
    scales = "free_y"
  ) +
  ggplot2::theme_minimal() +
  ggplot2::labs(
    x = "Composite score",
    y = "Count",
    title = "Strategy Composite Distributions"
  )
```

## Correlation with other Measures

```{r}
str(df)
```

```{r}
df <- df %>%
  mutate(
    # Binary: Female = 0, Male = 1
    sex_num = case_when(
      sex == "Female" ~ 0,
      sex == "Male" ~ 1,
      TRUE ~ NA_real_
    ),

    # Ordered categories: use their existing order
    household_income_num =
      as.numeric(household_income_usd_us_participants_only),

    undergraduate_year_num =
      as.numeric(undergraduate_year_of_study)
  )
```

```{r}
strategy_factor_cor <- cor(
  df %>%
    select(
      strategy_factor1,
      strategy_factor2,
      need_cog_mean,
      dirty_dozen_narcissism,
      dirty_dozen_psychopathy, 
      dirty_dozen_machiavellianism, 
      cooperation_mean, 
      age, 
      sex_num, 
      household_income_num, 
      undergraduate_year_num
    ),
  use = "pairwise.complete.obs"
)
```

```{r}
# filter correlation matrix
strategy_correlations <- strategy_factor_cor[
  !rownames(strategy_factor_cor) %in%
    c("strategy_factor1", "strategy_factor2"),
  c("strategy_factor1", "strategy_factor2"),
  drop = FALSE
]

round_half_up(strategy_correlations, 2)
```

## Models Compare Manipulation

If a clear factor structure emerges, analyze the composite scores across the between-participant conditions.

### Factor 1

##### Cooperation

```{r}
strategy_factor1_model <- lm(
  strategy_factor1 ~
    structure * motivation +
    cooperation_mean,
  data = df
)

summary(strategy_factor1_model)
```

##### No cooperation

```{r}
strategy_factor1_model <- lm(
  strategy_factor1 ~
    structure * motivation,
  data = df
)

summary(strategy_factor1_model)
```

Diagnostics

```{r}
# performance::check_model(strategy_factor1_model)
# performance::check_collinearity(strategy_factor1_model)
```

Estimated marginal means

```{r}
strategy_factor1_emm <- emmeans(
  strategy_factor1_model,
  ~ structure * motivation
)

strategy_factor1_emm
```

Follow-up comparisons

```{r}
pairs(
  emmeans(
    strategy_factor1_model,
    ~ motivation | structure
  ),
  adjust = "holm"
)
```

### Factor 2

##### Cooperation

```{r}
strategy_factor2_model <- lm(
  strategy_factor2 ~
    structure * motivation +
    cooperation_mean,
  data = df
)

summary(strategy_factor2_model)
```

##### No Cooperation

```{r}
strategy_factor2_model <- lm(
  strategy_factor2 ~
    structure * motivation,
  data = df
)

summary(strategy_factor2_model)
```

Diagnostics

```{r}
# performance::check_model(strategy_factor2_model)
# performance::check_collinearity(strategy_factor2_model)
```

Estimated marginal means

```{r}
strategy_factor2_emm <- emmeans(
  strategy_factor2_model,
  ~ structure * motivation
)

strategy_factor2_emm
```

Follow-up comparisons

```{r}
pairs(
  emmeans(
    strategy_factor2_model,
    ~ motivation | structure
  ),
  adjust = "holm"
)
```

### controls

If the strategy analyses are intended to include the same retained controls as the primary outcome analyses, add them explicitly. Because the strategy analysis is exploratory, keep the control-variable rationale clear and consistent with the broader analysis plan.

```{r}
# strategy_factor1_model <- lm(
#   strategy_factor1 ~
#     structure * motivation +
#     RETAINED_CONTROL_1 +
#     RETAINED_CONTROL_2,
#   data = df_analysis
# )
```

## Repeated Measures Back-up

If the EFA does not produce an interpretable solution, the planned alternative is to retain strategy responses as repeated measures according to information importance and information distribution.

This requires a long-format dataset.

| Item      | Information importance | Distribution |
|-----------|------------------------|--------------|
| `q9_1_10` | High                   | Unique       |
| `q9_1_11` | Low                    | Unique       |
| `q9_1_12` | High                   | Common       |
| `q9_1_13` | Low                    | Common       |

From the item wording:

-   `q9_1_10`: ruled out **more graves** and others **did not know**

-   `q9_1_11`: ruled out **fewer graves** and others **did not know**

-   `q9_1_12`: ruled out **more graves** and others **already knew**

-   `q9_1_13`: ruled out **fewer graves** and others **already knew**

### Reshape data

```{r}
strategy_rm_long <- df %>%
  dplyr::select(
    prolific_pid,
    structure,
    motivation,
    q9_1_10,
    q9_1_11,
    q9_1_12,
    q9_1_13
  ) %>%
  dplyr::mutate(
    dplyr::across(
      c(q9_1_10, q9_1_11, q9_1_12, q9_1_13),
      haven::zap_labels
    )
  ) %>%
  tidyr::pivot_longer(
    cols = c(
      q9_1_10,
      q9_1_11,
      q9_1_12,
      q9_1_13
    ),
    names_to = "strategy_item",
    values_to = "strategy_response"
  )
```

### Label

If item names encode importance and distribution, create variables from the item names.

-   `strategy_common_high`
-   `strategy_common_low`
-   `strategy_unique_high`
-   `strategy_unique_low`

Key:

```{r}
strategy_lookup <- tibble::tribble(
  ~strategy_item, ~info_importance, ~info_distribution,
  "q9_1_10",      "High",           "Unique",
  "q9_1_11",      "Low",            "Unique",
  "q9_1_12",      "High",           "Common",
  "q9_1_13",      "Low",            "Common"
)
```

```{r}
strategy_rm_long <- strategy_rm_long %>%
  dplyr::left_join(
    strategy_lookup,
    by = "strategy_item"
  )
```

```{r}
strategy_rm_long <- strategy_rm_long %>%
  dplyr::mutate(
    info_importance = factor(
      info_importance,
      levels = c("High", "Low")
    ),
    info_distribution = factor(
      info_distribution,
      levels = c("Common", "Unique")
    )
  )
```

```{r}
table(
  strategy_rm_long$info_importance,
  strategy_rm_long$info_distribution
)
```

### Model

If `strategy_response` can reasonably be treated as continuous:

```{r}
strategy_rm_model <- lme4::lmer(
  strategy_response ~
    structure *
    motivation *
    info_importance *
    info_distribution +
    (1 | prolific_pid),
  data = strategy_rm_long,
  REML = FALSE
)
```

```{r}
performance::check_model(strategy_rm_model)

performance::check_singularity(strategy_rm_model)
```

```{r}
summary(strategy_rm_model)
```

### Omnibus and follow-up comparisons

```{r}
emmeans::joint_tests(strategy_rm_model)
```

Estimated marginal means:

```{r}
strategy_rm_emm <- emmeans(
  strategy_rm_model,
  ~ structure * motivation |
    info_importance * info_distribution
)

strategy_rm_emm
```

### Open-ended strategy responses

Create a separate object containing participant ID and the open-ended strategy response.

```{r}
strategy_text <- df_analysis %>%
  select(
    PROLIFIC_PID,
    strategy_open
  ) %>%
  filter(
    !is.na(strategy_open),
    str_trim(strategy_open) != ""
  )

nrow(strategy_text)
```

Inspect responses:

```{r}
strategy_text
```

Export for qualitative coding if desired:

```{r}
write.csv(
  strategy_text,
  "strategy_open_responses.csv",
  row.names = FALSE
)
```

#### Suggested qualitative coding structure

The open-ended responses are intended to provide context for the quantitative strategy analyses. A basic coding workflow could include:

1.  read all responses without coding,
2.  identify recurring strategy concepts,
3.  create an initial codebook,
4.  code responses consistently,
5.  revise definitions when categories overlap,
6.  summarize the frequency and content of themes,
7.  use representative excerpts only after verifying them directly against the source responses.

The coding should remain exploratory unless a formal qualitative methodology is added to the study.

## Export Workbook

### EFA

```{r}
# Create the workbook
wb <- wb_workbook()
```

#### strategy_missing

```{r}
sheet_name <- "strategy_missing"
table      <- strategy_missing

wb$add_worksheet(sheet_name)

wb$add_data_table(
  sheet = sheet_name, 
  x = table
)
```

#### strategy_descriptives

```{r}
sheet_name <- "strategy_descriptives"
table      <- strategy_descriptives

wb$add_worksheet(sheet_name)

wb$add_data_table(
  sheet = sheet_name, 
  x = table
)
```

#### strategy_item_audit

```{r}
sheet_name <- "strategy_item_audit"
table      <- strategy_item_audit

wb$add_worksheet(sheet_name)

wb$add_data_table(
  sheet = sheet_name, 
  x = table
)
```

#### strategy_frequencies

```{r}
sheet_name <- "strategy_frequencies"
table      <- strategy_frequencies

wb$add_worksheet(sheet_name)

wb$add_data_table(
  sheet = sheet_name, 
  x = table
)
```

#### strategy_cor_pearson

```{r}
wb <- save_output_to_workbook(
  "strategy_cor_pearson",
  strategy_cor_pearson
)
```

#### strategy_cor_poly

```{r}
wb <- save_output_to_workbook(
  "strategy_cor_poly",
  strategy_cor_poly
)
```

#### wb_save

```{r}
wb_save(
  wb, 
  file = "../tables/efa.xlsx"
)
```

## Save EFA and strategy analysis objects

```{r}
# Save only objects that exist in the final analysis path.

# saveRDS(efa_paf, "strategy_efa.rds")
# saveRDS(strategy_factor1_model, "strategy_factor1_model.rds")
# saveRDS(strategy_rm_model, "strategy_repeated_measures_model.rds")
```
