---
title: "03-01_InfoSharing"
format: html
---

## Setup

```{r setup, include=FALSE}
library(tidyverse)
library(afex)
library(lme4)
library(emmeans)
library(tibble)
library(DHARMa)
library(janitor)
library(openxlsx2)
library(papaja)

source("../_common.R")

run_model <- TRUE
```

```{r}
df_long <- readRDS("../data/df_long.rds")
```

Variables of interest for this analysis:

-   `prolific_pid`: participant identifier
-   `structure_num`: experimental structure condition
    -   interindividual = 0
    -   intergroup = 1
-   `motivation`: experimental motivation condition
    -   prosocial
    -   proself
    -   hybrid
-   `q7_3_1` through `q7_3_10`: Church's public-letter clues (Common information)
-   `q7_4_1` through `q7_4_10`: participant-only letter clues (Unique information)
-   control variables
    -   age
    -   sex_num
    -   need_cog_mean
    -   dirty_dozen_narcissism
    -   dirty_dozen_psychopathy
    -   dirty_dozen_machiavellianism

### Review Dataset

```{r}
# Variable names
names(df_long)
```

```{r}
# More about the variables
str(df_long)
```

```{r}
# Dataset dimensions
dim(df_long)
```

#### Missingness

```{r}
control_missingness_participant <- df_long %>%
  distinct(
    prolific_pid,
    age,
    sex_num,
    ethnicity_simplified,
    need_cog_mean,
    dirty_dozen_narcissism,
    dirty_dozen_psychopathy,
    dirty_dozen_machiavellianism,
    cooperation_mean
  ) %>%
  summarise(
    across(
      -prolific_pid,
      list(
        missing_n = ~ sum(is.na(.)),
        missing_pct = ~ mean(is.na(.)) * 100
      )
    )
  ) %>%
  pivot_longer(
    cols = everything(),
    names_to = c("Variable", ".value"),
    names_pattern = "^(.*)_(missing_n|missing_pct)$"
  ) %>%
  arrange(desc(missing_pct))

control_missingness_participant
```

### Assumptions

#### ✅Independence, Check IDs

included in model:

(1 \| prolific_pid) + (1 \| item_id)

```{r}
# Participant and item identifiers
dplyr::n_distinct(df_long$prolific_pid)
dplyr::n_distinct(df_long$item_id)
```

#### ✅Dichotomous DV Sharing

```{r}
# Raw information-sharing response
table(df_long$item_response_label, useNA = "ifany")
```

```{r}
# Binary outcome
table(df_long$shared, useNA = "ifany")
```

```{r}
# Double checking coding for shared
df_long %>%
  count(
    item_response_label,
    shared
  )
```

```{r}
1156+547
```

```{r}
# sharing rate
df_long %>%
  summarise(
    n_observations = n(),
    n_shared = sum(shared == 1, na.rm = TRUE),
    proportion_shared = mean(shared, na.rm = TRUE)
  )
```

#### ✅Appropriate DV

##### Data Cleaning: As Factors

```{r}
df_long <- df_long %>%
  mutate(
    prolific_pid = factor(prolific_pid),
    item_id = factor(item_id),
  )
```

```{r}
sort(unique(df_long$structure_num))
table(df_long$structure_num, useNA = "ifany")

sort(unique(df_long$sex_num))
table(df_long$sex_num, useNA = "ifany")
```

```{r}
# levels(df_long$structure_num)
levels(df_long$motivation)
levels(df_long$info_distribution)
levels(df_long$info_importance)
```

```{r}
str(df_long)
```

#### ✅Information Type

```{r}
# Clue characteristics
table(df_long$info_distribution, useNA = "ifany")
table(df_long$info_importance, useNA = "ifany")
```

```{r}
df_long %>%
  distinct(
    item_id,
    info_distribution,
    info_importance,
    graves_excluded,
    clue_number,
    clue_text
  ) %>%
  arrange(
    info_distribution,
    desc(info_importance),
    clue_number
  )
```

```{r}
df_long %>%
  distinct(
    item_id,
    info_distribution,
    info_importance
  ) %>%
  count(
    info_distribution,
    info_importance
  )
```

```{r}
sharing_by_clue <- df_long %>%
  group_by(
    info_distribution,
    info_importance
  ) %>%
  summarise(
    n = n(),
    n_shared = sum(shared == 1, na.rm = TRUE),
    proportion_shared = mean(shared, na.rm = TRUE),
    .groups = "drop"
  )

sharing_by_clue
```

```{r}
df_long %>%
  summarise(
    missing_shared = sum(is.na(shared)),
    missing_structure_num = sum(is.na(structure_num)),
    missing_motivation = sum(is.na(motivation)),
    missing_distribution = sum(is.na(info_distribution)),
    missing_importance = sum(is.na(info_importance)),
    missing_age = sum(is.na(age)),
    missing_sex_num = sum(is.na(sex_num))
  )
```

#### ✅Sample sizes per condition

```{r}
# Experimental conditions
table(df_long$structure_num, useNA = "ifany")
table(df_long$motivation, useNA = "ifany")
table(df_long$condition, useNA = "ifany")
```

```{r}
df_long %>%
  distinct(
    prolific_pid,
    structure_num,
    motivation
  ) %>%
  count(
    structure_num,
    motivation
  )
```

```{r}
sharing_by_condition <- df_long %>%
  group_by(
    structure_num,
    motivation,
    info_distribution,
    info_importance
  ) %>%
  summarise(
    n = n(),
    n_shared = sum(shared == 1, na.rm = TRUE),
    proportion_shared = mean(shared, na.rm = TRUE),
    .groups = "drop"
  )

sharing_by_condition
```

#### ✅Multicollinearity among predictors

No obvious redundancy among controls/predictors before modeling

correlations / contingency checks can be preliminary

## Control

```{r}
candidate_controls <- c(
  "age",
  "sex_num",
  "ethnicity_simplified",
  "need_cog_mean",
  "dirty_dozen_narcissism",
  "dirty_dozen_psychopathy",
  "dirty_dozen_machiavellianism",
  "cooperation_mean"
)
```

```{r}
control_missingness <- df_long %>%
  distinct(
    prolific_pid,
    across(any_of(candidate_controls))
  ) %>%
  summarise(
    across(
      any_of(candidate_controls),
      ~ sum(is.na(.))
    )
  )

control_missingness
```

```{r}
df_long %>%
  distinct(
    prolific_pid,
    across(any_of(candidate_controls))
  ) %>%
  select(
    all_of(candidate_controls)
  ) %>%
  sapply(class)
```

```{r}
df_long %>%
  distinct(
    prolific_pid,
    ethnicity_simplified
  ) %>%
  count(
    ethnicity_simplified,
    sort = TRUE
  )
```

```{r}
df_long %>%
  distinct(
    prolific_pid,
    sex_num
  ) %>%
  count(
    sex_num,
    sort = TRUE
  )
```

### data

```{r}
# Create data
control_data <- df_long %>%
  select(
    shared,
    info_distribution,
    info_importance,
    age,
    sex_num,
    ethnicity_simplified,
    need_cog_mean,
    dirty_dozen_narcissism,
    dirty_dozen_psychopathy,
    dirty_dozen_machiavellianism,
    prolific_pid,
    item_id
  ) %>%
  drop_na() %>%
  droplevels()
```

```{r}
# Standardize continuous variables
control_data <- control_data %>%
  mutate(
    age_z = as.numeric(scale(age)),
    need_cog_z = as.numeric(scale(need_cog_mean)),
    narcissism_z = as.numeric(scale(dirty_dozen_narcissism)),
    psychopathy_z = as.numeric(scale(dirty_dozen_psychopathy)),
    machiavellianism_z = as.numeric(
      scale(dirty_dozen_machiavellianism)
    )
  )
```

```{r}
control_data %>%
  summarise(
    n_observations = n(),
    n_participants = n_distinct(prolific_pid),
    n_items = n_distinct(item_id)
  )
```

### form

```{r}
#| eval: !expr run_model

model_controls <- mixed(
  shared ~
    info_distribution +
    info_importance +
    age_z +
    sex_num +
    ethnicity_simplified +
    need_cog_z +
    narcissism_z +
    psychopathy_z +
    machiavellianism_z +
    (1 | prolific_pid) +
    (1 | item_id),
  data = control_data,
  family = binomial(link = "logit"),
  method = "LRT",
  control = glmerControl(
    optimizer = "bobyqa",
    optCtrl = list(maxfun = 200000)
  )
)

saveRDS(
  model_controls,
  "../artifacts/model_infosharing_controls.rds"
  )
```

```{r}
#| eval: !expr load_artifacts

model_controls <- readRDS(
  "../artifacts/model_infosharing_controls.rds"
)
```

```{r}
model_controls$full_model@optinfo$conv
```

```{r}
model_controls$full_model@optinfo$warnings
```

```{r}
isSingular(
  model_controls$full_model,
  tol = 1e-4
)
```

```{r}
summary(model_controls$full_model)
```

```{r}
VarCorr(model_controls$full_model)
```

```{r}
set.seed(1234)

sim_res_controls <- simulateResiduals(
  fittedModel = model_controls$full_model,
  n = 1000
)
```

```{r}
plot(sim_res_controls)
```

```{r}
testUniformity(sim_res_controls)

testDispersion(sim_res_controls)

testOutliers(sim_res_controls)
```

```{r}
plotResiduals(
  sim_res_controls,
  control_data$info_distribution
)

plotResiduals(
  sim_res_controls,
  control_data$info_importance
)

plotResiduals(
  sim_res_controls,
  control_data$ethnicity_simplified
)

plotResiduals(
  sim_res_controls,
  control_data$age_z
)

plotResiduals(
  sim_res_controls,
  control_data$need_cog_z
)
```

#### ANOVA

```{r}
anova(model_controls)
```

```{r}
# coefficient information
coef_table <- as.data.frame(
  summary(model_controls$full_model)$coefficients
) %>%
  tibble::rownames_to_column("term") %>%
  mutate(
    OR = exp(Estimate),
    CI_low = exp(Estimate - 1.96 * `Std. Error`),
    CI_high = exp(Estimate + 1.96 * `Std. Error`)
  )

coef_table
```

```{r}
control_table <- coef_table

control_table <- control_table %>%
  mutate(
    b = format_stat(Estimate),
    SE = format_stat(`Std. Error`),
    LR_chi2 = "",
    p = format_stat(`Pr(>|z|)`, p_value = TRUE),
    OR_CI = paste0(
      format_stat(OR),
      " [",
      format_stat(CI_low),
      ", ",
      format_stat(CI_high),
      "]"
    )
  )
```

```{r}
# Likelihood ratio tests
control_lrt <- as.data.frame(
  anova(model_controls)
)

control_lrt <- control_lrt %>%
  mutate(
    LR_chisq = format_stat(Chisq),
    p = format_stat(`Pr(>Chisq)`, p_value = TRUE)
  )

control_lrt
```

```{r}
names(control_lrt)
```

```{r}
control_table$term
```

```{r}
control_row_map <- tibble::tribble(
  ~coef_term,             ~lrt_term,               ~Predictor,                  ~Section,
  "(Intercept)",          NA,                      "Intercept",                  "Intercept",
  "info_distribution1",   "info_distribution",     "Common (0) vs. Unique (1)", "Within-Participant Variables",
  "info_importance1",     "info_importance",       "Low (0) vs. High (1)",     "Within-Participant Variables",
  "age_z",                "age_z",                 "Age",                        "Control Variables",
  "sex_num",              "sex_num",               "Sex",                        "Control Variables",
  NA,                     "ethnicity_simplified",  "Ethnicity",                  "Control Variables",
  "need_cog_z",           "need_cog_z",            "Need for Cognition",         "Control Variables",
  "narcissism_z",         "narcissism_z",          "Narcissism",                 "Control Variables",
  "psychopathy_z",        "psychopathy_z",          "Psychopathy",               "Control Variables",
  "machiavellianism_z",   "machiavellianism_z",    "Machiavellianism",           "Control Variables"
)
```

```{r}
coef_for_table <- control_table %>%
  select(
    term,
    Estimate,
    `Std. Error`,
    OR,
    CI_low,
    CI_high
  )
```

```{r}
lrt_for_table <- control_lrt %>%
  tibble::rownames_to_column("lrt_term") %>%
  select(
    lrt_term,
    Chisq,
    `Pr(>Chisq)`
  )
```

```{r}
# join two
control_paper <- control_row_map %>%
  left_join(
    coef_for_table,
    by = c("coef_term" = "term")
  ) %>%
  left_join(
    lrt_for_table,
    by = "lrt_term"
  )

control_paper
```

```{r}
control_paper <- control_paper %>%
  mutate(
    Estimate_display = format_stat(Estimate),
    
    SE_display = format_stat(`Std. Error`),
    
    LR_chisq_display = format_stat(Chisq),
    
    p_display = format_stat(
      `Pr(>Chisq)`,
      p_value = TRUE
    ),
    
    OR_CI_display = if_else(
      is.na(OR),
      "",
      paste0(
        format_stat(OR),
        " [",
        format_stat(CI_low),
        ", ",
        format_stat(CI_high),
        "]"
      )
    )
  )
```

```{r}
# no intercept for LR
control_paper <- control_paper %>%
  mutate(
    LR_chisq_display = if_else(
      Predictor == "Intercept",
      "",
      LR_chisq_display
    ),
    p_display = if_else(
      Predictor == "Intercept",
      "",
      p_display
    )
  )
```

```{r}
# select columns
control_paper <- control_paper %>%
  select(
    Section,
    Predictor,
    Estimate = Estimate_display,
    SE = SE_display,
    `LR χ²` = LR_chisq_display,
    p = p_display,
    `OR [95% CI]` = OR_CI_display
  )
```

```{r}
control_paper
```

## Full Model

Age, Sex, NFC as control variables

### data

```{r}
full_model_data <- df_long %>%
  select(
    shared,
    structure,
    structure_num,
    motivation,
    info_distribution,
    info_importance,
    age,
    sex_num,
    need_cog_mean,
    prolific_pid,
    item_id
  ) %>%
  drop_na() %>% 
  droplevels() %>%
  mutate(
    age_z = as.numeric(scale(age)),
    need_cog_z = as.numeric(scale(need_cog_mean))
  )
```

```{r}
full_model_data %>%
  summarise(
    n_observations = n(),
    n_participants = n_distinct(prolific_pid),
    n_items = n_distinct(item_id)
  )
```

### form

```{r}
#| eval: !expr run_model

model_full <- mixed(
  shared ~
    structure_num *
    motivation *
    info_distribution *
    info_importance +
    age_z +
    sex_num +
    need_cog_z +
    (1 | prolific_pid) +
    (1 | item_id),
  data = full_model_data,
  family = binomial(link = "logit"),
  method = "LRT",
  control = glmerControl(
    optimizer = "bobyqa",
    optCtrl = list(maxfun = 200000)
  )
)

saveRDS(
  model_full,
  "../artifacts/model_infosharing_full.rds"
)
```

```{r}
#| eval: !expr load_artifacts

model_full <- readRDS(
   "../artifacts/model_infosharing_full.rds"
)
```

#### motivation level

```{r}
colnames(
  model.matrix(
    model_full$full_model
  )
)
```

```{r}
contrasts(
  model.frame(model_full$full_model)$motivation
)
```

#### emmeans

```{r}
#| eval: !expr run_model

table_emm_full <- emmeans(
  model_full,
  ~ structure_num * motivation | info_distribution * info_importance,
  type = "response"
)

saveRDS(
  table_emm_full,
  "../artifacts/emmeans_infosharing_full"
)

table_emm_full
```

```{r}
#| eval: !expr load_artifacts

table_emm_full <- readRDS(
  "../artifacts/emmeans_infosharing_full"
)
```

```{r}
table_emm_full_df <- as.data.frame(table_emm_full)
names(table_emm_full_df)
```

```{r}
table_emm_full_df <- table_emm_full_df %>%
  mutate(
    Estimate_CI = paste0(
      format_stat(prob),
      " [",
      format_stat(asymp.LCL),
      ", ",
      format_stat(asymp.UCL),
      "]"
    )
  )
```

```{r}
table_emm_full_df <- table_emm_full_df %>%
  arrange(
    match(info_distribution, c("Common", "Unique")),
    match(info_importance, c("Low", "High")),
    structure_num,
    match(motivation, c("Proself", "Hybrid", "Prosocial"))
  )
```

```{r}
names(table_emm_full_df)
```

```{r}
head(table_emm_full_df)
```

```{r}
table_emm_check1 <- table_emm_full_df %>%
  mutate(
    structure_label = case_when(
      structure_num == 0 ~ "individual",
      structure_num == 1 ~ "group"
    ),
    motivation_label = tolower(as.character(motivation))
  )
```

```{r}
unique(table_emm_check1$structure_num)
unique(table_emm_check1$structure_label)

unique(table_emm_check1$motivation)
unique(table_emm_check1$motivation_label)
```

```{r}
table_emm_check2 <- table_emm_check1 %>%
  select(
    info_distribution,
    info_importance,
    structure_label,
    motivation_label,
    Estimate_CI
  )
```

```{r}
names(table_emm_check2)

head(table_emm_check2)
```

```{r}
table_emm_check3 <- table_emm_check2 %>%
  pivot_wider(
    names_from = c(structure_label, motivation_label),
    values_from = Estimate_CI,
    names_sep = "_"
  )
```

```{r}
names(table_emm_check3)
```

```{r}
table_emm_full_export <- table_emm_check3 %>%
  select(
    info_distribution,
    info_importance,
    individual_proself,
    individual_hybrid,
    individual_prosocial,
    group_proself,
    group_hybrid,
    group_prosocial
  )
```

```{r}
table_emm_check2 %>%
  count(structure_label, motivation_label)
```

```{r}
table_emm_full_export <- table_emm_check3 %>%
  select(
    info_distribution,
    info_importance,
    individual_proself,
    individual_hybrid,
    individual_prosocial,
    group_proself,
    group_hybrid,
    group_prosocial
  )
```

```{r}
table_emm_full_export
```

#### figure 

```{r}
fig_emm_sm <- ggplot(
  table_emm_full_df,
  aes(
    x = structure_num,
    y = prob,
    fill = motivation
  )
) +
  geom_col(
    position = position_dodge(width = 0.8),
    width = 0.7,
    alpha = 0.5,
    color = "black",
    linewidth = 0.2
  ) +
  geom_errorbar(
    aes(
      ymin = asymp.LCL,
      ymax = asymp.UCL
    ),
    position = position_dodge(width = 0.8),
    width = 0.25,
    linewidth = 0.8
  ) +
  facet_grid(
    info_distribution ~ info_importance
  ) +
  scale_y_continuous(
    breaks = seq(0, 1, 0.2),
    limits = c(0, 1)
  ) +
  theme_apa() +
  theme(
    text = element_text(
      size = 12,
      family = "serif",
      color = "black"
    ),
    axis.title = element_text(
      size = 12,
      face = "plain",
      color = "black"
    ),
    axis.text = element_text(
      size = 11,
      face = "plain",
      color = "black"
    ),
    strip.text = element_text(
      size = 12,
      face = "plain",
      family = "serif"
    ),
    legend.title = element_text(
      size = 12,
      face = "plain"
    ),
    legend.text = element_text(
      size = 11,
      face = "plain"
    ),
    axis.ticks = element_line(
      color = "black",
      linewidth = 0.5
    ),
    axis.ticks.length = unit(0.10, "cm"),
    axis.line = element_line(
      color = "black"
    ),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    panel.border = element_blank(),
    panel.spacing = unit(0.8, "lines")
  ) +
  labs(
    x = "Structure",
    y = "Predicted Probability of Sharing",
    fill = "Motivation"
  )

fig_emm_sm
```

#### table

```{r}
full_coef <- as.data.frame(
  summary(model_full$full_model)$coefficients
) %>%
  tibble::rownames_to_column("coef_term") %>%
  mutate(
    OR = exp(Estimate),
    CI_low = exp(Estimate - 1.96 * `Std. Error`),
    CI_high = exp(Estimate + 1.96 * `Std. Error`)
  )
```

```{r}
full_coef$coef_term
```

```{r}
full_lrt <- as.data.frame(
  anova(model_full)
) %>%
  tibble::rownames_to_column("lrt_term")
```

```{r}
full_lrt
```

```{r}
contrasts(df_long$motivation)
```

motivation1 = Hybrid vs. Proself

motivation2 = Prosocial vs. Proself

```{r}
levels(df_long$motivation)
```

```{r}
# levels(df_long$structure_num)
# contrasts(df_long$structure_num)

levels(df_long$info_distribution)
contrasts(df_long$info_distribution)

levels(df_long$info_importance)
contrasts(df_long$info_importance)

# levels(df_long$sex_num)
# contrasts(df_long$sex_num)
```

```{r}
sort(unique(df_long$structure_num))
table(df_long$structure_num, useNA = "ifany")

sort(unique(df_long$sex_num))
table(df_long$sex_num, useNA = "ifany")
```

Structure: 0 = interindividual; 1 = intergroup

Motivation: Proself is reference, so motivation1 = Hybrid vs. Proself and motivation2 = Prosocial vs. Proself

Information distribution: Common is reference, so info_distribution1 = Unique vs. Common

Information importance: Low is reference, so info_importance1 = High vs. Low

Sex: 0 = male; 1 = female

##### map

```{r}
full_row_map <- tibble::tribble(
  ~coef_term, ~lrt_term, ~Predictor, ~Section,

  # Intercept
  "(Intercept)", NA, "Intercept", "Intercept",

  # Control Variables
  "age_z", "age_z",
  "Age",
  "Control Variables",
  
  "sex_num", "sex_num",
  "Sex (1 = female)",
  "Control Variables",

  "need_cog_z", "need_cog_z",
  "Need for Cognition",
  "Control Variables",

  # Between Manipulations
  "structure_num", "structure_num",
  "Individual (0) vs. Group (1)",
  "Between Manipulations",

  NA, "motivation",
  "Motivation",
  "Between Manipulations",

  "motivation1", NA,
  "Hybrid vs. Proself",
  "Between Manipulations",

  "motivation2", NA,
  "Prosocial vs. Proself",
  "Between Manipulations",

  # Within Manipulations
  "info_distribution1", "info_distribution",
  "Unique vs. Common",
  "Within Manipulations",

  "info_importance1", "info_importance",
  "High vs. Low",
  "Within Manipulations",

  # Two-way interactions
  NA, "structure_num:motivation",
  "structure × Motivation",
  "Interactions",

  "structure_num:motivation1", NA,
  "(Individual vs. Group) × (Hybrid vs. Proself)",
  "Interactions",

  "structure_num:motivation2", NA,
  "(Individual vs. Group) × (Prosocial vs. Proself)",
  "Interactions",

  "structure_num:info_distribution1", "structure_num:info_distribution",
  "Structure × Information Distribution",
  "Interactions",

  NA, "motivation:info_distribution",
  "Motivation × Information Distribution",
  "Interactions",

  "motivation1:info_distribution1", NA,
  "(Hybrid vs. Proself) × (Unique vs. Common)",
  "Interactions",

  "motivation2:info_distribution1", NA,
  "(Prosocial vs. Proself) × (Unique vs. Common)",
  "Interactions",

  "structure_num:info_importance1", "structure_num:info_importance",
  "Structure × Information Importance",
  "Interactions",

  NA, "motivation:info_importance",
  "Motivation × Information Importance",
  "Interactions",

  "motivation1:info_importance1", NA,
  "(Hybrid vs. Proself) × (High vs. Low)",
  "Interactions",

  "motivation2:info_importance1", NA,
  "(Prosocial vs. Proself) × (High vs. Low)",
  "Interactions",

  "info_distribution1:info_importance1", "info_distribution:info_importance",
  "Information Distribution × Information Importance",
  "Interactions",

  # Three-way interactions
  NA, "structure_num:motivation:info_distribution",
  "Structure × Motivation × Information Distribution",
  "Interactions",

  "structure_num:motivation1:info_distribution1", NA,
  "Structure × (Hybrid vs. Proself) × Information Distribution",
  "Interactions",

  "structure_num:motivation2:info_distribution1", NA,
  "Structure × (Prosocial vs. Proself) × Information Distribution",
  "Interactions",

  NA, "structure_num:motivation:info_importance",
  "Structure × Motivation × Information Importance",
  "Interactions",

  "structure_num:motivation1:info_importance1", NA,
  "Structure × (Hybrid vs. Proself) × Information Importance",
  "Interactions",

  "structure_num:motivation2:info_importance1", NA,
  "Structure × (Prosocial vs. Proself) × Information Importance",
  "Interactions",

  "structure_num:info_distribution1:info_importance1",
  "structure:info_distribution:info_importance",
  "Structure × Information Distribution × Information Importance",
  "Interactions",

  NA, "motivation:info_distribution:info_importance",
  "Motivation × Information Distribution × Information Importance",
  "Interactions",

  "motivation1:info_distribution1:info_importance1", NA,
  "(Hybrid vs. Proself) × Information Distribution × Information Importance",
  "Interactions",

  "motivation2:info_distribution1:info_importance1", NA,
  "(Prosocial vs. Proself) × Information Distribution × Information Importance",
  "Interactions",

  # Four-way interaction
  NA, "structure_num:motivation:info_distribution:info_importance",
  "Structure × Motivation × Information Distribution × Information Importance",
  "Interactions",

  "structure_num:motivation1:info_distribution1:info_importance1", NA,
  "Structure × (Hybrid vs. Proself) × Information Distribution × Information Importance",
  "Interactions",

  "structure_num:motivation2:info_distribution1:info_importance1", NA,
  "Structure × (Prosocial vs. Proself) × Information Distribution × Information Importance",
  "Interactions"
)
```

```{r}
full_paper <- full_row_map %>%
  left_join(
    full_coef %>%
      select(
        coef_term,
        Estimate,
        `Std. Error`,
        OR,
        CI_low,
        CI_high
      ),
    by = "coef_term"
  ) %>%
  left_join(
    full_lrt %>%
      select(
        lrt_term,
        Chisq,
        `Pr(>Chisq)`
      ),
    by = "lrt_term"
  )
```

```{r}
full_paper <- full_paper %>%
  mutate(
    Estimate_display = if_else(
      is.na(Estimate),
      "",
      format_stat(Estimate)
    ),

    SE_display = if_else(
      is.na(`Std. Error`),
      "",
      format_stat(`Std. Error`)
    ),

    LR_chisq_display = if_else(
      is.na(Chisq),
      "",
      format_stat(Chisq)
    ),

    p_display = if_else(
      is.na(`Pr(>Chisq)`),
      "",
      format_stat(`Pr(>Chisq)`, p_value = TRUE)
    ),

    OR_CI_display = if_else(
      is.na(OR),
      "",
      paste0(
        format_stat(OR),
        " [",
        format_stat(CI_low),
        ", ",
        format_stat(CI_high),
        "]"
      )
    )
  )
```

```{r}
full_paper <- full_paper %>%
  select(
    Section,
    Predictor,
    Estimate = Estimate_display,
    SE = SE_display,
    `LR χ²` = LR_chisq_display,
    p = p_display,
    `OR [95% CI]` = OR_CI_display
  )
```

```{r}
full_paper
```

```{r}
full_table_export <- bind_rows(
  
  # Intercept
  full_paper %>%
    filter(Section == "Intercept") %>%
    select(-Section),
  
  # Control Variables header
  tibble(
    Predictor = "Control Variables",
    Estimate = "",
    SE = "",
    `LR χ²` = "",
    p = "",
    `OR [95% CI]` = ""
  ),
  
  full_paper %>%
    filter(Section == "Control Variables") %>%
    select(-Section),
  
  # Between Manipulations header
  tibble(
    Predictor = "Between Manipulations",
    Estimate = "",
    SE = "",
    `LR χ²` = "",
    p = "",
    `OR [95% CI]` = ""
  ),
  
  full_paper %>%
    filter(Section == "Between Manipulations") %>%
    select(-Section),
  
  # Within Manipulations header
  tibble(
    Predictor = "Within Manipulations",
    Estimate = "",
    SE = "",
    `LR χ²` = "",
    p = "",
    `OR [95% CI]` = ""
  ),
  
  full_paper %>%
    filter(Section == "Within Manipulations") %>%
    select(-Section),
  
  # Interactions header
  tibble(
    Predictor = "Interactions",
    Estimate = "",
    SE = "",
    `LR χ²` = "",
    p = "",
    `OR [95% CI]` = ""
  ),
  
  full_paper %>%
    filter(Section == "Interactions") %>%
    select(-Section)
)
```

```{r}
full_table_export
```

#### convergence

```{r}
model_full$full_model@optinfo$conv

model_full$full_model@optinfo$warnings
```

#### singularity and random effects

```{r}
# Ideally, FALSE
isSingular(
  model_full$full_model,
  tol = 1e-4
)
```

#### estimated variance for repeated

```{r}
VarCorr(model_full$full_model)
```

#### diagnostics

```{r}
set.seed(1234)

sim_res_full <- simulateResiduals(
  fittedModel = model_full$full_model,
  n = 1000
)
```

```{r}
plot(sim_res_full)
```

```{r}
testUniformity(sim_res_full)

testDispersion(sim_res_full)

testOutliers(sim_res_full)
```

##### Outliers

DHARMa recommends at least 1,000 bootstrap replications for the more exact procedure.

```{r}
set.seed(1234)

testOutliers(
  sim_res_full,
  type = "bootstrap",
  nBoot = 1000
)
```

```{r}
outlier_test <- testOutliers(sim_res_full)
outlier_test
```

```{r}
residual_df <- full_model_data %>%
  mutate(
    dharma_resid = residuals(sim_res_full)
  )
```

```{r}
residual_df %>%
  arrange(dharma_resid) %>%
  select(
    prolific_pid,
    item_id,
    structure_num,
    motivation,
    info_distribution,
    info_importance,
    shared,
    dharma_resid
  ) %>%
  head(20)
```

```{r}
residual_df %>%
  arrange(desc(dharma_resid)) %>%
  select(
    prolific_pid,
    item_id,
    structure_num,
    motivation,
    info_distribution,
    info_importance,
    shared,
    dharma_resid
  ) %>%
  head(20)
```

```{r}
# Cluster by participant
residual_df %>%
  group_by(prolific_pid) %>%
  summarise(
    min_resid = min(dharma_resid, na.rm = TRUE),
    max_resid = max(dharma_resid, na.rm = TRUE),
    .groups = "drop"
  ) %>%
  arrange(min_resid)

residual_df %>%
  group_by(prolific_pid) %>%
  summarise(
    min_resid = min(dharma_resid, na.rm = TRUE),
    max_resid = max(dharma_resid, na.rm = TRUE),
    .groups = "drop"
  ) %>%
  arrange(desc(max_resid))
```

```{r}
# Cluster by item
residual_df %>%
  group_by(item_id) %>%
  summarise(
    mean_resid = mean(dharma_resid, na.rm = TRUE),
    min_resid = min(dharma_resid, na.rm = TRUE),
    max_resid = max(dharma_resid, na.rm = TRUE),
    .groups = "drop"
  ) %>%
  arrange(mean_resid)
```

```{r}
plot(sim_res_full)
```

```{r}
plotResiduals(
  sim_res_full,
  full_model_data$structure_num
)

plotResiduals(
  sim_res_full,
  full_model_data$motivation
)

plotResiduals(
  sim_res_full,
  full_model_data$info_distribution
)

plotResiduals(
  sim_res_full,
  full_model_data$info_importance
)
```

#### ANOVA

```{r}
anova(model_full)
```

#### coefficient output

```{r}
summary(model_full$full_model)
```

#### four panel models

##### HC

```{r}
#| eval: !expr run_model

lrt_high_common <- mixed(
  shared ~
    structure * motivation +
    sex_num +
    need_cog_z +
    (1 | prolific_pid) +
    (1 | item_id),
  data = full_model_data %>%
    filter(
      info_importance == "High",
      info_distribution == "Common"
    ),
  family = binomial(link = "logit"),
  method = "LRT",
  control = glmerControl(
    optimizer = "bobyqa",
    optCtrl = list(maxfun = 200000)
  )
)

saveRDS(
  lrt_high_common,
  "../artifacts/model_infosharing_lrt_high_common.rds"
)
```

```{r}
#| eval: !expr load_artifacts

lrt_high_common <- readRDS(
  "../artifacts/model_infosharing_lrt_high_common.rds"
)
```

##### HU

```{r}
#| eval: !expr run_model

lrt_high_unique <- mixed(
  shared ~
    structure_num * motivation +
    sex_num +
    need_cog_z +
    (1 | prolific_pid) +
    (1 | item_id),
  data = full_model_data %>%
    filter(
      info_importance == "High",
      info_distribution == "Unique"
    ),
  family = binomial(link = "logit"),
  method = "LRT",
  control = glmerControl(
    optimizer = "bobyqa",
    optCtrl = list(maxfun = 200000)
  )
)
saveRDS(
  lrt_high_unique,
  "../artifacts/model_infosharing_lrt_high_unique.rds"
)
```

```{r}
#| eval: !expr load_artifacts

lrt_high_unique <- readRDS(
  "../artifacts/model_infosharing_lrt_high_unique.rds"
)
```

##### LC

```{r}
#| eval: !expr run_model

lrt_low_common <- mixed(
  shared ~
    structure * motivation +
    sex_num +
    need_cog_z +
    (1 | prolific_pid) +
    (1 | item_id),
  data = full_model_data %>%
    filter(
      info_importance == "Low",
      info_distribution == "Common"
    ),
  family = binomial(link = "logit"),
  method = "LRT",
  control = glmerControl(
    optimizer = "bobyqa",
    optCtrl = list(maxfun = 200000)
  )
)
saveRDS(
  lrt_low_common,
  "../artifacts/model_infosharing_lrt_low_common.rds"
)
```

```{r}
#| eval: !expr load_artifacts

lrt_low_common <- readRDS(
  "../artifacts/model_infosharing_lrt_low_common.rds"
)
```

##### LU

```{r}
#| eval: !expr run_model

lrt_low_unique <- mixed(
  shared ~
    structure_num * motivation +
    sex_num +
    need_cog_z +
    (1 | prolific_pid) +
    (1 | item_id),
  data = full_model_data %>%
    filter(
      info_importance == "Low",
      info_distribution == "Unique"
    ),
  family = binomial(link = "logit"),
  method = "LRT",
  control = glmerControl(
    optimizer = "bobyqa",
    optCtrl = list(maxfun = 200000)
  )
)

saveRDS(
  lrt_low_unique,
  "../artifacts/model_infosharing_lrt_low_unique.rds"
)
```

```{r}
#| eval: !expr load_artifacts

lrt_low_unique <- readRDS(
  "../artifacts/model_infosharing_lrt_low_unique.rds"
)
```

##### ANOVA

```{r}
lrt_high_common
lrt_high_unique
lrt_low_common
lrt_low_unique
```

```{r}
anova(lrt_high_common)
anova(lrt_high_unique)
anova(lrt_low_common)
anova(lrt_low_unique)
```

#### emmeans

pick one....

```{r}
#| eval: !expr run_model

motivation_by_importance <- emmeans(
  model_full,
  ~ motivation | info_importance,
  type = "response"
)

saveRDS(
  motivation_by_importance,
  "../artifacts/emmeans_infosharing_motivation_by_importance.rds"
)

motivation_by_importance
```

```{r}
#| eval: !expr load_artifacts

motivation_by_importance <- readRDS(
  "../artifacts/emmeans_infosharing_motivation_by_importance.rds"
)
```

```{r}
pairs(
  motivation_by_importance,
  adjust = "holm"
)
```

## Simplified Model

```{r}
simple_model_data <- df_long %>%
  select(
    shared,
    structure,
    motivation,
    info_distribution,
    info_importance,
    prolific_pid,
    item_id
  ) %>%
  drop_na() %>% 
  droplevels() 
```

```{r}
simple_model_data %>%
  summarise(
    n_observations = n(),
    n_participants = n_distinct(prolific_pid),
    n_items = n_distinct(item_id)
  )
```

```{r}
#| eval: !expr run_model

model_simple <- mixed(
  shared ~
    structure_num *
    motivation *
    info_distribution *
    info_importance +
    need_cog_z +
    (1 | prolific_pid) +
    (1 | item_id),
  data = full_model_data,
  family = binomial(link = "logit"),
  method = "LRT",
  control = glmerControl(
    optimizer = "bobyqa",
    optCtrl = list(maxfun = 200000)
  )
)

saveRDS(
  model_simple,
  "../artifacts/model_infosharing_simple.rds"
)
```

```{r}
#| eval: !expr load_artifacts

model_simple <- readRDS(
  "../artifacts/model_infosharing_simple.rds"
)
```

## Export to Excel

Predicted Probability of Sharing Clues by Condition

Binomial Regression Examining the Influence of Motivation and Structure on Intention to Share Information

Structure, Motivation, and Interaction by Information Importance and Information Distribution

Figure of panels

Pairwise Comparisions

### Create workbook

```{r}
wb <- wb_workbook()
```

### Tables

```{r}
# Predicted Probability of Sharing Clues by Condition
wb <- save_output_to_workbook(
  sheet_name = "Emmeans by Condition",
  output = table_emm_full_export,
  wb = wb
)

# binomial controls
wb <- save_output_to_workbook(
  sheet_name = "Binomial Controls",
  output = control_paper,
  wb = wb
)

# predicted probability of sharing clues by condition
wb <- save_output_to_workbook(
  sheet_name = "Emmeans Full",
  output = table_emm_full_export,
  wb = wb
)

# full model
wb <- save_output_to_workbook(
  sheet_name = "Binomial Full",
  output = full_table_export,
  wb = wb
)
```

```{r}
wb <- save_figure_to_workbook(
  wb = wb,
  sheet_name = "Figure",
  figure_file = "../figures/InfoSharing_EstProb.png",
  plot_obj = fig_emm_sm,
  width = 8,
  height = 6,
  dpi = 300
)
```

### Save

```{r}
wb_save(wb, file = "../tables/infosharing.xlsx", overwrite = TRUE)
```

## End

```{r}
print("end of script")
```
