---
title: "03-02_Cooperation"
format: html
---

## Setup

```{r setup, include=FALSE}
library(tidyverse)
library(car)
library(performance)
library(emmeans)
library(parameters)
library(broom)
library(gt)
library(openxlsx2)
library(dplyr)
library(tibble)
library(papaja)

source("../_common.R")

run_model <- TRUE
```

```{r}
df <- readRDS("../data/df_full.rds")
```

### Expected variables

This template assumes a cleaned dataset called `df` containing variables similar to:

-   `prolific_pid`
-   `cooperation_mean`
-   `structure`
-   `motivation`
-   `age`
-   `sex_num`
-   `household_income_usd_us_participants_only`
-   `ethnicity_simplified`
-   `need_cog_mean`
-   `dirty_dozen_machiavellianism`
-   `dirty_dozen_narcissism`
-   `dirty_dozen_psychopathy`

### Confirm variable coding

```{r}
str(
  df %>%
    select(
      prolific_pid,
      cooperation_mean,
      structure,
      motivation, 
      cooperation_mean,
      age,
      sex_num,
      household_income_usd_us_participants_only,
      ethnicity_simplified,
      need_cog_mean,
      dirty_dozen_machiavellianism,
      dirty_dozen_narcissism,
      dirty_dozen_psychopathy
    )
)
```

Set factor ordering explicitly.

```{r}
levels(df$structure)
levels(df$motivation)

table(df$structure, useNA = "ifany")
table(df$motivation, useNA = "ifany")
```

Standardize age

```{r}
df <- df %>%
  mutate(
    age_z = as.numeric(scale(age))
  )
```

The motivation level order is especially important for planned contrasts.

### Inspect cooperation variable

```{r}
summary(df$cooperation_mean)

mean(df$cooperation_mean, na.rm = TRUE)
sd(df$cooperation_mean, na.rm = TRUE)
```

### Distribution

```{r}
ggplot(df, aes(x = cooperation_mean)) +
  geom_histogram(bins = 30) +
  labs(
    x = "Self-reported cooperation",
    y = "Frequency",
    title = "Distribution of Cooperation Scores"
  )
```

```{r}
ggplot(df, aes(sample = cooperation_mean)) +
  stat_qq() +
  stat_qq_line() +
  labs(
    title = "Q-Q Plot for Cooperation Scores"
  )
```

The distribution of the raw outcome is informative, but the assumptions of a linear model concern the residuals from the fitted model more directly.

### Descriptive statistics by condition

```{r}
cooperation_descriptives <- df %>%
  group_by(structure, motivation) %>%
  summarise(
    n = n(),
    mean = mean(cooperation_mean, na.rm = TRUE),
    sd = sd(cooperation_mean, na.rm = TRUE),
    median = median(cooperation_mean, na.rm = TRUE),
    min = min(cooperation_mean, na.rm = TRUE),
    max = max(cooperation_mean, na.rm = TRUE),
    .groups = "drop"
  )

cooperation_descriptives
```

If participants have one observation each, `n()` is participant count.

### differences by manipulation

```{r}
df %>%
  group_by(motivation) %>%
  summarise(
    n = sum(!is.na(cooperation_mean)),
    mean = mean(cooperation_mean, na.rm = TRUE),
    sd = sd(cooperation_mean, na.rm = TRUE),
    min = min(cooperation_mean, na.rm = TRUE),
    max = max(cooperation_mean, na.rm = TRUE),
    .groups = "drop"
  )
```

```{r}
cooperation_model <- lm(
  cooperation_mean ~ structure * motivation,
  data = df
)

anova(cooperation_model)
```

### Visualize condition means

```{r}
ggplot(
  cooperation_descriptives,
  aes(
    x = motivation,
    y = mean,
    group = structure,
    linetype = structure
  )
) +
  geom_point() +
  geom_line() +
  labs(
    x = "Motivation",
    y = "Mean cooperation",
    linetype = "Structure"
  ) +
  theme_classic()
```

This plot is descriptive only. Inferential conclusions should come from the fitted model and planned contrasts.

## Control

The planned potential controls are:

-   age,
-   sex_num,
-   household income (U.S. participants only),
-   race/ethnicity,
-   Need for Cognition,
-   Machiavellianism,
-   narcissism,
-   psychopathy.

### Missingness

Many participants (\>90) are missing household income, so it will not continue in the modeling.

```{r}
df %>%
  summarise(
    across(
      c(
        cooperation_mean,
        age,
        sex_num,
        household_income_usd_us_participants_only,
        ethnicity_simplified,
        need_cog_mean,
        dirty_dozen_machiavellianism,
        dirty_dozen_narcissism,
        dirty_dozen_psychopathy
      ),
      ~ sum(is.na(.x))
    )
  )
```

### Sparse categorical variables

```{r}
df %>% count(sex_num, sort = TRUE)
df %>% count(ethnicity_simplified, sort = TRUE)
```

If categories are combined, document the rule and preserve the original variable.

### Model

The analysis plan proposes screening controls before testing the experimental predictors.

```{r}
cooperation_control_model <- lm(
  cooperation_mean ~
    age +
    sex_num +
    # household_income_usd_us_participants_only +  # missing ~90 
    ethnicity_simplified +
    need_cog_mean +
    dirty_dozen_machiavellianism +
    dirty_dozen_narcissism +
    dirty_dozen_psychopathy,
  data = df
)

summary(cooperation_control_model)
```

```{r}
car::Anova(
  cooperation_control_model,
  type = 2
)
```

A table of coefficients can be useful for reviewing the screening model.

```{r}
parameters::model_parameters(cooperation_control_model)
```

Record the controls that meet the planned retention rule rather than relying on automatic variable-selection procedures.

### Preliminary diagnostics for the control model

```{r}
performance::check_model(cooperation_control_model)
```

Check collinearity among predictors:

```{r}
performance::check_collinearity(cooperation_control_model)
```

Potential issues to inspect include:

-   strong nonlinearity,
-   non-constant residual variance,
-   influential observations,
-   unusually non-normal residuals,
-   high multicollinearity.

#### export

```{r}
control_model_cooperation_table <- broom::tidy(
  cooperation_control_model,
  conf.int = TRUE
) %>%
  mutate(
    Predictor = dplyr::recode(
      term,
      "(Intercept)" = "Intercept",
      "Age" = "Age",
      "sex_binary" = "Sex",
      "SES" = "SES",
      "ethnicity_binary" = "Ethnicity",
      "NeedCog_Mean" = "Need for Cognition",
      "DirtyDozen_Narcissism" = "Narcissism",
      "DirtyDozen_Psychopathy" = "Psychopathy",
      "DirtyDozen_Machiavellianism" = "Machiavellianism"
    ),
    Estimate = format_stat(estimate),
    SE = format_stat(std.error),
    `95% CI` = paste0(
      "[",
      format_stat(conf.low),
      ", ",
      format_stat(conf.high),
      "]"
    ),
    p = format_stat(p.value, p_value = TRUE)
  ) %>%
  select(
    Predictor,
    Estimate,
    SE,
    `95% CI`,
    p
  )
```

## Full Model

The base template below includes the structure by motivation interaction. Remove terms only if the final analytical plan calls for a simpler model.

```{r}
h2_model <- lm(
  cooperation_mean ~
    structure * motivation +
    age_z + 
    sex_num + 
    dirty_dozen_machiavellianism,
  data = df
)

summary(h2_model)
```

### Model assumptions

#### Standard diagnostic plots

```{r}
par(mfrow = c(2, 2))
plot(h2_model)
par(mfrow = c(1, 1))
```

#### Performance package diagnostics

```{r}
performance::check_model(h2_model)
```

#### Collinearity

```{r}
performance::check_collinearity(h2_model)
```

#### Residual normality

```{r}
residuals_h2 <- residuals(h2_model)

hist(residuals_h2)
qqnorm(residuals_h2)
qqline(residuals_h2)
```

For moderate sample sizes, mild deviations from residual normality may not be consequential. Consider the degree and pattern of departure together with leverage and heteroskedasticity rather than relying on a single formal normality test.

#### Influence diagnostics

```{r}
# Cook's distance
cooks_d <- cooks.distance(h2_model)

summary(cooks_d)
```

```{r}
plot(
  cooks_d,
  type = "h",
  ylab = "Cook's distance",
  xlab = "Observation"
)
```

A commonly used descriptive reference line is `4 / n`, although observations exceeding it should be investigated rather than automatically removed.

```{r}
# abline(
#   h = 4 / nrow(model.frame(h2_model)),
#   lty = 2
# )
```

Identify potentially influential rows:

```{r}
which(
  cooks_d > 4 / nrow(model.frame(h2_model))
)
```

### Omnibus effects

If using Type III tests, ensure the contrast coding is appropriate for the intended interpretation.

```{r}
h2_type3_data <- df %>%
  select(
    cooperation_mean,
    structure,
    motivation,
    age_z,
    sex_num,
    dirty_dozen_machiavellianism
  ) %>%
  drop_na()
```

```{r}
contrasts(h2_type3_data$structure) <- contr.sum(2)
contrasts(h2_type3_data$motivation) <- contr.sum(3)
```

```{r}
h2_model_type3 <- lm(
  cooperation_mean ~
    structure * motivation +
    age_z +
    sex_num +
    dirty_dozen_machiavellianism,
  data = h2_type3_data
)
```

```{r}
# Optional sum-to-zero contrasts for Type III tests
# options(contrasts = c("contr.sum", "contr.poly"))

h2_anova <- car::Anova(
  h2_model_type3,
  type = 3
)

h2_anova
```

If the interaction is meaningful, follow-up comparisons should reflect that interaction rather than interpreting only the marginal main effects.

### Estimated marginal means

#### Motivation overall

```{r}
h2_motivation_emm <- emmeans(
  h2_model,
  ~ motivation
)

h2_motivation_emm
```

#### Motivation within structure

```{r}
h2_emm_by_structure <- emmeans(
  h2_model,
  ~ motivation | structure
)

h2_emm_by_structure
```

## Ha & Hb: Planned comparisons

The planned hypotheses are:

-   H2a: Prosocial cooperation is higher than Proself cooperation.
-   H2b: Hybrid cooperation is higher than Proself cooperation.

If the factor levels are ordered as:

1.  Proself
2.  Hybrid
3.  Prosocial

then the following contrasts compare Prosocial and Hybrid with Proself.

```{r}
levels(df$motivation)
```

```{r}
h2_planned_contrasts <- contrast(
  h2_motivation_emm,
  method = list(
    "Prosocial vs Proself" = c(-1, 1, 0),
    "Hybrid vs Proself" = c(-1, 0, 1)
  ),
  adjust = "holm"
)

summary(
  h2_planned_contrasts,
  infer = TRUE
)
```

If the structure by motivation interaction is important, run the planned contrasts within structure instead:

```{r}
h2_planned_by_structure <- contrast(
  h2_emm_by_structure,
  method = list(
    "Prosocial vs Proself" = c(-1, 1, 0),
    "Hybrid vs Proself" = c(-1, 0, 1)
  ),
  adjust = "holm"
)

summary(
  h2_planned_by_structure,
  infer = TRUE
)
```

Check contrast direction carefully. Positive estimates should correspond to the condition named first being higher than the comparison condition under this coding.

### Optional pairwise comparisons

If all pairwise comparisons are useful for exploratory interpretation:

```{r}
pairs(
  h2_motivation_emm,
  adjust = "holm"
)
```

```{r}
h2_motivation_pairs <- emmeans(
  h2_model,
  ~ motivation
) %>%
  pairs(adjust = "holm")

h2_motivation_pairs
```

```{r}
h2_motivation_pairs_df <- as.data.frame(
  summary(
    h2_motivation_pairs,
    infer = c(TRUE, TRUE)
  )
)
```

```{r}
h2_motivation_pairs_table <- h2_motivation_pairs_df %>%
  mutate(
    Comparison = case_when(
      contrast == "Proself - Hybrid" ~
        "Proself vs. Hybrid",
      
      contrast == "Proself - Prosocial" ~
        "Proself vs. Prosocial",
      
      contrast == "Hybrid - Prosocial" ~
        "Hybrid vs. Prosocial",
      
      TRUE ~ contrast
    ),
    
    `Difference [95% CI]` = paste0(
      format_stat(estimate),
      " [",
      format_stat(lower.CL),
      ", ",
      format_stat(upper.CL),
      "]"
    ),
    
    p = format_stat(
      p.value,
      p_value = TRUE
    )
  ) %>%
  select(
    Comparison,
    `Difference [95% CI]`,
    p
  )
```

Planned contrasts should remain the primary tests for H2a and H2b if those are the hypotheses specified in advance.

```{r}
h2_joint_tests <- emmeans::joint_tests(h2_model)

h2_joint_tests
```

### Estimated means table

```{r}
h2_emm_table <- as.data.frame(
  emmeans(
    h2_model,
    ~ motivation | structure
  )
)

h2_emm_table
```

### Planned contrast table

```{r}
h2_contrast_table <- as.data.frame(
  summary(
    h2_planned_contrasts,
    infer = TRUE
  )
)

h2_contrast_table
```

### Figure with model-estimated means

```{r}
h2_plot_data <- as.data.frame(
  emmeans(
    h2_model,
    ~ motivation * structure
  )
)

h2_plot_data
```

```{r}
ggplot(
  h2_plot_data,
  aes(
    x = motivation,
    y = emmean,
    group = structure,
    linetype = structure
  )
) +
  geom_point(position = position_dodge(width = 0.15)) +
  geom_line(position = position_dodge(width = 0.15)) +
  geom_errorbar(
    aes(
      ymin = lower.CL,
      ymax = upper.CL
    ),
    width = 0.08,
    position = position_dodge(width = 0.15)
  ) +
  labs(
    x = "Motivation",
    y = "Estimated cooperation",
    linetype = "Structure"
  ) +
  theme_classic()
```

## Sensitivity checks if assumptions are problematic

If there is substantial heteroskedasticity or influential-case sensitivity, document the issue before changing the primary model. Potential sensitivity analyses may include:

-   heteroskedasticity-consistent standard errors,
-   robust regression,
-   transformations when substantively reasonable,
-   comparing results with and without highly influential observations when removal is justified independently of the outcome.

These should be treated as sensitivity analyses unless the analytical plan specifies otherwise.

### Simple Model

```{r}
h2_model_simple <- lm(
  cooperation_mean ~
    structure * motivation +
    dirty_dozen_machiavellianism,
  data = df
)

summary(h2_model_simple)
```

```{r}
h2_simple_coefficients <- broom::tidy(
  h2_model_simple,
  conf.int = TRUE
)
```

```{r}
h2_simple_table <- h2_simple_coefficients %>%
  mutate(
    Predictor = case_when(
      term == "(Intercept)" ~ "Intercept",
      
      term == "dirty_dozen_machiavellianism" ~
        "Machiavellianism",
      
      term == "structureIntergroup" ~
        "Structure",
      
      term == "motivationHybrid" ~
        "Hybrid vs. Proself",
      
      term == "motivationProsocial" ~
        "Prosocial vs. Proself",
      
      term == "structureIntergroup:motivationHybrid" ~
        "Structure × (Hybrid vs. Proself)",
      
      term == "structureIntergroup:motivationProsocial" ~
        "Structure × (Prosocial vs. Proself)",
      
      TRUE ~ term
    ),
    
    Estimate = format_stat(estimate),
    SE = format_stat(std.error),
    
    `95% CI` = paste0(
      "[",
      format_stat(conf.low),
      ", ",
      format_stat(conf.high),
      "]"
    ),
    
    p = format_stat(
      p.value,
      p_value = TRUE
    )
  ) %>%
  select(
    Predictor,
    Estimate,
    SE,
    `95% CI`,
    p
  )

h2_simple_table <- h2_simple_table %>%
  mutate(
    Predictor = factor(
      Predictor,
      levels = c(
        "Intercept",
        "Machiavellianism",
        "Structure",
        "Hybrid vs. Proself",
        "Prosocial vs. Proself",
        "Structure × (Hybrid vs. Proself)",
        "Structure × (Prosocial vs. Proself)"
      )
    )
  ) %>%
  arrange(Predictor) %>%
  mutate(
    Predictor = as.character(Predictor)
  )
```

## Figure

```{r}
unique(df$structure)
unique(df$motivation)
```

```{r}
fig_cooperation <- ggplot(
  df,
  aes(
    x = structure,
    y = cooperation_mean,
    fill = motivation
  )
) +
  geom_boxplot(
    position = position_dodge(width = 0.8),
    width = 0.65,
    alpha = 0.5,
    outlier.shape = NA,
    color = "black",
    linewidth = 0.4
  ) +
  geom_point(
    aes(
      color = motivation,
      group = motivation
    ),
    position = position_jitterdodge(
      jitter.width = 0.10,
      dodge.width = 0.8
    ),
    size = 1.2,
    alpha = 0.7
  ) +
  stat_summary(
    aes(group = motivation),
    fun = mean,
    geom = "point",
    position = position_dodge(width = 0.8),
    shape = 21,
    size = 2,
    fill = "white",
    color = "black",
    stroke = 0.8
  ) +
  theme_apa() +
  theme(
    text = element_text(
      size = 12,
      family = "serif",
      color = "black"
    ),
    axis.title = element_text(
      size = 12,
      face = "plain",
      color = "black"
    ),
    axis.text = element_text(
      size = 11,
      face = "plain",
      color = "black"
    ),
    legend.title = element_text(
      size = 12,
      face = "plain"
    ),
    legend.text = element_text(
      size = 11,
      face = "plain"
    ),
    axis.ticks = element_line(
      color = "black",
      linewidth = 0.5
    ),
    axis.line = element_line(
      color = "black"
    ),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    panel.border = element_blank()
  ) +
  labs(
    x = "Group Structure",
    y = "Cooperation",
    fill = "Motivation",
    color = "Motivation"
  )

fig_cooperation
```

## Export

```{r}
# ---------------------------------------------------------
# Prepare tables
# ---------------------------------------------------------

# Model coefficients
h2_model_coefficients <- broom::tidy(
  h2_model,
  conf.int = TRUE
)

h2_model_table <- h2_model_coefficients %>%
  mutate(
    Predictor = case_when(
      term == "(Intercept)" ~ "Intercept",
      term == "age_z" ~ "Age",
      term == "sex_num" ~ "Sex (1 = female)",
      term == "dirty_dozen_machiavellianism" ~ "Machiavellianism",
      term == "structureIntergroup" ~ "Structure",
      term == "motivationHybrid" ~ "Hybrid vs. Proself",
      term == "motivationProsocial" ~ "Prosocial vs. Proself",
      term == "structureIntergroup:motivationHybrid" ~
        "Structure × (Hybrid vs. Proself)",
      term == "structureIntergroup:motivationProsocial" ~
        "Structure × (Prosocial vs. Proself)",
      TRUE ~ term
    ),

    Estimate = format_stat(estimate),
    SE = format_stat(std.error),

    `95% CI` = paste0(
      "[",
      format_stat(conf.low),
      ", ",
      format_stat(conf.high),
      "]"
    ),

    p = format_stat(
      p.value,
      p_value = TRUE
    )
  ) %>%
  select(
    Predictor,
    Estimate,
    SE,
    `95% CI`,
    p
  )

h2_model_table <- h2_model_table %>%
  mutate(
    Predictor = factor(
      Predictor,
      levels = c(
        "Intercept",
        "Age",
        "Sex (1 = female)",
        "Machiavellianism",
        "Structure",
        "Hybrid vs. Proself",
        "Prosocial vs. Proself",
        "Structure × (Hybrid vs. Proself)",
        "Structure × (Prosocial vs. Proself)"
      )
    )
  ) %>%
  arrange(Predictor) %>%
  mutate(
    Predictor = as.character(Predictor)
  )

# Overall model fit
h2_model_fit <- broom::glance(h2_model)

# ANOVA / omnibus tests
h2_anova_export <- h2_anova %>%
  as.data.frame() %>%
  rownames_to_column("Effect")

# Emmeans
h2_emm_table_export <- h2_emm_table %>%
  mutate(
    Estimate_CI = paste0(
      format_stat(emmean),
      " [",
      format_stat(lower.CL),
      ", ",
      format_stat(upper.CL),
      "]"
    )
  ) %>%
  select(
    structure,
    motivation,
    Estimate_CI
  ) %>%
  pivot_wider(
    names_from = motivation,
    values_from = Estimate_CI
  ) %>%
  select(
    structure,
    Proself,
    Hybrid,
    Prosocial
  ) %>%
  rename(
    Structure = structure
  )

# Model diagnostics
h2_diagnostics <- broom::augment(h2_model) %>%
  select(
    .fitted,
    .resid,
    .std.resid,
    .hat,
    .cooksd
  )


# model fir
h2_model_fit <- broom::glance(h2_model)


```

```{r}
# ---------------------------------------------------------
# Create Excel workbook
# ---------------------------------------------------------

wb <- wb_workbook()

wb <- save_output_to_workbook(
  sheet_name = "Cooperation Controls",
  output = control_model_cooperation_table,
  wb = wb
)

wb$add_worksheet("Model Coefficients")
wb$add_data(
  sheet = "Model Coefficients",
  x = h2_model_table
)

wb$add_worksheet("Model Fit")
wb$add_data(
  sheet = "Model Fit",
  x = h2_model_fit
)

wb$add_worksheet("ANOVA")
wb$add_data(
  sheet = "ANOVA",
  x = h2_anova
)

wb$add_worksheet("Estimated Marginal Means")
wb$add_data(
  sheet = "Estimated Marginal Means",
  x = h2_emm_table_export
)

wb$add_worksheet("Pairwise Contrasts")
wb$add_data(
  sheet = "Pairwise Contrasts",
  x = h2_motivation_pairs_table
)

wb$add_worksheet("Model Diagnostics")
wb$add_data(
  sheet = "Model Diagnostics",
  x = h2_diagnostics
)
```

```{r}
wb <- save_output_to_workbook(
  sheet_name = "Cooperation Simple Model",
  output = h2_simple_table,
  wb = wb
)
```

```{r}
wb <- save_figure_to_workbook(
  wb = wb,
  sheet_name = "Cooperation Figure",
  figure_file = "../figures/cooperation.png",
  plot_obj = fig_cooperation,
  width = 8,
  height = 6,
  dpi = 300
)
```

```{r}
wb_save(
  wb,
  "../tables/cooperation.xlsx",
  overwrite = TRUE
)
```

## End of Script

```{r}
print("end of script")
```
